\item \htmladdnormallink{\it Video-rate acquisition fluorescence microscopy via generative adversarial networks}{https://cvinegoni.github.io/assets/pdf/proceedings/2020-BIBE.pdf} \\ Issa, T.B. and {\bf Vinegoni, C.} and Shaw, A. and Feruglio, P.F. and Weissleder, R. and Uminsky, D. \\ ``2020 IEEE 20th International Conference on Bioinformatics and Bioengineering (BIBE)''  (2020). \item \htmladdnormallink{\it An algorithm to correct 2D near-infrared fluorescence signals using 3D intravascular ultrasound architectural information}{https://cvinegoni.github.io/assets/pdf/proceedings/2011-SPIE.pdf} \\ Mallas, G. and Brooks, D.H. and Rosenthal, A. and {\bf Vinegoni, C.} and Calfon, M.A. and Razansky, D. and Jaffer, F.A. and Ntziachristos, V. \\ ``Multimodal Biomedical Imaging''  (2011). \item \htmladdnormallink{\it Fluorescent protein imaging with multispectral optoacoustic tomography}{https://cvinegoni.github.io/assets/pdf/proceedings/2010-SPIE.pdf} \\ Razansky, D. and Distel, M. and {\bf Vinegoni, C.} and Ma, R. and Koster, R. and Ntziachristos, V. \\ ``Photons Plus Ultrasound, San Jose (CA) 2010''  (2010). \item \htmladdnormallink{\it Deep tissue optoacoustic imaging of polarized structures}{https://cvinegoni.github.io/assets/pdf/proceedings/2009-BIOS-2.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Conference on Photons Plus Ultrasound - Imaging and Sensing''  (2009). \item \htmladdnormallink{\it Mesoscopic imaging of fluorescent proteins using multi-spectral optoacoustic tomography}{https://cvinegoni.github.io/assets/pdf/proceedings/2009-BIOS-1.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and ntziachristos, V. \\ ``Photons Plus Ultrasound, San Jose (CA)''  (2009). \item \htmladdnormallink{\it Multi-spectral photo-acoustic molecular tomography resolves fluorochrome distribution with high resolution and sensitivity in small animals}{https://cvinegoni.github.io/assets/pdf/proceedings/2008-SPIE.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Photons Plus Ultrasound, San Jose (CA)''  (2008). \item \htmladdnormallink{\it Multi-modality imaging of structure and function combining spectral-domain optical coherence and multiphoton microscopy}{https://cvinegoni.github.io/assets/pdf/proceedings/2006-SPIE.pdf} \\ {\bf Vinegoni, C.} and Ralston, T. and Tan, W. and Marks, D.L. and Boppart, S.A. \\ ``SPIE 2006''  (2006). \item \htmladdnormallink{\it Advances in optical imaging of dynamic three-dimensional engineered tissues}{https://cvinegoni.github.io/assets/pdf/proceedings/2006-BIOSA.pdf} \\ Boppart, S.A. and {\bf Vinegoni, C.} and Tan, W. and Luo, W. and Ralston, T. and Marks, D.L. \\ ``Biomedical OSA, Ft. Lauderdale (FL)''  (2006). \item \htmladdnormallink{\it Optical coherence tomography of cell dynamics in three-dimensional engineered tissues}{https://cvinegoni.github.io/assets/pdf/proceedings/2005-SPIE-2.pdf} \\ Boppart, S.A. and Tan, W. and Ko, H.J. and {\bf Vinegoni, C.} \\ ``SPIE 2005, Optical Coherence Tomography and Coherence Techniques II''  (2005). \item \htmladdnormallink{\it Molecularly-sensitive optical ranging using nonlinear interferometric vibrational imaging}{https://cvinegoni.github.io/assets/pdf/proceedings/2005-SPIE-1.pdf} \\ Marks, D.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Boppart, S.A. \\ ``Progress in Biomedical Optics and Imaging - Proceedings of SPIE Coherence Domain Optical Methods and Optical Coherence Tomography in Biomedicine IX''  (2005). \item \htmladdnormallink{\it Nonlinear interferometric vibrational imaging: optical ranging and spatial localization of CARS}{https://cvinegoni.github.io/assets/pdf/proceedings/2005-BIOS.pdf} \\ Marks, D.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Boppart, S.A. \\ ``BIOS 2005, San Jose, CA''  (2005). \item \htmladdnormallink{\it Structural and Functional Imaging of Engineered Tissue Development using an Integrated OCT and MultiPhoton Microscope}{https://cvinegoni.github.io/assets/pdf/proceedings/2004-SPIE-2.pdf} \\ Fahrner, L.J. and Tan, W. and {\bf Vinegoni, C.} and Eurell, T. and Boppart, S.A. \\ ``SPIE 2004 Medical Imaging (S. Diego, CA)''  (2004). \item \htmladdnormallink{\it Nonlinear interferometric vibrational imaging of molecular species}{https://cvinegoni.github.io/assets/pdf/proceedings/2004-SPIE-1.pdf} \\ Bredfeldt, J.S. and Marks, D.L. and {\bf Vinegoni, C.} and Hambir, S. and Dlott, D. and Boppart, S.A. \\ ``SPIE 2004 Medical Imaging (S. Diego, CA)''  (2004). \item \htmladdnormallink{\it Nonlinear optical contrast enhancement in OCT}{https://cvinegoni.github.io/assets/pdf/proceedings/2004-OSA-2.pdf} \\ {\bf Vinegoni, C.} and Bredfeldt, J.S. and Marks, D.L. and Boppart, S.A. \\ ``OSA BIOMED 2004 (Miami, FL)''  (2004). \item \htmladdnormallink{\it Functional optical coherence tomography of neurophysiology}{https://cvinegoni.github.io/assets/pdf/proceedings/2004-OSA-1.pdf} \\ Boppart, S.A. and Lazebnik, M. and {\bf Vinegoni, C.} and Bowonder, A. and Marks, D.L. and Gillete, R. \\ ``OSA BIOMED 2004 (Miami, FL)''  (2004). \item \htmladdnormallink{\it Contrast enhancement methods for optical coherence tomography}{https://cvinegoni.github.io/assets/pdf/proceedings/2004-LEOS.pdf} \\ Boppart, S.A. and Marks, D.L. and Oldenburg, A.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Chenyang, X. and Gunther, J.R. and Toublan, F.J.J. and Suslick, K.S. \\ ``2004 Digest of the LEOS Summer Topical Meetings''  (2004). \item \htmladdnormallink{\it Pulse Shaping Strategies for Nonlinear Interferometric Vibrational Imaging Optimized for Biomolecular Imaging}{https://cvinegoni.github.io/assets/pdf/proceedings/2004-EMBS.pdf} \\ Marks, D.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Boppart, S.A. \\ ``EMBS 2004 Engineering in Medicine and Biology (S. Francisico, CA)''  (2004). \item \htmladdnormallink{\it Distribution of Differential Group Delay in Recirculating Loops}{https://cvinegoni.github.io/assets/pdf/proceedings/2003-ECOC-2.pdf} \\ Petersson, M. and {\bf Vinegoni, C.} and Sunnerud, H. and Karlsson, M. \\ ``IEEE LEOS Summer Topical Meeting 2003, Vancouver, Canada''  (2003). \item \htmladdnormallink{\it Polarization-dependent loss statistics in recirculating loops}{https://cvinegoni.github.io/assets/pdf/proceedings/2003-ECOC-1.pdf} \\ {\bf Vinegoni, C.} and Karlsson, M. and Petersson, M. and Sunnerud, H. \\ ``ECOC 2003 (Rimini, Italy)''  (2003). \item \htmladdnormallink{\it PMD effect on measurements of distributed chromatic dispersion in DSF fibers}{https://cvinegoni.github.io/assets/pdf/proceedings/2002-PN.pdf} \\ Chen, H. and Leblanc, M. and Schinn, G. and {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``Photonics North 2002 (Quebec City, CA)''  (2002). \item \htmladdnormallink{\it Distributed measurements of chromatic dispersion and of the nonlinear coefficient in DSF fibers with non negligible values of PMD}{https://cvinegoni.github.io/assets/pdf/proceedings/2002-OFC.pdf} \\ {\bf Vinegoni, C.} and Chen, H. and Leblanc, M. and Schinn, G. and Wegmuller, M. and Gisin, N. \\ ``OFC 2002 (Anaheim, U.S.A.)''  (2002). \item \htmladdnormallink{\it A Comparison of Six techniques for nonlinear coefficient measurements of various single mode optical fibers}{https://cvinegoni.github.io/assets/pdf/proceedings/2002-NIST.pdf} \\ Namihira, Y. and Miyagy, K. and Kaneshima, K. and Tadakuma, M. and {\bf Vinegoni, C.} and Pietra, G. and Kawanami, K. \\ ``NIST 2002 Boulder, CO (USA)''  (2002). \item \htmladdnormallink{\it First and second order PMD emulator}{https://cvinegoni.github.io/assets/pdf/proceedings/2001-OFMC-2.pdf} \\ Wegmuller, M. and Demma, S. and {\bf Vinegoni, C.} and Gisin, N. \\ ``OFMC 2001, Cambridge (UK)''  (2001). \item \htmladdnormallink{\it Interlaboratory measurements of the nonlinear coefficient of standard SMF and DSF fibers using an inter- ferometric method and an SPM based cw dual-frequency method}{https://cvinegoni.github.io/assets/pdf/proceedings/2001-OFMC-1.pdf} \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. and Nakajima, K. and Ohashi, M. \\ ``OFMC 2001, Cambridge (UK)''  (2001). \item \htmladdnormallink{\it Measurements of the polarization coupling length in telecom fiber using nonlinear polarization rotation}{https://cvinegoni.github.io/assets/pdf/proceedings/2001-OFC.pdf} \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``OFC 2001 (Anaheim, U.S.A.)''  (2001). \item \htmladdnormallink{\it Measurements of the nonlinear coefficient n2/Aef f using a self aligned interferometer and a Faraday mirror}{https://cvinegoni.github.io/assets/pdf/proceedings/2000-NOISE.pdf} \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``NOISE 2000 (Twente, the Netherlands).''  (2000). \item \htmladdnormallink{\it Overview of coherent reflectometry techniques: characterization of components and small systems}{https://cvinegoni.github.io/assets/pdf/proceedings/2000-NIST-2.pdf} \\ Wegmuller, M. and Oberson, P. and von der Weid, J.P. and Guinnard, O. and Guinnard, L. and {\bf Vinegoni, C.} and Legre, M. and Gisin, N. \\ ``NIST 2000 (Boulder, CO)''  (2000). \item \htmladdnormallink{\it Estimation of the polarization coupling length in standard telecom fibers from measurements of nonlinear polarization rotation}{https://cvinegoni.github.io/assets/pdf/proceedings/2000-NIST-1.pdf} \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``NIST 2000 (Boulder, CO)''  (2000). \item \htmladdnormallink{\it Implementation of a Faraday mirror stabilization scheme for all optical switching in a standard telecom fiber}{https://cvinegoni.github.io/assets/pdf/proceedings/2000-ICTON.pdf} \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``ICTON 2000 (Warsaw, Poland)''  (2000). \item \htmladdnormallink{\it Faraday mirror stabilization scheme for nonlinear polarization rotation in optical fibers: model and applications}{https://cvinegoni.github.io/assets/pdf/proceedings/2000-CLEO.pdf} \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``CLEO 2000 (Nice)''  (2000). \item \htmladdnormallink{\it CVD diamond wires and tips for x-ray detection: growth and characterization by SEM and micro-Raman spectroscopy}{https://cvinegoni.github.io/assets/pdf/proceedings/1998-SPIE.pdf} \\ Manfredotti, C. and Fizzotti, F. and Lo Giudice, A. and Mucera, G. and Polesello, P. and Vittone, E. and Mariotto, G. and {\bf Vinegoni, C.} and Cazzanelli, E. \\ ``SPIE conference in “Laser processes in synthesis, characterization and processing of diamond”''  (1998). \item \htmladdnormallink{\it Radiative emission properties of a-SiN:H based alloys, nanometric multilayers and light emitting devices}{https://cvinegoni.github.io/assets/pdf/proceedings/1998-EMRS.pdf} \\ Giorgis, F. and Pirri, C.F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``E-MRS 98 Spring Meeting''  (1998). \item \htmladdnormallink{\it Changes of structural, optical and vibrational properties of WO3 powders after milling or mixing with ReO3}{https://cvinegoni.github.io/assets/pdf/proceedings/1998-ECSI.pdf} \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzmin, A. and Purans., J. \\ ``Electrochemical Society International meeting (S. Antonio TX, USA)''  (1998). 