\item \it A Mouse Model of Recurrent Myocardial Infarction Reports Diminished Emergency Hematopoiesis and Cardiac Inflammation \\ Cremer, S. and Schloss, M. and {\bf Vinegoni, C.} and Zhang, S. and Rohde, D. and Fumene, F.P. and Stephen, S. and Greg, W. and Weissleder, R. and Swirski, F.K. and Nahrendorf, M. \\ ``Circulation''  (2019). \item \it Two photon fluorescence polarization microscopy for imaging and quantifying drug target binding in vitro and in vivo \\ {\bf Vinegoni, C.} and Weissleder, R. \\ ``Abstracts of Papers of the American Chemical Society''  (2017). \item \it Mitochondrial morphology as a biomarker of cancer phenotype and drug response \\ Giedt, R.J. and Feruglio, P.F. and Pathania, D. and Yang, K.S. and {\bf Vinegoni, C.} and Mitchison, T.J. and Weissleder, R. \\ ``Cancer Research''  (2016). \item \it In Vivo Imaging of Anticancer Drug Activity At the Cellular Level \\ Dubach, J.M. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``AIChE Annual Meeting''  (2015). \item \it Imaging Drug Target Engagement in Vivo \\ Dubach, J.M. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``AIChE Annual Meeting''  (2014). \item \it Regulation of basal cell plasticity by epidermal growth factor and c-sRc in vivo in the mouse epididymis \\ Roy, J. and Ruan, Y.C. and Hill, E. and Visconti, P. and Krapf, D. and {\bf Vinegoni, C.} and Breton, S. \\ ``FASEB J.''  (2013). \item \it In-vivo two-photon imaging of the honeybee antennal lobe \\ Haase, A. and Rigosi, E. and Anfora, G. and {\bf Vinegoni, C.} and Vallortigara, G. and Antolini, R. \\ ``European Biophysics Journal with Biophysics Letters''  (2011). \item \it In-vivo Mesoscopic Fluorescence Tomography of Developing Insects \\ {\bf Vinegoni, C.} and Pitsouli, C and Razansky, D. and Perrimon, N. and Ntziachristos, V. \\ ``SMI, Rhode Island (MA)''  (2007). \item \it Live imaging of Drosophila pupae with Fluorescence Molecular Tomography \\ Pitsouli, C and {\bf Vinegoni, C.} and Razansky, D. and Ntziachristos, V. and Perrimon, N. \\ ``48th Annual Drosophila Research Conference (2007)''  (2007). \item \it In vivo near infrared fluorescence imaging of protease activity in a rabbit model of atherosclerosis \\ Jaffer, F.A. and Nahrendorf, M. and {\bf Vinegoni, C.} and John, M.C. and Aikawa, E. and Uchihashi, M. and Finn, A.V. and Ntziachristos, V. and Libby, P. and Gold, H.K. and Weissleder, R. \\ ``BMI''  (2006). \item \it In vivo imaging of protease activity in atherosclorosis using a near infrared fluorescence intravascular catheter \\ Jaffer, F.A. and Nahrendorf, M. and {\bf Vinegoni, C.} and John, M.C. and Aikawa, E. and Uchihashi, M. and Finn, A.V. and Ntziachristos, V. and Libby, P. and Gold, H.K. and Weissleder, R. \\ ``AHA 2006''  (2006). \item \it Nonlinear interferometric vibrational imaging for molecular species detection and localization \\ Boppart, S.A. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Marks, D.L. \\ ``The Society for Molecular Imaging Annual Meeting, St. Louis, MO''  (2004). \item \it Interferometric contrast between resonant coherent anti-Stokes Raman Scattering and nonresonant four-wave mixing \\ Marks, D.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Boppart, S.A. \\ ``Optical Society of America Annual Meeting, Rochester, NY''  (2004). \item \it Nonlinear interferometric vibrational imaging with differentiation of resonant CARS from nonresonant four-wave-mixing processes \\ Boppart, S.A. and Marks, D.L. and Bredfeldt, J.S. and {\bf Vinegoni, C.} \\ ``Optical Society of America Topical Meeting on Nonlinear Optics, Waikoloa, HI''  (2004). \item \it Molecular contrast enhancement for optical coherence tomography \\ Boppart, S.A. and Oldenburg, A.L. and Marks, D.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Xu, C. and Gunther, J.R. and Toublan, F.J.J. and Watkin, K.L. and Suslick, K.S. \\ ``Poster presentation, NIH Optical Imaging Workshop, Bethesda, MD''  (2004). \item \it Biomolecular laser imaging and therapeutic system \\ Marks, D.L. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Xu, C. and Wiedermann, A. and Dlott, D. and Gruebele, M. and Kitchell, B. and boppart, S.A. \\ ``Poster presentation, Frontiers of Biomedical Imaging Symposium, Urbana, IL''  (2004). \item \it Optical coherence tomography of neural activity \\ Bowonder, A. and {\bf Vinegoni, C.} and Yafremava, L. and Gillete, R. and Boppart, S.A. \\ ``Chicago Universities Bioengineering Industry Consortium (CUBIC). Chicago, IL''  (2004). \item \it Nonlinear interferometric vibrational imaging for molecular diagnostics \\ Boppart, S.A. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Marks, D.L. and Hambir, S. and Dlott, D. \\ ``Annual Conference of the Academy of Molecular Imaging, Orlando, FL''  (2004). \item \it Optical coherence tomography for basic science investigation and clinical diagnosis of cancer \\ Boppart, S.A. and Oldenburg, A.L. and Tan, W. and Marks, D.L. and Lee, T.M. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Luo, W. and Gunther, J.R. and Suslick, K.S. and Singletary, K.W. \\ ``Annual Meeting of the American Association for Cancer Research, Orlando, FL''  (2004). \item \it Nonlinear Interferometric Vibrational Imaging \\ Marks, D.L. and Hambir, S. and {\bf Vinegoni, C.} and Bredfeldt, J.S. and Xu, C. and Ye, J. and Wiedermann, A. and Dlott, D. and Gruebele, M. and Kitchell, B. and Boppart, S.A. \\ ``Meeting of the NCI/NASA Fundamental technologies for the development of biomolecular sensors programs''  (2003). \item \it A near infrared SNOM: first results and prospects \\ Mugnier, Y. and Mored, M. and Descouts, P. and {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``Workshop on nanoscience 2001. (Twannberg, CH)''  (2001). \item \it Nonlinear polarization rotation in high birefringence optical fibers with a Faraday mirror \\ {\bf Vinegoni, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Presented at Goteborg ’00 (COST 265)''  (2000). \item \it Measurement of nonlinear coefficient n2/Aef f in optical fibers using a self aligned interferometer and a Faraday Mirror \\ {\bf Vinegoni, C.} and Wegmuller, M. and Gisin, N. \\ ``Presented at Goteborg ’00 (COST 265)''  (2000). \item \it Pulsed laser deposition of gallium nitrade \\ Lunney, J.G. and Cole, D. and Cazzanelli, M. and {\bf Vinegoni, C.} and Castro, J. \\ ``Presented at THE 1ST UKNC CONFERENCE''  (1999). \item \it Structure and vibrational dynamics of WO3 and W1−xRexO3−y \\ {\bf Vinegoni, C.} \\ ``Presented at the Dept. of Physics, Universitaet Konstanz (D)''  (1999). \item \it Stress mapping in CVD diamond films by micro-Raman spectroscopy \\ Benedetti, S. and Mariotto, G. and Levy, J. and {\bf Vinegoni, C.} \\ ``APS 1999 Meeting (Atlanta)''  (1999). \item \it Morphological and optical characterization of GaN prepared by pulsed laser ablation \\ Trivelli, A. and Cazzanelli, M. and {\bf Vinegoni, C.} and Lunney, J.G. and Levy, J. \\ ``APS 1999 Meeting (Atlanta)''  (1999). \item \it Measurement of nonlinear polarization rotation in high birefringence optical fibers with a Faraday mirror \\ {\bf Vinegoni, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Presented at Amalfi Workshop ’99 (Amalfi, Italy)''  (1999). \item \it Porous silicon multilayers and microcavities \\ {\bf Vinegoni, C.} \\ ``Presented at the Dept. of Physics, University of Pittsburgh US''  (1998). \item \it Luminescent properties of GaN thin films prepared by Pulsed Laser Deposition \\ Cazzanelli, M. and Cole, D. and Lunney, J.G. and O'Donnel, K.P. and Middleton, P.G. and Trager-Cowan, C. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``EMRS Conference''  (1998). \item \it Raman spectroscopy and scanning electron microscopy investigations of annealed amorphous carbon- germanium films deposited by dc-magnetron sputtering \\ Mariotto, G. and {\bf Vinegoni, C.} and Jacobson, L.G. and Freire Jr., F.L. \\ ``Diamond 1998, 9th European Conf. on Diamond, Diamondlike materials, Nitrides and Silicon carbide. Creta, Greece''  (1998). \item \it Raman resonant effects at the oxide interface in WxRe1−xO3−y mixed systems \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzming, A. and Purans., J. \\ ``Annual conference of Raman Spectroscopy, Padova, Italy''  (1997). \item \it Investigations of the visible emission in thermal and pressure treated Czochralski-grown silicon \\ Cazzanelli, M. and Pavesi, L. and {\bf Vinegoni, C.} and Brusa, R.S. and Karwasz, G.P. and Tiengo, M. and Zecca, A. and Surma, B. and Misiuk, A. \\ ``Presented at the 5th annual meeting INSEL-V on “Light Emitting Silicon” in Modena''  (1997). \item \it Radiative recombination processes in a-Si:C, H thin films deposited by plasma enhanced chemical vapour deposition \\ Giorgis, F. and Giuliani, C.F. and Tresso, E. and Calcagno, L. and Musumeci, P. and Reitano, R. and Compagnini, G. and Pavesi, L. and {\bf Vinegoni, C.} \\ ``Presented at the 5th annual meeting INSEL-V on “Light Emitting Silicon” in Modena''  (1997). \item \it Photoluminescence and electroluminescence in amorphous silicon–based superlattice structures \\ Giorgis, F. and Pirri, C.F. and Rizzoli, R. and Summonte, C.  and Pavesi, L. and {\bf Vinegoni, C.} \\ ``Presented at the 5th annual meeting INSEL-V on “Light Emitting Silicon” in Modena''  (1997). 