\item \htmladdnormallink{\it  Cerebrospinal fluid can exit into the skull bone marrow and instruct cranial hematopoiesis in mice with bacterial meningitis}{https://boh/2022-NN.PDF} \\ Pulous, F. E. and Cruz-Hernandez, J. C. and Yang, C. B. and Kaya, Z. and Paccalet, A. and Wojtkiewicz, G. and Capen, D. and Brown, D. and Wu, J. W. and Schloss, M. J. and {\bf Vinegoni, C.} and Richter, D. and Yamazoe, M. and Hulsmans, M. and Momin, N. and Grune, J. and Rohde, D. and McAlpine, C. S. and Panizzi, P. and Weissleder, R. and Kim, D. E. and Swirski, F. K. and Lin, C. P. and Moskowitz, M. A. and Nahrendorf, M. \\ ``Nature Neuroscience'' Vol. 25 (2022) pp. 567-+. \\ DOI: 10.1038/s41593-022-01060-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Bone marrow endothelial dysfunction promotes myeloid cell expansion in cardiovascular disease}{https://boh/2022-NCR.pdf} \\ Rohde, D. and Vandoorne, K. and Lee, I. H. and Grune, J. and Zhang, S. and McAlpine, C. S. and Schloss, M. J. and Nayar, R. and Courties, G. and Frodermann, V. and Wojtkiewicz, G. and Honold, L. and Chen, Q. and Schmidt, S. and Iwamoto, Y. and Sun, Y. and Cremer, S. and Hoyer, F. F. and Iborra-Egea, O. and Muñoz-Guijosa, C. and Ji, F. and Zhou, G. and Adams, R. H. and Wythe, J. D. and Hidalgo, J. and Watanabe, H. and Jung, Y. and van der Laan, A. M. and Piek, J. J. and Kfoury, Y. and Désogère, P. A. and {\bf Vinegoni, C.} and Dutta, P. and Sadreyev, R. I. and Caravan, P. and Bayes-Genis, A. and Libby, P. and Scadden, D. T. and Lin, C. P. and Naxerova, K. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 28-44. \\ DOI: 10.1038/s44161-021-00002-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Astrocytic interleukin-3 programs microglia and limits Alzheimer's disease}{https://boh/2021-NATURE.pdf} \\ McAlpine, C. S. and Park, J. and Griciuc, A. and Kim, E. and Choi, S. H. and Iwamoto, Y. and Kiss, M. G. and Christie, K. A. and {\bf Vinegoni, C.} and Poller, W. C. and Mindur, J. E. and Chan, C. T. and He, S. and Janssen, H. and Wong, L. P. and Downey, J. and Singh, S. and Anzai, A. and Kahles, F. and Jorfi, M. and Feruglio, P. F. and Sadreyev, R. I. and Weissleder, R. and Kleinstiver, B. P. and Nahrendorf, M. and Tanzi, R. E. and Swirski$^\#$, F. K. \\ ``Nature'' Vol. 595 (2021) pp. 701-+. \\ DOI: 10.1038/s41586-021-03734-6 PMID: 34262178 PMCID: PMC8934148\item \htmladdnormallink{\it  CytoPAN-Portable cellular analyses for rapid point-of-care cancer diagnosis}{https://boh/2020-STM.pdf} \\ Min, J. and Chin, L. K. and Oh, J. and Landeros, C. and {\bf Vinegoni, C.} and Lee, J. and Lee, S. J. and Park, J. Y. and Liu, A. Q. and Castro, C. M. and Lee, H. and Im, H. and Weissleder$^\#$, R. \\ ``Science Translational Medicine'' Vol. 12 (2020) pp. 14. \\ DOI: 10.1126/scitranslmed.aaz9746 PMID: 32759277 PMCID: PMC8217912\item \htmladdnormallink{\it  Fluorescence microscopy tensor imaging representations for large-scale dataset analysis}{https://boh/2020-SCIREP.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Feruglio$^\dag$, P. F. and Courties, G. and Schmidt, S. and Hulsmans, M. and Lee, S. and Wang, R. and Sosnovik, D. and Nahrendorf, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 10 (2020) pp. 15. \\ DOI: 10.1038/s41598-020-62233-2 PMID: 32221334 PMCID: PMC7101442\item \htmladdnormallink{\it  Extended dynamic range imaging for noise mitigation in fluorescence anisotropy imaging}{https://boh/2020-JBO.pdf} \\ Feruglio$^\dag$, P. F. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 25 (2020) pp. 13. \\ DOI: 10.1117/1.Jbo.25.8.086003 PMID: 32820624 PMCID: PMC7439791\item \htmladdnormallink{\it  Diminished Reactive Hematopoiesis and Cardiac Inflammation in a Mouse Model of Recurrent Myocardial Infarction}{https://boh/2020-JAMCC.pdf} \\ Cremer, S. and Schloss, M. J. and {\bf Vinegoni, C.} and Foy, B. H. and Zhang, S. and Rohde, D. and Hulsmans, M. and Feruglio, P. F. and Schmidt, S. and Wojtkiewicz, G. and Higgins, J. M. and Weissleder, R. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 75 (2020) pp. 901-915. \\ DOI: 10.1016/j.jacc.2019.12.056 PMID: 32130926 PMCID: PMC7254576\item \htmladdnormallink{\it  Characterization of single microvesicles in plasma from glioblastoma patients}{https://boh/2019-NO.pdf} \\ Fraser, K. and Jo, A. and Giedt, J. and {\bf Vinegoni, C.} and Yang, K. S. and Peruzzi, P. and Chiocca, E. A. and Breakefield, X. O. and Lee, H. and Weissleder$^\#$, R. \\ ``Neuro-Oncology'' Vol. 21 (2019) pp. 606-615. \\ DOI: 10.1093/neuonc/noy187 PMID: 30561734 PMCID: 6502493\item \htmladdnormallink{\it  High Dynamic Range Fluorescence Imaging}{https://boh/2019-JSTQE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 25 (2019) pp. 7. \\ DOI: 10.1109/jstqe.2018.2881608 PMID: 31598059 PMCID: PMC6785194\item \htmladdnormallink{\it  Fluorescence anisotropy imaging in drug discovery}{https://boh/2019-ADDR.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Gryczynski, I. and Mazitschek, R. and Weissleder, R. \\ ``Advanced Drug Delivery Reviews'' Vol. 151 (2019) pp. 262-288. \\ DOI: 10.1016/j.addr.2018.01.019 PMID: 29410158 PMCID: 6072632\item \htmladdnormallink{\it  The anti-tumor diterpene oridonin is a direct inhibitor of Nucleolin in cancer cells}{https://boh/2018-SCIREP.pdf} \\ Vasaturo, M. and Cotugno, R. and Fiengo, L. and {\bf Vinegoni, C.} and Dal Piaz, F. and De Tommasi$^\#$, N. \\ ``Scientific Reports'' Vol. 8 (2018) pp. 13. \\ DOI: 10.1038/s41598-018-35088-x PMID: 30425290 PMCID: 6233161\item \htmladdnormallink{\it  Direct vascular channels connect skull bone marrow and the brain surface enabling myeloid cell migration}{https://boh/2018-NATNEURO.pdf} \\ Herisson, F. and Frodermann, V. and Courties, G. and Rohde, D. and Sun, Y. and Vandoorne, K. and Wojtkiewicz, G. R. and Masson, G. S. and {\bf Vinegoni, C.} and Kim, J. and Kim, D. E. and Weissleder, R. and Swirski, F. K. and Moskowitz, M. A. and Nahrendorf$^\#$, M. \\ ``Nature Neuroscience'' Vol. 21 (2018) pp. 1209-+. \\ DOI: 10.1038/s41593-018-0213-2 PMID: 30150661 PMCID: PMC6148759 \item \htmladdnormallink{\it  Cardiac macrophages promote diastolic dysfunction}{https://boh/2018-JEM.pdf} \\ Hulsmans, M. and Sager, H. B. and Roh, J. D. and Valero-Munoz, M. and Houstis, N. E. and Iwamoto, Y. and Sun, Y. and Wilson, R. M. and Wojtkiewicz, G. and Tricot, B. and Osborne, M. T. and Hung, J. and {\bf Vinegoni, C.} and Naxerova, K. and Sosnovik, D. E. and Zile, M. R. and Bradshaw, A. D. and Liao, R. and Tawakol, A. and Weissleder, R. and Rosenzweig, A. and Swirski, F. K. and Sam, F. and Nahrendorf$^\#$, M. \\ ``Journal of Experimental Medicine'' Vol. 215 (2018) pp. 423-440. \\ DOI: 10.1084/jem.20171274 PMID: 29339450 PMCID: PMC3366498\item \htmladdnormallink{\it  Imaging the Vascular Bone Marrow Niche During Inflammatory Stress}{https://boh/2018-CIRCRES.pdf} \\ Vandoorne, K. and Rohde, D. and Kim, H. Y. and Courties, G. and Wojtkiewicz, G. and Honold, L. and Hoyer, F. F. and Frodermann, V. and Nayar, R. and Herisson, F. and Jung, Y. and Desogere, P. A. and {\bf Vinegoni, C.} and Caravan, P. and Weissleder, R. and Sosnovik, D. E. and Lin, C. P. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Circulation Research'' Vol. 123 (2018) pp. 415-427. \\ DOI: 10.1161/circresaha.118.313302 PMID: 29980569 PMCID: 6202141\item \htmladdnormallink{\it  Design and Development of Fluorescent Vemurafenib Analogs for In Vivo Imaging}{https://boh/2017-THERA.pdf} \\ Mikula, H. and Stapleton, S. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Theranostics'' Vol. 7 (2017) pp. 1257-1265. \\ DOI: 10.7150/thno.18238 PMID: 28435463 PMCID: PMC5399591\item \htmladdnormallink{\it  Measurement of drug-target engagement in live cells by two-photon fluorescence anisotropy imaging}{https://boh/2017-NP.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Brand, C. and Lee, S. and Nibbs, A. E. and Stapleton, S. and Shah, S. and Gryczynski, I. and Reiner, T. and Mazitschek, R. and Weissleder, R. \\ ``Nature Protocols'' Vol. 12 (2017) pp. 1472-1497. \\ DOI: 10.1038/nprot.2017.043 PMID: 28686582 PMCID: PMC5928516\item \htmladdnormallink{\it  Quantitating drug-target engagement in single cells in vitro and in vivo}{https://boh/2017-NCBIOL.pdf} \\ Dubach, J. M. and Kim, E. and Yang, K. and Cuccarese, M. and Giedt, R. J. and Meirnetis, L. G. and {\bf Vinegoni$^\#$, C.} and Weissleder$^\#$, R. \\ ``Nature Chemical Biology'' Vol. 13 (2017) pp. 168-173. \\ DOI: 10.1038/nchembio.2248 PMID: 27918558 PMCID: PMC5630128\item \htmladdnormallink{\it  Motion characterization scheme to minimize motion artifacts in intravital microscopy}{https://boh/2017-JBO.pdf} \\ Lee, S. and Courties, G. and Nahrendorf, M. and Weissleder, R. and {\bf Vinegoni$^\#$, C.} \\ ``Journal of Biomedical Optics'' Vol. 22 (2017) pp. 7. \\ DOI: 10.1117/1.Jbo.22.3.036005 PMID: 28253383 PMCID: PMC5333764\item \htmladdnormallink{\it  Macrophages Facilitate Electrical Conduction in the Heart}{https://boh/2017-CELL.pdf} \\ Hulsmans, M. and Clauss, S. and Xiao, L. and Aguirre, A. D. and King, K. R. and Hanley, A. and Hucker, W. J. and Wulfers, E. M. and Seemann, G. and Courties, G. and Iwamoto, Y. and Sun, Y. and Savol, A. J. and Sager, H. B. and Lavine, K. J. and Fishbein, G. A. and Capen, D. E. and Da Silva, N. and Miquerol, L. and Wakimoto, H. and Seidman, C. E. and Seidman, J. G. and Sadreyev, R. I. and Naxerova, K. and Mitchell, R. N. and Brown, D. and Libby, P. and Weissleder, R. and Swirski, F. K. and Kohl, P. and {\bf Vinegoni, C.} and Milan, D. J. and Ellinor, P. T. and Nahrendorf$^\#$, M. \\ ``Cell'' Vol. 169 (2017) pp. 510-+. \\ DOI: 10.1016/j.cell.2017.03.050 PMID: 28431249 PMCID: PMC5474950\item \htmladdnormallink{\it  Transparent Electrophysiology Microelectrodes and Interconnects from Meta Nanomesh}{https://boh/2017-ACSN.pdf} \\ Seo, K. J. and Qiang, Y. and Bilgin, I. and Kar, S. and {\bf Vinegoni, C.} and Weissleder, R. and Fang$^\#$, H. \\ ``Acs Nano'' Vol. 11 (2017) pp. 4365-4372. \\ DOI: 10.1021/acsnano.7b01995 PMID: 28391679 PMCID: N/A\item \htmladdnormallink{\it  Two-photon imaging of pancreatic beta cells in real time in vivo}{https://boh/2016-TECHNOL.pdf} \\ Clardy, S. M. and Kohler, R. and {\bf Vinegoni, C.} and Iwamoto, Y. and Keliher, E. and Weissleder$^\#$, R. \\ ``Technology'' Vol. 4 (2016) pp. 130-34. \\ DOI: 10.1142/S2339547816200028 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  RNAi targeting multiple cell adhesion molecules reduces immune cell recruitment and vascular inflammation after myocardial infarction}{https://boh/2016-STM.pdf} \\ Sager, H. B. and Dutta, P. and Dahlman, J. E. and Hulsmans, M. and Courties, G. and Sun, Y. and Heidt, T. and {\bf Vinegoni, C.} and Borodovsky, A. and Fitzgerald, K. and Wojtkiewicz, G. R. and Iwamoto, Y. and Tricot, B. and Khan, O. F. and Kauffman, K. J. and Xing, Y. P. and Shaw, T. E. and Libby, P. and Langer, R. and Weissleder, R. and Swirski, F. K. and Anderson, D. G. and Nahrendorf$^\#$, M. \\ ``Science Translational Medicine'' Vol. 8 (2016) pp. 11. \\ DOI: 10.1126/scitranslmed.aaf1435 PMID: 27280687 PMCID: PMC5125383\item \htmladdnormallink{\it  Computational imaging reveals mitochondrial morphology as a biomarker of cancer phenotype and drug response}{https://boh/2016-SCIREP.pdf} \\ Giedt, R. J. and Fumene Feruglio, P. and Pathania, D. and Yang, K. S. and Kilcoyne, A. and {\bf Vinegoni, C.} and Mitchison, T. J. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 6 (2016) pp. 10. \\ DOI: 10.1038/srep32985 PMID: 27609668 PMCID: PMC5017129\item \htmladdnormallink{\it  Real-time high dynamic range laser scanning microscopy}{https://boh/2016-NCOMM-2.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Swisher$^\dag$, C. L. and Fumene Feruglio$^\dag$, P. and Giedt, R. J. and Rousso, D. L. and Stapleton, S. and Weissleder, R. \\ ``Nature Communications'' Vol. 7 (2016) pp. 13. \\ DOI: 10.1038/ncomms11077 PMID: 27032979 PMCID: PMC4821995\item \htmladdnormallink{\it  Tyrosine kinase-mediated axial motility of basal cells revealed by intravital imaging}{https://boh/2016-NCOMM-1.pdf} \\ Roy, J. and Kim, B. and Hill, E. and Visconti, P. and Krapf, D. and {\bf Vinegoni, C.} and Weissleder, R. and Brown, D. and Breton$^\#$, S. \\ ``Nature Communications'' Vol. 7 (2016) pp. 11. \\ DOI: 10.1038/ncomms10666 PMID: 26868824 PMCID: PMC4754344\item \htmladdnormallink{\it  Two-Photon Fluorescence Anisotropy Microscopy for Imaging and Direct Measurement of Intracellular Drug Target Engagement}{https://boh/2016-IEEE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 22 (2016) pp. 7. \\ DOI: 10.1109/jstqe.2015.2501384 PMID: 27440991 PMCID: PMC4946648\item \htmladdnormallink{\it  Rapid, high efficiency isolation of pancreatic beta-cells}{https://boh/2015-SREP.pdf} \\ Clardy, S. M. and Mohan, J. F. and {\bf Vinegoni, C.} and Keliher, E. J. and Iwamoto, Y. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 5 (2015) pp. 9. \\ DOI: 10.1038/srep13681 PMID: 26330153 PMCID: PMC4557033\item \htmladdnormallink{\it  Imaging the beating heart in the mouse using intravital microscopy techniques}{https://boh/2015-NPROT.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Aguirre$^\dag$, A. D. and Lee, S. and Weissleder, R. \\ ``Nature Protocols'' Vol. 10 (2015) pp. 1802-1819. \\ DOI: 10.1038/nprot.2015.119 PMID: 26492138 PMCID: PMC5380003\item \htmladdnormallink{\it  New techniques for motion-artifact-free in vivo cardiac microscopy}{https://boh/2015-FPHYS.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Aguirre, A. D. and Weissleder, R. \\ ``Frontiers in Physiology'' Vol. 6 (2015) pp. 12. \\ DOI: 10.3389/fphys.2015.00147 PMID: 26029116 PMCID: PMC4428079\item \htmladdnormallink{\it  Advances in measuring single-cell pharmacology in vivo}{https://boh/2015-DDT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Thurber, G. M. and Miller, M. A. and Mazitschek, R. and Weissleder, R. \\ ``Drug Discovery Today'' Vol. 20 (2015) pp. 1087-1092. \\ DOI: 10.1016/j.drudis.2015.05.011 PMID: 26024776 PMCID: PMC4567932\item \htmladdnormallink{\it  Myocardial Infarction Activates CCR2(+) Hematopoietic Stem and Progenitor Cells}{https://boh/2015-CSC.pdf} \\ Dutta, P. and Sager, H. B. and Stengel, K. R. and Naxerova, K. and Courties, G. and Saez, B. and Silberstein, L. and Heidt, T. and Sebas, M. and Sun, Y. and Wojtkiewicz, G. and Fumene Feruglio, P. and King, K. and Baker, J. N. and van der Laan, A. M. and Borodovsky, A. and Fitzgerald, K. and Hulsmans, M. and Hoyer, F. and Iwamoto, Y. and {\bf Vinegoni, C.} and Brown, D. and Di Carli, M. and Libby, P. and Hiebert, S. W. and Scadden, D. T. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Cell Stem Cell'' Vol. 16 (2015) pp. 477-487. \\ DOI: 10.1016/j.stem.2015.04.008 PMID: 25957903 PMCID: PMC4426344\item \htmladdnormallink{\it  Automated motion artifact removal for intravital microscopy, without a priori information}{https://boh/2014-SR.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Sebas, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 4 (2014) pp. 9. \\ DOI: 10.1038/srep04507 PMID: 24676021 PMCID: PMC3968488\item \htmladdnormallink{\it  Intravital imaging of cardiac function at the single-cell level}{https://boh/2014-PNAS.pdf} \\ Aguirre, A. D. and {\bf Vinegoni$^\#$, C.} and Sebas, M. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 111 (2014) pp. 11257-11262. \\ DOI: 10.1073/pnas.1401316111 PMID: 25053815 PMCID: PMC4128110\item \htmladdnormallink{\it  Steady state anisotropy two-photon microscopy resolves multiple, spectrally similar fluorophores, enabling in vivo multilabel imaging}{https://boh/2014-OL.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Optics Letters'' Vol. 39 (2014) pp. 4482-4485. \\ DOI: 10.1364/ol.39.004482 PMID: 25078208 PMCID: PMC4341989\item \htmladdnormallink{\it  Chronic variable stress activates hematopoietic stem cells}{https://boh/2014-NM.pdf} \\ Heidt, T. and Sager, H. B. and Courties, G. and Dutta, P. and Iwamoto, Y. and Zaltsman, A. and von zur Muhlen, C. and Bode, C. and Fricchione, G. L. and Denninger, J. and Lin, C. P. and {\bf Vinegoni, C.} and Libby, P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature Medicine'' Vol. 20 (2014) pp. 754-758. \\ DOI: 10.1038/nm.3589 PMID: 24952646 PMCID: PMC4087061\item \htmladdnormallink{\it  In vivo imaging of specific drug-target binding at subcellular resolution}{https://boh/2014-NC.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Mazitschek, R. and Fumene Feruglio, P. and Cameron, L. A. and Weissleder, R. \\ ``Nature Communications'' Vol. 5 (2014) pp. 9. \\ DOI: 10.1038/ncomms4946 PMID: 24867710 PMCID: PMC4362617\item \htmladdnormallink{\it  Advanced Motion Compensation Methods for Intravital Optical Microscopy}{https://boh/2014-IEEE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 20 (2014) pp. 9. \\ DOI: 10.1109/jstqe.2013.2279314 PMID: 24273405 PMCID: PMC3832946\item \htmladdnormallink{\it  Perinatal health and translational medicine}{https://boh/2013-JHGD.pdf} \\ Figueiredo, J. L. and {\bf Vinegoni, C.} and De Abreu, L. C. \\ ``Journal of Human Growth and Development'' Vol. 23 (2013) pp. 125-127. \\ DOI: 10.7322/jhgd.61318 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Sequential average segmented microscopy for high signal-to-noise ratio motion-artifact-free in vivo heart imaging}{https://boh/2013-BOE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Marzola, P. and Nahrendorf, M. and Weissleder, R. \\ ``Biomedical Optics Express'' Vol. 4 (2013) pp. 2095-2106. \\ DOI: 10.1364/boe.4.002095 PMID: 24156067 PMCID: PMC3799669\item \htmladdnormallink{\it  Noise suppressed, multifocus image fusion for enhanced intraoperative navigation}{https://boh/2013-BIOPHTNCS.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Fexon, L. and Thurber, G. and Sbarbati, A. and Weissleder, R. \\ ``Journal of Biophotonics'' Vol. 6 (2013) pp. 363-370. \\ DOI: 10.1002/jbio.201200086 PMID: 22887724 PMCID: PMC3779878\item \htmladdnormallink{\it  Implantable microenvironments to attract hematopoietic stem/cancer cells}{https://boh/2012-PNAS.pdf} \\ Lee, J. and Li, M. and Milwid, J. and Dunham, J. and {\bf Vinegoni, C.} and Gorbatov, R. and Iwamoto, Y. and Wang, F. J. and Shen, K. Y. and Hatfield, K. and Enger, M. and Shafiee, S. and McCormack, E. and Ebert, B. L. and Weissleder, R. and Yarmush, M. L. and Parekkadan$^\#$, B. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 109 (2012) pp. 19638-19643. \\ DOI: 10.1073/pnas.1208384109 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Mapping Molecular Agents Distributions in Whole Mice Hearts Using Born-Normalized Optical Projection Tomography}{https://boh/2012-PLOSONE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio$^\dag$, P. and Razansky, D. and Gorbatov, R. and Ntziachristos, V. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Plos One'' Vol. 7 (2012) pp. 9. \\ DOI: 10.1371/journal.pone.0034427 PMID: 22509302 PMCID: PMC3324534\item \htmladdnormallink{\it  Imaging Therapeutic PARP Inhibition In Vivo through Bioorthogonally Developed Companion Imaging Agents}{https://boh/2012-NEOPLASIA.pdf} \\ Reiner, T. and Lacy, J. and Keliher, E. J. and Yang, K. S. and Ullal, A. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Neoplasia'' Vol. 14 (2012) pp. 169-+. \\ DOI: 10.1593/neo.12414 PMID: 22496617 PMCID: PMC3323895\item \htmladdnormallink{\it  Real-time in vivo imaging of the beating mouse heart at microscopic resolution}{https://boh/2012-NC.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Fexon, L. and Gorbatov, R. and Pivoravov, M. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Nature Communications'' Vol. 3 (2012) pp. 8. \\ DOI: 10.1038/ncomms2060 PMID: 22968700 PMCID: PMC3622400\item \htmladdnormallink{\it  Myocardial infarction accelerates atherosclerosis}{https://boh/2012-NATURE.pdf} \\ Dutta, P. and Courties, G. and Wei, Y. and Leuschner, F. and Gorbatov, R. and Robbins, C. S. and Iwamoto, Y. and Thompson, B. and Carlson, A. L. and Heidt, T. and Majmudar, M. D. and Lasitschka, F. and Etzrodt, M. and Waterman, P. and Waring, M. T. and Chicoine, A. T. and van der Laan, A. M. and Niessen, H. W. M. and Piek, J. J. and Rubin, B. B. and Butany, J. and Stone, J. R. and Katus, H. A. and Murphy, S. A. and Morrow, D. A. and Sabatine, M. S. and {\bf Vinegoni, C.} and Moskowitz, M. A. and Pittet, M. J. and Libby, P. and Lin, C. P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature'' Vol. 487 (2012) pp. 325-329. \\ DOI: 10.1038/nature11260 PMID: 22763456 PMCID: PMC3401326\item \htmladdnormallink{\it  Improved intravital microscopy via synchronization of respiration and holder stabilization}{https://boh/2012-JBO.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 17 (2012) pp. 8. \\ DOI: 10.1117/1.Jbo.17.9.096018 PMID: 23085919 PMCID: PMC3449295\item \htmladdnormallink{\it  PET/MRI of Inflammation in Myocardial Infarction}{https://boh/2012-JACC.pdf} \\ Lee, W. W. and Marinelli, B. and van der Laan, A. M. and Sena, B. F. and Gorbatov, R. and Leuschner, F. and Dutta, P. and Iwamoto, Y. and Ueno, T. and Begieneman, M. P. V. and Niessen, H. W. M. and Piek, J. J. and {\bf Vinegoni, C.} and Pittet, M. J. and Swirski, F. K. and Tawakol, A. and Di Carli, M. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 59 (2012) pp. 153-163. \\ DOI: 10.1016/j.jacc.2011.08.066 PMID: 22222080 PMCID: PMC3257823\item \htmladdnormallink{\it  Motion compensation using a suctioning stabilizer for intravital microscopy}{https://boh/2012-INTRVTL.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Gorbatov, R. and Weissleder, R. \\ ``Intravital'' Vol. 1 (2012) pp. 115. \\ DOI: 10.4161/intv.23017 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Deep Tissue Optical and Optoacoustic Molecular Imaging Technologies for Pre-Clinical Research and Drug Discovery}{https://boh/2012-CPB.pdf} \\ Razansky$^\#$, D. and Deliolanis, N. C. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Current Pharmaceutical Biotechnology'' Vol. 13 (2012) pp. 504-522. \\ DOI: 10.2174/138920112799436258 PMID: 22216767 PMCID: N/A\item \htmladdnormallink{\it  In Vivo Imaging of Drug-Induced Mitochondrial Outer Membrane Permeabilization at Single-Cell Resolution}{https://boh/2012-CNCRRES.pdf} \\ Earley, S. and {\bf Vinegoni, C.} and Dunham, J. and Gorbatov, R. and Fumene Feruglio, P. and Weissleder$^\#$, R. \\ ``Cancer Research'' Vol. 72 (2012) pp. 2949-2956. \\ DOI: 10.1158/0008-5472.Can-11-4096 PMID: 22505651 PMCID: PMC3603290\item \htmladdnormallink{\it  Optochemogenetics (OCG) Allows More Precise Control of Genetic Engineering in Mice with CreER regulators}{https://boh/2012-BIOCHEM.pdf} \\ Lu, X. and Agasti, S. S. and {\bf Vinegoni, C.} and Waterman, P. and DePinho, R. A. and Weissleder$^\#$, R. \\ ``Bioconjugate Chemistry'' Vol. 23 (2012) pp. 1945-1951. \\ DOI: 10.1021/bc300319c PMID: 22917215 PMCID: PMC3775343\item \htmladdnormallink{\it  Bioorthogonal Imaging of Aurora Kinase A in Live Cells}{https://boh/2012-AC.pdf} \\ Yang, K. S. and Budin, G. and Reiner, T. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Angewandte Chemie-International Edition'' Vol. 51 (2012) pp. 6598-6603. \\ DOI: 10.1002/anie.201200994 PMID: 22644700 PMCID: PMC3523717\item \htmladdnormallink{\it  Indocyanine Green Enables Near-Infrared Fluorescence Imaging of Lipid-Rich, Inflamed Atherosclerotic Plaques}{https://boh/2011-STM.pdf} \\ {\bf Vinegoni, C.} and Botnaru, I. and Aikawa, E. and Calfon, M. A. and Iwamoto, Y. and Folco, E. J. and Ntziachristos, V. and Weissleder, R. and Libby, P. and Jaffer$^\#$, F. A. \\ ``Science Translational Medicine'' Vol. 3 (2011) pp. 9. \\ DOI: 10.1126/scitranslmed.3001577 PMID: 21613624 PMCID: PMC3112179\item \htmladdnormallink{\it  Accurate measurement of pancreatic islet beta-cell mass using a second-generation fluorescent exendin-4 analog}{https://boh/2011-PNAS.pdf} \\ Reiner, T. and Thurber, G. and Gaglia, J. and {\bf Vinegoni, C.} and Liew, C. W. and Upadhyay, R. and Kohler, R. H. and Li, L. and Kulkarni, R. N. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 108 (2011) pp. 12815-12820. \\ DOI: 10.1073/pnas.1109859108 PMID: 21768367 PMCID: PMC3150928\item \htmladdnormallink{\it  A multimodal approach for tracing lateralisation along the olfactory pathway in the honeybee through electrophysiological recordings, morpho-functional imaging, and behavioural studies}{https://boh/2011-EB.pdf} \\ Haase, A. and Rigosi, E. and Frasnelli, E. and Trona, F. and Tessarolo, F. and {\bf Vinegoni, C.} and Anfora, G. and Vallortigara, G. and Antolini$^\#$, R. \\ ``European Biophysics Journal with Biophysics Letters'' Vol. 40 (2011) pp. 1247-1258. \\ DOI: 10.1007/s00249-011-0748-6 PMID: 21956452 PMCID: PMC3366498\item \htmladdnormallink{\it  Searching for anatomical correlates of olfactory lateralization in the honeybee antennal lobes: A morphological and behavioural study}{https://boh/2011-BBR.pdf} \\ Rigosi$^\#$, E. and Frasnelli, E. and {\bf Vinegoni, C.} and Antolini, R. and Anfora, G. and Vallortigara, G. and Haase, A. \\ ``Behavioural Brain Research'' Vol. 221 (2011) pp. 290-294. \\ DOI: 10.1016/j.bbr.2011.03.015 PMID: 21402106 PMCID: PMC3089663\item \htmladdnormallink{\it  Intraoperative Near-infrared Fluorescent Cholangiography (NIRFC) in Mouse Models of Bile Duct Injury: Reply}{https://boh/2010-WJS.pdf} \\ Figueiredo, J. L. and Nahrendorf, M. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``World Journal of Surgery'' Vol. 35 (2011) pp. 694-695. \\ DOI: 10.1007/s00268-010-0728-5 PMID: 20645091 PMCID: N/A\item \htmladdnormallink{\it  Hybrid PET-optical imaging using targeted probes}{https://boh/2010-PNAS.pdf} \\ Nahrendorf$^{\dag \#}$, M. and Keliher$^\dag$, E. and Marinelli, B. and Waterman, P. and Fumene Feruglio, P. and Fexon, L. and Pivovarov, M. and Swirski, F. K. and Pittet, M. J. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 107 (2010) pp. 7910-7915. \\ DOI: 10.1073/pnas.0915163107 PMID: 20385821 PMCID: PMC2867879\item \htmladdnormallink{\it  Block matching 3D random noise filtering for absorption optical projection tomography}{https://boh/2010-PMB.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Gros, J. and Sbarbati, A. and Weissleder, R. \\ ``Physics in Medicine and Biology'' Vol. 55 (2010) pp. 5401-5415. \\ DOI: 10.1088/0031-9155/55/18/009 PMID: 20736500 PMCID: PMC2934766\item \htmladdnormallink{\it  Imaging of molecular probe activity with Born-normalized fluorescence optical projection tomography}{https://boh/2010-OL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Cortez-Retamozo, V. and Razansky, D. and Medoff, B. D. and Ntziachristos, V. and Sbarbati, A. and Pittet, M. and Weissleder, R. \\ ``Optics Letters'' Vol. 35 (2010) pp. 1088-1090. \\ DOI: 10.1364/ol.35.001088 PMID: 20364226 PMCID: PMC2900933\item \htmladdnormallink{\it  Intravascular near-infrared fluorescence molecular imaging of atherosclerosis: toward coronary arterial visualization of biologically high-risk plaques}{https://boh/2010-JBO.pdf} \\ Calfon, M. A. and {\bf Vinegoni, C.} and Ntziachristos, V. and Jaffer$^\#$, F. A. \\ ``Journal of Biomedical Optics'' Vol. 15 (2010) pp. 6. \\ DOI: 10.1117/1.3280282 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  WNT5A/JNK and FGF/MAPK Pathways Regulate the Cellular Events Shaping the Vertebrate Limb Bud}{https://boh/2010-CB.pdf} \\ Gros, J. and Hu, J. K. H. and {\bf Vinegoni, C.} and Fumene Feruglio, P. and Weissleder, R. and Tabin$^\#$, C. J. \\ ``Current Biology'' Vol. 20 (2010) pp. 1993-2002. \\ DOI: 10.1016/j.cub.2010.09.063 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  In-vivo two-photon imaging of the honey bee antennal lobe}{https://boh/2010-BOEX.pdf} \\ Haase, A. and Rigosi, E. and Trona, F. and Anfora, G. and Vallortigara, G. and Antolini, R. and {\bf Vinegoni$^\#$, C.} \\ ``Biomedical Optics Express'' Vol. 2 (2011) pp. 131-138. \\ DOI: 10.1364/boe.2.000131 PMID: 21326643 PMCID: PMC3028488\item \htmladdnormallink{\it  Imaging of mesoscopic-scale organisms using selective-plane optoacoustic tomography}{https://boh/2009-PMB.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Physics in Medicine and Biology'' Vol. 54 (2009) pp. 2769-2777. \\ DOI: 10.1088/0031-9155/54/9/012 PMID: 19369709 PMCID: N/A\item \htmladdnormallink{\it  Normalized Born ratio for fluorescence optical projection tomography}{https://boh/2009-OL-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 319-321. \\ DOI: 10.1364/ol.34.000319 PMID: 19183644 PMCID: PMC2771918\item \htmladdnormallink{\it  Transillumination fluorescence imaging in mice using biocompatible upconverting nanoparticles}{https://boh/2009-OL-1.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Razansky$^\dag$, D. and Hilderbrand, S. A. and Shao, F. W. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 2566-2568. \\ DOI: 10.1364/ol.34.002566 PMID: 19724491 PMCID: PMC2749971\item \htmladdnormallink{\it  Diffractionless beam in free space with adiabatic changing refractive index in a single mode tapered slab waveguide}{https://boh/2009-OE-2.pdf} \\ Tsai$^\#$, C. C. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 21723-21731. \\ DOI: 10.1364/oe.17.021723 PMID: 19997414 PMCID: PMC2805120\item \htmladdnormallink{\it  High throughput transmission optical projection tomography using low cost graphics processing unit}{https://boh/2009-OE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fexon, L. and Fumene Feruglio, P. and Pivovarov, M. and Figueiredo, J. L. and Nahrendorf, M. and Pozzo, A. and Sbarbati, A. and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 22320-22332. \\ DOI: 10.1364/oe.17.022320 PMID: 20052155 PMCID: PMC2805020\item \htmladdnormallink{\it  Multispectral opto-acoustic tomography of deep-seated fluorescent proteins in vivo}{https://boh/2009-NATPHOT.pdf} \\ Razansky$^\#$, D. and Distel, M. and {\bf Vinegoni, C.} and Ma, R. and Perrimon, N. and Koster, R. W. and Ntziachristos$^\#$, V. \\ ``Nature Photonics'' Vol. 3 (2009) pp. 412-417. \\ DOI: 10.1038/nphoton.2009.98 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Mesoscopic Fluorescence Tomography for In-vivo Imaging of Developing Drosophila}{https://boh/2009-JOVE-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Pitsouli, C. and Perrimon, N. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1510. \\ DOI: 10.3791/1510 PMID: 19696720 PMCID: PMC2736679\item \htmladdnormallink{\it  Born normalization for fluorescence optical projection tomography for whole heart imaging}{https://boh/2009-JOVE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Fexon, L. and Pivoravov, M. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1389. \\ DOI: 10.3791/1389 PMID: 19578329 PMCID: PMC2794886\item \htmladdnormallink{\it  Unprecedent in vivo views at the mesoscopic scale}{https://boh/2009-BOW.pdf} \\ Razansky, R. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``BioOptics World'' Vol. 2 (2009) pp. 22. \\ DOI: N/A PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Polarization-sensitive optoacoustic tomography of optically diffuse tissues}{https://boh/2008-OL.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Optics Letters'' Vol. 33 (2008) pp. 2308-2310. \\ DOI: 10.1364/ol.33.002308 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  In vivo imaging of Drosophila melanogaster pupae with mesoscopic fluorescence tomography}{https://boh/2008-NM.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Pitsouli$^\dag$, C. and Razansky$^\dag$, D. and Perrimon, N. and Ntziachristos, V. \\ ``Nature Methods'' Vol. 5 (2008) pp. 45-47. \\ DOI: 10.1038/nmeth1149 PMID: 18066071 PMCID: N/A\item \htmladdnormallink{\it  Real-time assessment of inflammation and treatment response in a mouse model of allergic airway inflammation}{https://boh/2008-JCI.pdf} \\ Cortez-Retamozo, V. and Swirski, F. K. and Waterman, P. and Yuan, H. and Figueiredo, J. L. and Newton, A. P. and Upadhyay, R. and {\bf Vinegoni, C.} and Kohler, R. and Blois, J. and Smith, A. and Nahrendorf, M. and Josephson, L. and Weissleder, R. and Pittet$^\#$, M. J. \\ ``Journal of Clinical Investigation'' Vol. 118 (2008) pp. 4058-4066. \\ DOI: 10.1172/jci36335 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  Real-Time Catheter Molecular Sensing of Inflammation in Proteolytically Active Atherosclerosis}{https://boh/2008-CRCLT.pdf} \\ Jaffer, F. A. and {\bf Vinegoni, C.} and John, M. C. and Aikawa, E. and Gold, H. K. and Finn, A. V. and Ntziachristos, V. and Libby, P. and Weissleder$^\#$, R. \\ ``Circulation'' Vol. 118 (2008) pp. 1802-1809. \\ DOI: 10.1161/circulationaha.108.785881 PMID: 18852366 PMCID: PMC2729441\item \htmladdnormallink{\it  Multispectral photoacoustic imaging of fluorochromes in small animals}{https://boh/2007-OL.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``Optics Letters'' Vol. 32 (2007) pp. 2891-2893. \\ DOI: 10.1364/ol.32.002891 PMID: 17909608 PMCID: N/A\item \htmladdnormallink{\it  Imaging cellular responses to mechanical stimuli within three-dimensional tissue constructs}{https://boh/2007-MRT.pdf} \\ Tan, W. and {\bf Vinegoni, C.} and Norman, J. J. and Desai, T. A. and Boppart$^\#$, S. A. \\ ``Microscopy Research and Technique'' Vol. 70 (2007) pp. 361-371. \\ DOI: 10.1002/jemt.20420 PMID: 17262787 PMCID: N/A\item \htmladdnormallink{\it  High-spectral-resolution coherent anti-Stokes Raman scattering with interferometric ally detected broadband chirped pulses}{https://boh/2006-OL-2.pdf} \\ Jones, G. W. and Marks, D. L. and {\bf Vinegoni, C.} and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1543-1545. \\ DOI: 10.1364/ol.31.001543 PMID: 16642166 PMCID: N/A\item \htmladdnormallink{\it  Spectroscopic spectral-domain optical coherence microscopy}{https://boh/2006-OL-1.pdf} \\ Xu, C. Y. and {\bf Vinegoni, C.} and Ralston, T. S. and Luo, W. and Tan, W. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1079-1081. \\ DOI: 10.1364/ol.31.001079 PMID: 16625909 PMCID: N/A\item \htmladdnormallink{\it  Integrated structural and functional optical imaging combining spectral-domain optical coherence and multiphoton microscopy}{https://boh/2006-APL.pdf} \\ {\bf Vinegoni, C.} and Ralston, T. and Tan, W. and Luo, W. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 88 (2006) pp. 3. \\ DOI: 10.1063/1.2171477 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Nonlinear Interferometric Vibrational Imaging. efficient detection of Coherent Anti-Stokes Raman Scattering}{https://boh/2005-OPN.pdf} \\ McAlpine, C. S. and Marks, D. and {\bf Vinegoni, C.} and Bredfeldt, J. and Boppart$^\#$, S.A. \\ ``Optics & Photonics News'' Vol. 16 (2005) pp. 23. \\ DOI: 10.1364/OPN.16.12.000023 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Molecularly sensitive optical coherence tomography}{https://boh/2005-OL.pdf} \\ Bredfeldt, J. S. and {\bf Vinegoni, C.} and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 30 (2005) pp. 495-497. \\ DOI: 10.1364/ol.30.000495 PMID: 15789714 PMCID: N/A\item \htmladdnormallink{\it  Nonlinear optical contrast enhancement for optical coherence tomography}{https://boh/2004-OE.pdf} \\ {\bf Vinegoni, C.} and Bredfeldt, J. S. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Express'' Vol. 12 (2004) pp. 331-341. \\ DOI: 10.1364/opex.12.000331 PMID: 19471542 PMCID: N/A\item \htmladdnormallink{\it  The statistics of polarization-dependent loss in a recirculating loop}{https://boh/2004-JLT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Karlsson, M. and Petersson, M. and Sunnerud, H. \\ ``Journal of Lightwave Technology'' Vol. 22 (2004) pp. 968-976. \\ DOI: 10.1109/jlt.2004.824861 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Interferometric differentiation between resonant coherent anti-Stokes Raman scattering and nonresonant four-wave-mixing processes}{https://boh/2004-APL.pdf} \\ Marks, D. L. and {\bf Vinegoni, C.} and Bredfeldt, J. S. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 85 (2004) pp. 5787-5789. \\ DOI: 10.1063/1.1829162 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed measurements of chromatic dispersion and nonlinear coefficient in low-PMD dispersion-shifted fibers}{https://boh/2003-PTL-2.pdf} \\ {\bf Vinegoni, C.} and Chen$^\#$, H. X. and Leblanc, M. and Schinn, G. W. and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 739-741. \\ DOI: 10.1109/lpt.2003.810249 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Statistics of PMD in recirculating loops}{https://boh/2003-PTL-1.pdf} \\ Petersson$^\#$, M. and {\bf Vinegoni, C.} and Sunnerud, H. and Karlsson, M. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 1543-1545. \\ DOI: 10.1109/lpt.2003.818681 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Emulator of first- and second-order polarization-mode dispersion}{https://boh/2002-PTL.pdf} \\ Wegmuller, M. and Demma, S. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 14 (2002) pp. 630-632. \\ DOI: 10.1109/68.998707 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Analysis of the polarization evolution in a ribbon cable using high-resolution coherent OFDR}{https://boh/2001-PTL-2.pdf} \\ Wegmuller, M. and Legre, M. and Oberson, P. and Guinnard, O. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 145-147. \\ DOI: 10.1109/68.910516 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurements of the nonlinear coefficient of standard SMF, DSF, and DCF fibers using a self-aligned interferometer and a Faraday mirror}{https://boh/2001-PTL-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 1337-1339. \\ DOI: 10.1109/68.969900 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Morphological and optical characterization of GaN prepared by pulsed laser deposition}{https://boh/2000-SCT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Cazzanelli, M. and Trivelli, A. and Mariotto, G. and Castro, J. and Lunney, J. G. and Levy, J. \\ ``Surface & Coatings Technology'' Vol. 124 (2000) pp. 272-277. \\ DOI: 10.1016/s0257-8972(99)00657-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Optical absorption and photoluminescence properties of alpha-Si1-xNx : H films deposited by plasma-enhanced CVD}{https://boh/2000-PRB.pdf} \\ Giorgis$^\#$, F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 61 (2000) pp. 4693-4698. \\ DOI: 10.1103/PhysRevB.61.4693 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  All optical switching in a highly birefringent and a standard telecom fiber using a Faraday mirror stabilization scheme}{https://boh/2000-OC.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Optics Communications'' Vol. 182 (2000) pp. 335-341. \\ DOI: 10.1016/s0030-4018(00)00845-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurement of nonlinear polarization rotation in a highly birefringent optical fibre using a Faraday mirror}{https://boh/2000-JOA.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Journal of Optics a-Pure and Applied Optics'' Vol. 2 (2000) pp. 314-318. \\ DOI: 10.1088/1464-4258/2/4/313 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed gain measurements in Er-doped fibers with high resolution and accuracy using an optical frequency domain reflectometer}{https://boh/2000-JLT.pdf} \\ Wegmuller$^\#$, M. and Oberson, P. and Guinnard, O. and Huttner, B. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin, N. \\ ``Journal of Lightwave Technology'' Vol. 18 (2000) pp. 2127-2132. \\ DOI: 10.1109/50.908823 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Determination of nonlinear coefficient n(2)/A(eff) using self-aligned interferometer and Faraday mirror}{https://boh/2000-EL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Electronics Letters'' Vol. 36 (2000) pp. 886-888. \\ DOI: 10.1049/el:20000668 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman study of the phase transitions sequence in pure WO3 at high temperature and in HxWO3 with variable hydrogen content}{https://boh/1999-SSI.pdf} \\ Cazzanelli$^\#$, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzmin, A. and Purans, J. \\ ``Solid State Ionics'' Vol. 123 (1999) pp. 67-74. \\ DOI: 10.1016/s0167-2738(99)00101-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescence processes in amorphous hydrogenated silicon-nitride nanometric multilayers}{https://boh/1999-PRB.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 60 (1999) pp. 11572-11576. \\ DOI: 10.1103/PhysRevB.60.11572 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescent properties of GaN thin films prepared by pulsed laser deposition}{https://boh/1999-MSEB.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Cole, D. and Lunney, J. G. and Middleton, P. G. and Trager-Cowan, C. and O'Donnell, K. P. and Pavesi$^\#$, L. \\ ``Materials Science and Engineering B-Solid State Materials for Advanced Technology'' Vol. 59 (1999) pp. 137-140. \\ DOI: 10.1016/s0921-5107(98)00333-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Low-temperature polymorphism in tungsten trioxide powders and its dependence on mechanical treatments}{https://boh/1999-JSSC.pdf} \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto$^\#$, G. and Kuzmin, A. and Purans, J. \\ ``Journal of Solid State Chemistry'' Vol. 143 (1999) pp. 24-32. \\ DOI: 10.1006/jssc.1998.8061 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Temperature dependence of the photoluminescence of all-porous-silicon optical microcavities}{https://boh/1999-JAP.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Journal of Applied Physics'' Vol. 85 (1999) pp. 1760-1764. \\ DOI: 10.1063/1.369320 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Color Centres and Polymorphism in Pure WO(3) and Mixed (1-x)WO(3-y)center dot xReO(2) Powders}{https://boh/1999-INCS.pdf} \\ Cazzanelli$^\#$, E. and Mariotto, G. and {\bf Vinegoni, C.} and Kuzmin, A. and Purans, J. \\ ``Ionics'' Vol. 5 (1999) pp. 335-344. \\ DOI: 10.1007/bf02375997 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman spectroscopy and scanning electron microscopy investigation of annealed amorphous carbon-germanium films deposited by d.c. magnetron sputtering}{https://boh/1999-DRM.pdf} \\ Mariotto, G. and {\bf Vinegoni, C.} and Jacobsohn, L. G. and Freire$^\#$, F. L. \\ ``Diamond and Related Materials'' Vol. 8 (1999) pp. 668-672. \\ DOI: 10.1016/s0925-9635(98)00328-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Resonant second harmonic generation in ZnSe bulk microcavity}{https://boh/1999-APL.pdf} \\ Pellegrini, V. and Colombelli, R. and Carusotto, I. and Beltram, F. and Rubini, S. and Lantier, R. and Franciosi, A. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Applied Physics Letters'' Vol. 74 (1999) pp. 1945-1947. \\ DOI: 10.1063/1.123736 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Radiative emission properties of a-SiN : H based nanometric multilayers for light emitting devices}{https://boh/1998-JL.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Journal of Luminescence'' Vol. 80 (1998) pp. 423-427. \\ DOI: 10.1016/s0022-2313(98)00141-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  X-ray diffraction, extended x-ray absorption fine structure and Raman spectroscopy studies of WO3 powders and, (1-x)WO3-y center dot xReO(2) mixtures}{https://boh/1998-JAP.pdf} \\ Kuzmin$^\#$, A. and Purans, J. and Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. \\ ``Journal of Applied Physics'' Vol. 84 (1998) pp. 5515-5524. \\ DOI: 10.1063/1.368596 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Photoluminescence of localized excitons in pulsed-laser-deposited GaN}{https://boh/1998-APL.pdf} \\ Cazzanelli$^\#$, M. and Cole, D. and Donegan, J. F. and Lunney, J. G. and Middleton, P. G. and O'Donnell, K. P. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Applied Physics Letters'' Vol. 73 (1998) pp. 3390-3392. \\ DOI: 10.1063/1.122776 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Spatiotemporal multiplexed immunofluorescence imaging of living cells and tissues with bioorthogonal cycling of fluorescent probes}{https://boh/2022-NB.pdf} \\ Ko, J.A. and Wilkovitsch, M. and Oh, J. and Kohler, R.H. and Bolli, E. and Pittet, M.J. and {\bf Vinegoni, C.} and Sykes, D.B. and Mikula, H. and Weissleder, R. and Carlson$^\#$, J.C.T. \\ ``Nature Biotechnology'' Vol.  (2022) pp. online. \\ DOI: 10.1038/s41587-022-01339-6 PMID: 35654978 PMCID: \item \htmladdnormallink{\it  Neutrophils incite and macrophages avert electrical storm after myocardial infarction}{https://boh/2022-NCR-2.pdf} \\ Grune, J. and Lewis, A.J.M. and Yamazoe, M. and Hulsmans, M. and Rohde, D. and Xiao, L. and Zhang, S. and Ott, C. and Calcagno, D.M. and Zhou, Y. and Timm, K. and Shanmuganathan, M. and Pulous, F.E. and Schloss, M.J. and Foy, B.H. and Capen, D. and {\bf Vinegoni, C.} and Wojtkiewicz, G.R. and Iwamoto, I. and Grune, T. and Brown, D. and Higgins, J. and Ferreira, V.M. and Herring, N. and Channon, K.M. and Neubauer, S. and Oxford Acute Myocardial Infarction (OxAMI) Study and Sosnovik, D.E. and Milan, D.J. and Swirski, F.K. and King, K.R. and Aguirre, A.D. and Ellinor, P.T. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 649–664. \\ DOI: 10.1038/s44161-022-00094-w PMID:  PMCID: \item \htmladdnormallink{\it  Cerebrospinal fluid can exit into the skull bone marrow and instruct cranial hematopoiesis in mice with bacterial meningitis}{https://boh/2022-NN.PDF} \\ Pulous, F. E. and Cruz-Hernandez, J. C. and Yang, C. B. and Kaya, Z. and Paccalet, A. and Wojtkiewicz, G. and Capen, D. and Brown, D. and Wu, J. W. and Schloss, M. J. and {\bf Vinegoni, C.} and Richter, D. and Yamazoe, M. and Hulsmans, M. and Momin, N. and Grune, J. and Rohde, D. and McAlpine, C. S. and Panizzi, P. and Weissleder, R. and Kim, D. E. and Swirski, F. K. and Lin, C. P. and Moskowitz, M. A. and Nahrendorf, M. \\ ``Nature Neuroscience'' Vol. 25 (2022) pp. 567-+. \\ DOI: 10.1038/s41593-022-01060-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Bone marrow endothelial dysfunction promotes myeloid cell expansion in cardiovascular disease}{https://boh/2022-NCR.pdf} \\ Rohde, D. and Vandoorne, K. and Lee, I. H. and Grune, J. and Zhang, S. and McAlpine, C. S. and Schloss, M. J. and Nayar, R. and Courties, G. and Frodermann, V. and Wojtkiewicz, G. and Honold, L. and Chen, Q. and Schmidt, S. and Iwamoto, Y. and Sun, Y. and Cremer, S. and Hoyer, F. F. and Iborra-Egea, O. and Muñoz-Guijosa, C. and Ji, F. and Zhou, G. and Adams, R. H. and Wythe, J. D. and Hidalgo, J. and Watanabe, H. and Jung, Y. and van der Laan, A. M. and Piek, J. J. and Kfoury, Y. and Désogère, P. A. and {\bf Vinegoni, C.} and Dutta, P. and Sadreyev, R. I. and Caravan, P. and Bayes-Genis, A. and Libby, P. and Scadden, D. T. and Lin, C. P. and Naxerova, K. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 28-44. \\ DOI: 10.1038/s44161-021-00002-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Astrocytic interleukin-3 programs microglia and limits Alzheimer's disease}{https://boh/2021-NATURE.pdf} \\ McAlpine, C. S. and Park, J. and Griciuc, A. and Kim, E. and Choi, S. H. and Iwamoto, Y. and Kiss, M. G. and Christie, K. A. and {\bf Vinegoni, C.} and Poller, W. C. and Mindur, J. E. and Chan, C. T. and He, S. and Janssen, H. and Wong, L. P. and Downey, J. and Singh, S. and Anzai, A. and Kahles, F. and Jorfi, M. and Feruglio, P. F. and Sadreyev, R. I. and Weissleder, R. and Kleinstiver, B. P. and Nahrendorf, M. and Tanzi, R. E. and Swirski$^\#$, F. K. \\ ``Nature'' Vol. 595 (2021) pp. 701-+. \\ DOI: 10.1038/s41586-021-03734-6 PMID: 34262178 PMCID: PMC8934148\item \htmladdnormallink{\it  CytoPAN-Portable cellular analyses for rapid point-of-care cancer diagnosis}{https://boh/2020-STM.pdf} \\ Min, J. and Chin, L. K. and Oh, J. and Landeros, C. and {\bf Vinegoni, C.} and Lee, J. and Lee, S. J. and Park, J. Y. and Liu, A. Q. and Castro, C. M. and Lee, H. and Im, H. and Weissleder$^\#$, R. \\ ``Science Translational Medicine'' Vol. 12 (2020) pp. 14. \\ DOI: 10.1126/scitranslmed.aaz9746 PMID: 32759277 PMCID: PMC8217912\item \htmladdnormallink{\it  Fluorescence microscopy tensor imaging representations for large-scale dataset analysis}{https://boh/2020-SCIREP.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Feruglio$^\dag$, P. F. and Courties, G. and Schmidt, S. and Hulsmans, M. and Lee, S. and Wang, R. and Sosnovik, D. and Nahrendorf, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 10 (2020) pp. 15. \\ DOI: 10.1038/s41598-020-62233-2 PMID: 32221334 PMCID: PMC7101442\item \htmladdnormallink{\it  Extended dynamic range imaging for noise mitigation in fluorescence anisotropy imaging}{https://boh/2020-JBO.pdf} \\ Feruglio$^\dag$, P. F. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 25 (2020) pp. 13. \\ DOI: 10.1117/1.Jbo.25.8.086003 PMID: 32820624 PMCID: PMC7439791\item \htmladdnormallink{\it  Diminished Reactive Hematopoiesis and Cardiac Inflammation in a Mouse Model of Recurrent Myocardial Infarction}{https://boh/2020-JAMCC.pdf} \\ Cremer, S. and Schloss, M. J. and {\bf Vinegoni, C.} and Foy, B. H. and Zhang, S. and Rohde, D. and Hulsmans, M. and Feruglio, P. F. and Schmidt, S. and Wojtkiewicz, G. and Higgins, J. M. and Weissleder, R. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 75 (2020) pp. 901-915. \\ DOI: 10.1016/j.jacc.2019.12.056 PMID: 32130926 PMCID: PMC7254576\item \htmladdnormallink{\it  Characterization of single microvesicles in plasma from glioblastoma patients}{https://boh/2019-NO.pdf} \\ Fraser, K. and Jo, A. and Giedt, J. and {\bf Vinegoni, C.} and Yang, K. S. and Peruzzi, P. and Chiocca, E. A. and Breakefield, X. O. and Lee, H. and Weissleder$^\#$, R. \\ ``Neuro-Oncology'' Vol. 21 (2019) pp. 606-615. \\ DOI: 10.1093/neuonc/noy187 PMID: 30561734 PMCID: 6502493\item \htmladdnormallink{\it  High Dynamic Range Fluorescence Imaging}{https://boh/2019-JSTQE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 25 (2019) pp. 7. \\ DOI: 10.1109/jstqe.2018.2881608 PMID: 31598059 PMCID: PMC6785194\item \htmladdnormallink{\it  Fluorescence anisotropy imaging in drug discovery}{https://boh/2019-ADDR.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Gryczynski, I. and Mazitschek, R. and Weissleder, R. \\ ``Advanced Drug Delivery Reviews'' Vol. 151 (2019) pp. 262-288. \\ DOI: 10.1016/j.addr.2018.01.019 PMID: 29410158 PMCID: 6072632\item \htmladdnormallink{\it  The anti-tumor diterpene oridonin is a direct inhibitor of Nucleolin in cancer cells}{https://boh/2018-SCIREP.pdf} \\ Vasaturo, M. and Cotugno, R. and Fiengo, L. and {\bf Vinegoni, C.} and Dal Piaz, F. and De Tommasi$^\#$, N. \\ ``Scientific Reports'' Vol. 8 (2018) pp. 13. \\ DOI: 10.1038/s41598-018-35088-x PMID: 30425290 PMCID: 6233161\item \htmladdnormallink{\it  Direct vascular channels connect skull bone marrow and the brain surface enabling myeloid cell migration}{https://boh/2018-NATNEURO.pdf} \\ Herisson, F. and Frodermann, V. and Courties, G. and Rohde, D. and Sun, Y. and Vandoorne, K. and Wojtkiewicz, G. R. and Masson, G. S. and {\bf Vinegoni, C.} and Kim, J. and Kim, D. E. and Weissleder, R. and Swirski, F. K. and Moskowitz, M. A. and Nahrendorf$^\#$, M. \\ ``Nature Neuroscience'' Vol. 21 (2018) pp. 1209-+. \\ DOI: 10.1038/s41593-018-0213-2 PMID: 30150661 PMCID: PMC6148759 \item \htmladdnormallink{\it  Cardiac macrophages promote diastolic dysfunction}{https://boh/2018-JEM.pdf} \\ Hulsmans, M. and Sager, H. B. and Roh, J. D. and Valero-Munoz, M. and Houstis, N. E. and Iwamoto, Y. and Sun, Y. and Wilson, R. M. and Wojtkiewicz, G. and Tricot, B. and Osborne, M. T. and Hung, J. and {\bf Vinegoni, C.} and Naxerova, K. and Sosnovik, D. E. and Zile, M. R. and Bradshaw, A. D. and Liao, R. and Tawakol, A. and Weissleder, R. and Rosenzweig, A. and Swirski, F. K. and Sam, F. and Nahrendorf$^\#$, M. \\ ``Journal of Experimental Medicine'' Vol. 215 (2018) pp. 423-440. \\ DOI: 10.1084/jem.20171274 PMID: 29339450 PMCID: PMC3366498\item \htmladdnormallink{\it  Imaging the Vascular Bone Marrow Niche During Inflammatory Stress}{https://boh/2018-CIRCRES.pdf} \\ Vandoorne, K. and Rohde, D. and Kim, H. Y. and Courties, G. and Wojtkiewicz, G. and Honold, L. and Hoyer, F. F. and Frodermann, V. and Nayar, R. and Herisson, F. and Jung, Y. and Desogere, P. A. and {\bf Vinegoni, C.} and Caravan, P. and Weissleder, R. and Sosnovik, D. E. and Lin, C. P. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Circulation Research'' Vol. 123 (2018) pp. 415-427. \\ DOI: 10.1161/circresaha.118.313302 PMID: 29980569 PMCID: 6202141\item \htmladdnormallink{\it  Design and Development of Fluorescent Vemurafenib Analogs for In Vivo Imaging}{https://boh/2017-THERA.pdf} \\ Mikula, H. and Stapleton, S. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Theranostics'' Vol. 7 (2017) pp. 1257-1265. \\ DOI: 10.7150/thno.18238 PMID: 28435463 PMCID: PMC5399591\item \htmladdnormallink{\it  Measurement of drug-target engagement in live cells by two-photon fluorescence anisotropy imaging}{https://boh/2017-NP.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Brand, C. and Lee, S. and Nibbs, A. E. and Stapleton, S. and Shah, S. and Gryczynski, I. and Reiner, T. and Mazitschek, R. and Weissleder, R. \\ ``Nature Protocols'' Vol. 12 (2017) pp. 1472-1497. \\ DOI: 10.1038/nprot.2017.043 PMID: 28686582 PMCID: PMC5928516\item \htmladdnormallink{\it  Quantitating drug-target engagement in single cells in vitro and in vivo}{https://boh/2017-NCBIOL.pdf} \\ Dubach, J. M. and Kim, E. and Yang, K. and Cuccarese, M. and Giedt, R. J. and Meirnetis, L. G. and {\bf Vinegoni$^\#$, C.} and Weissleder$^\#$, R. \\ ``Nature Chemical Biology'' Vol. 13 (2017) pp. 168-173. \\ DOI: 10.1038/nchembio.2248 PMID: 27918558 PMCID: PMC5630128\item \htmladdnormallink{\it  Motion characterization scheme to minimize motion artifacts in intravital microscopy}{https://boh/2017-JBO.pdf} \\ Lee, S. and Courties, G. and Nahrendorf, M. and Weissleder, R. and {\bf Vinegoni$^\#$, C.} \\ ``Journal of Biomedical Optics'' Vol. 22 (2017) pp. 7. \\ DOI: 10.1117/1.Jbo.22.3.036005 PMID: 28253383 PMCID: PMC5333764\item \htmladdnormallink{\it  Macrophages Facilitate Electrical Conduction in the Heart}{https://boh/2017-CELL.pdf} \\ Hulsmans, M. and Clauss, S. and Xiao, L. and Aguirre, A. D. and King, K. R. and Hanley, A. and Hucker, W. J. and Wulfers, E. M. and Seemann, G. and Courties, G. and Iwamoto, Y. and Sun, Y. and Savol, A. J. and Sager, H. B. and Lavine, K. J. and Fishbein, G. A. and Capen, D. E. and Da Silva, N. and Miquerol, L. and Wakimoto, H. and Seidman, C. E. and Seidman, J. G. and Sadreyev, R. I. and Naxerova, K. and Mitchell, R. N. and Brown, D. and Libby, P. and Weissleder, R. and Swirski, F. K. and Kohl, P. and {\bf Vinegoni, C.} and Milan, D. J. and Ellinor, P. T. and Nahrendorf$^\#$, M. \\ ``Cell'' Vol. 169 (2017) pp. 510-+. \\ DOI: 10.1016/j.cell.2017.03.050 PMID: 28431249 PMCID: PMC5474950\item \htmladdnormallink{\it  Transparent Electrophysiology Microelectrodes and Interconnects from Meta Nanomesh}{https://boh/2017-ACSN.pdf} \\ Seo, K. J. and Qiang, Y. and Bilgin, I. and Kar, S. and {\bf Vinegoni, C.} and Weissleder, R. and Fang$^\#$, H. \\ ``Acs Nano'' Vol. 11 (2017) pp. 4365-4372. \\ DOI: 10.1021/acsnano.7b01995 PMID: 28391679 PMCID: N/A\item \htmladdnormallink{\it  Two-photon imaging of pancreatic beta cells in real time in vivo}{https://boh/2016-TECHNOL.pdf} \\ Clardy, S. M. and Kohler, R. and {\bf Vinegoni, C.} and Iwamoto, Y. and Keliher, E. and Weissleder$^\#$, R. \\ ``Technology'' Vol. 4 (2016) pp. 130-34. \\ DOI: 10.1142/S2339547816200028 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  RNAi targeting multiple cell adhesion molecules reduces immune cell recruitment and vascular inflammation after myocardial infarction}{https://boh/2016-STM.pdf} \\ Sager, H. B. and Dutta, P. and Dahlman, J. E. and Hulsmans, M. and Courties, G. and Sun, Y. and Heidt, T. and {\bf Vinegoni, C.} and Borodovsky, A. and Fitzgerald, K. and Wojtkiewicz, G. R. and Iwamoto, Y. and Tricot, B. and Khan, O. F. and Kauffman, K. J. and Xing, Y. P. and Shaw, T. E. and Libby, P. and Langer, R. and Weissleder, R. and Swirski, F. K. and Anderson, D. G. and Nahrendorf$^\#$, M. \\ ``Science Translational Medicine'' Vol. 8 (2016) pp. 11. \\ DOI: 10.1126/scitranslmed.aaf1435 PMID: 27280687 PMCID: PMC5125383\item \htmladdnormallink{\it  Computational imaging reveals mitochondrial morphology as a biomarker of cancer phenotype and drug response}{https://boh/2016-SCIREP.pdf} \\ Giedt, R. J. and Fumene Feruglio, P. and Pathania, D. and Yang, K. S. and Kilcoyne, A. and {\bf Vinegoni, C.} and Mitchison, T. J. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 6 (2016) pp. 10. \\ DOI: 10.1038/srep32985 PMID: 27609668 PMCID: PMC5017129\item \htmladdnormallink{\it  Real-time high dynamic range laser scanning microscopy}{https://boh/2016-NCOMM-2.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Swisher$^\dag$, C. L. and Fumene Feruglio$^\dag$, P. and Giedt, R. J. and Rousso, D. L. and Stapleton, S. and Weissleder, R. \\ ``Nature Communications'' Vol. 7 (2016) pp. 13. \\ DOI: 10.1038/ncomms11077 PMID: 27032979 PMCID: PMC4821995\item \htmladdnormallink{\it  Tyrosine kinase-mediated axial motility of basal cells revealed by intravital imaging}{https://boh/2016-NCOMM-1.pdf} \\ Roy, J. and Kim, B. and Hill, E. and Visconti, P. and Krapf, D. and {\bf Vinegoni, C.} and Weissleder, R. and Brown, D. and Breton$^\#$, S. \\ ``Nature Communications'' Vol. 7 (2016) pp. 11. \\ DOI: 10.1038/ncomms10666 PMID: 26868824 PMCID: PMC4754344\item \htmladdnormallink{\it  Two-Photon Fluorescence Anisotropy Microscopy for Imaging and Direct Measurement of Intracellular Drug Target Engagement}{https://boh/2016-IEEE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 22 (2016) pp. 7. \\ DOI: 10.1109/jstqe.2015.2501384 PMID: 27440991 PMCID: PMC4946648\item \htmladdnormallink{\it  Rapid, high efficiency isolation of pancreatic beta-cells}{https://boh/2015-SREP.pdf} \\ Clardy, S. M. and Mohan, J. F. and {\bf Vinegoni, C.} and Keliher, E. J. and Iwamoto, Y. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 5 (2015) pp. 9. \\ DOI: 10.1038/srep13681 PMID: 26330153 PMCID: PMC4557033\item \htmladdnormallink{\it  Imaging the beating heart in the mouse using intravital microscopy techniques}{https://boh/2015-NPROT.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Aguirre$^\dag$, A. D. and Lee, S. and Weissleder, R. \\ ``Nature Protocols'' Vol. 10 (2015) pp. 1802-1819. \\ DOI: 10.1038/nprot.2015.119 PMID: 26492138 PMCID: PMC5380003\item \htmladdnormallink{\it  New techniques for motion-artifact-free in vivo cardiac microscopy}{https://boh/2015-FPHYS.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Aguirre, A. D. and Weissleder, R. \\ ``Frontiers in Physiology'' Vol. 6 (2015) pp. 12. \\ DOI: 10.3389/fphys.2015.00147 PMID: 26029116 PMCID: PMC4428079\item \htmladdnormallink{\it  Advances in measuring single-cell pharmacology in vivo}{https://boh/2015-DDT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Thurber, G. M. and Miller, M. A. and Mazitschek, R. and Weissleder, R. \\ ``Drug Discovery Today'' Vol. 20 (2015) pp. 1087-1092. \\ DOI: 10.1016/j.drudis.2015.05.011 PMID: 26024776 PMCID: PMC4567932\item \htmladdnormallink{\it  Myocardial Infarction Activates CCR2(+) Hematopoietic Stem and Progenitor Cells}{https://boh/2015-CSC.pdf} \\ Dutta, P. and Sager, H. B. and Stengel, K. R. and Naxerova, K. and Courties, G. and Saez, B. and Silberstein, L. and Heidt, T. and Sebas, M. and Sun, Y. and Wojtkiewicz, G. and Fumene Feruglio, P. and King, K. and Baker, J. N. and van der Laan, A. M. and Borodovsky, A. and Fitzgerald, K. and Hulsmans, M. and Hoyer, F. and Iwamoto, Y. and {\bf Vinegoni, C.} and Brown, D. and Di Carli, M. and Libby, P. and Hiebert, S. W. and Scadden, D. T. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Cell Stem Cell'' Vol. 16 (2015) pp. 477-487. \\ DOI: 10.1016/j.stem.2015.04.008 PMID: 25957903 PMCID: PMC4426344\item \htmladdnormallink{\it  Automated motion artifact removal for intravital microscopy, without a priori information}{https://boh/2014-SR.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Sebas, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 4 (2014) pp. 9. \\ DOI: 10.1038/srep04507 PMID: 24676021 PMCID: PMC3968488\item \htmladdnormallink{\it  Intravital imaging of cardiac function at the single-cell level}{https://boh/2014-PNAS.pdf} \\ Aguirre, A. D. and {\bf Vinegoni$^\#$, C.} and Sebas, M. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 111 (2014) pp. 11257-11262. \\ DOI: 10.1073/pnas.1401316111 PMID: 25053815 PMCID: PMC4128110\item \htmladdnormallink{\it  Steady state anisotropy two-photon microscopy resolves multiple, spectrally similar fluorophores, enabling in vivo multilabel imaging}{https://boh/2014-OL.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Optics Letters'' Vol. 39 (2014) pp. 4482-4485. \\ DOI: 10.1364/ol.39.004482 PMID: 25078208 PMCID: PMC4341989\item \htmladdnormallink{\it  Chronic variable stress activates hematopoietic stem cells}{https://boh/2014-NM.pdf} \\ Heidt, T. and Sager, H. B. and Courties, G. and Dutta, P. and Iwamoto, Y. and Zaltsman, A. and von zur Muhlen, C. and Bode, C. and Fricchione, G. L. and Denninger, J. and Lin, C. P. and {\bf Vinegoni, C.} and Libby, P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature Medicine'' Vol. 20 (2014) pp. 754-758. \\ DOI: 10.1038/nm.3589 PMID: 24952646 PMCID: PMC4087061\item \htmladdnormallink{\it  In vivo imaging of specific drug-target binding at subcellular resolution}{https://boh/2014-NC.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Mazitschek, R. and Fumene Feruglio, P. and Cameron, L. A. and Weissleder, R. \\ ``Nature Communications'' Vol. 5 (2014) pp. 9. \\ DOI: 10.1038/ncomms4946 PMID: 24867710 PMCID: PMC4362617\item \htmladdnormallink{\it  Advanced Motion Compensation Methods for Intravital Optical Microscopy}{https://boh/2014-IEEE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 20 (2014) pp. 9. \\ DOI: 10.1109/jstqe.2013.2279314 PMID: 24273405 PMCID: PMC3832946\item \htmladdnormallink{\it  Perinatal health and translational medicine}{https://boh/2013-JHGD.pdf} \\ Figueiredo, J. L. and {\bf Vinegoni, C.} and De Abreu, L. C. \\ ``Journal of Human Growth and Development'' Vol. 23 (2013) pp. 125-127. \\ DOI: 10.7322/jhgd.61318 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Sequential average segmented microscopy for high signal-to-noise ratio motion-artifact-free in vivo heart imaging}{https://boh/2013-BOE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Marzola, P. and Nahrendorf, M. and Weissleder, R. \\ ``Biomedical Optics Express'' Vol. 4 (2013) pp. 2095-2106. \\ DOI: 10.1364/boe.4.002095 PMID: 24156067 PMCID: PMC3799669\item \htmladdnormallink{\it  Noise suppressed, multifocus image fusion for enhanced intraoperative navigation}{https://boh/2013-BIOPHTNCS.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Fexon, L. and Thurber, G. and Sbarbati, A. and Weissleder, R. \\ ``Journal of Biophotonics'' Vol. 6 (2013) pp. 363-370. \\ DOI: 10.1002/jbio.201200086 PMID: 22887724 PMCID: PMC3779878\item \htmladdnormallink{\it  Implantable microenvironments to attract hematopoietic stem/cancer cells}{https://boh/2012-PNAS.pdf} \\ Lee, J. and Li, M. and Milwid, J. and Dunham, J. and {\bf Vinegoni, C.} and Gorbatov, R. and Iwamoto, Y. and Wang, F. J. and Shen, K. Y. and Hatfield, K. and Enger, M. and Shafiee, S. and McCormack, E. and Ebert, B. L. and Weissleder, R. and Yarmush, M. L. and Parekkadan$^\#$, B. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 109 (2012) pp. 19638-19643. \\ DOI: 10.1073/pnas.1208384109 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Mapping Molecular Agents Distributions in Whole Mice Hearts Using Born-Normalized Optical Projection Tomography}{https://boh/2012-PLOSONE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio$^\dag$, P. and Razansky, D. and Gorbatov, R. and Ntziachristos, V. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Plos One'' Vol. 7 (2012) pp. 9. \\ DOI: 10.1371/journal.pone.0034427 PMID: 22509302 PMCID: PMC3324534\item \htmladdnormallink{\it  Imaging Therapeutic PARP Inhibition In Vivo through Bioorthogonally Developed Companion Imaging Agents}{https://boh/2012-NEOPLASIA.pdf} \\ Reiner, T. and Lacy, J. and Keliher, E. J. and Yang, K. S. and Ullal, A. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Neoplasia'' Vol. 14 (2012) pp. 169-+. \\ DOI: 10.1593/neo.12414 PMID: 22496617 PMCID: PMC3323895\item \htmladdnormallink{\it  Real-time in vivo imaging of the beating mouse heart at microscopic resolution}{https://boh/2012-NC.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Fexon, L. and Gorbatov, R. and Pivoravov, M. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Nature Communications'' Vol. 3 (2012) pp. 8. \\ DOI: 10.1038/ncomms2060 PMID: 22968700 PMCID: PMC3622400\item \htmladdnormallink{\it  Myocardial infarction accelerates atherosclerosis}{https://boh/2012-NATURE.pdf} \\ Dutta, P. and Courties, G. and Wei, Y. and Leuschner, F. and Gorbatov, R. and Robbins, C. S. and Iwamoto, Y. and Thompson, B. and Carlson, A. L. and Heidt, T. and Majmudar, M. D. and Lasitschka, F. and Etzrodt, M. and Waterman, P. and Waring, M. T. and Chicoine, A. T. and van der Laan, A. M. and Niessen, H. W. M. and Piek, J. J. and Rubin, B. B. and Butany, J. and Stone, J. R. and Katus, H. A. and Murphy, S. A. and Morrow, D. A. and Sabatine, M. S. and {\bf Vinegoni, C.} and Moskowitz, M. A. and Pittet, M. J. and Libby, P. and Lin, C. P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature'' Vol. 487 (2012) pp. 325-329. \\ DOI: 10.1038/nature11260 PMID: 22763456 PMCID: PMC3401326\item \htmladdnormallink{\it  Improved intravital microscopy via synchronization of respiration and holder stabilization}{https://boh/2012-JBO.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 17 (2012) pp. 8. \\ DOI: 10.1117/1.Jbo.17.9.096018 PMID: 23085919 PMCID: PMC3449295\item \htmladdnormallink{\it  PET/MRI of Inflammation in Myocardial Infarction}{https://boh/2012-JACC.pdf} \\ Lee, W. W. and Marinelli, B. and van der Laan, A. M. and Sena, B. F. and Gorbatov, R. and Leuschner, F. and Dutta, P. and Iwamoto, Y. and Ueno, T. and Begieneman, M. P. V. and Niessen, H. W. M. and Piek, J. J. and {\bf Vinegoni, C.} and Pittet, M. J. and Swirski, F. K. and Tawakol, A. and Di Carli, M. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 59 (2012) pp. 153-163. \\ DOI: 10.1016/j.jacc.2011.08.066 PMID: 22222080 PMCID: PMC3257823\item \htmladdnormallink{\it  Motion compensation using a suctioning stabilizer for intravital microscopy}{https://boh/2012-INTRVTL.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Gorbatov, R. and Weissleder, R. \\ ``Intravital'' Vol. 1 (2012) pp. 115. \\ DOI: 10.4161/intv.23017 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Deep Tissue Optical and Optoacoustic Molecular Imaging Technologies for Pre-Clinical Research and Drug Discovery}{https://boh/2012-CPB.pdf} \\ Razansky$^\#$, D. and Deliolanis, N. C. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Current Pharmaceutical Biotechnology'' Vol. 13 (2012) pp. 504-522. \\ DOI: 10.2174/138920112799436258 PMID: 22216767 PMCID: N/A\item \htmladdnormallink{\it  In Vivo Imaging of Drug-Induced Mitochondrial Outer Membrane Permeabilization at Single-Cell Resolution}{https://boh/2012-CNCRRES.pdf} \\ Earley, S. and {\bf Vinegoni, C.} and Dunham, J. and Gorbatov, R. and Fumene Feruglio, P. and Weissleder$^\#$, R. \\ ``Cancer Research'' Vol. 72 (2012) pp. 2949-2956. \\ DOI: 10.1158/0008-5472.Can-11-4096 PMID: 22505651 PMCID: PMC3603290\item \htmladdnormallink{\it  Optochemogenetics (OCG) Allows More Precise Control of Genetic Engineering in Mice with CreER regulators}{https://boh/2012-BIOCHEM.pdf} \\ Lu, X. and Agasti, S. S. and {\bf Vinegoni, C.} and Waterman, P. and DePinho, R. A. and Weissleder$^\#$, R. \\ ``Bioconjugate Chemistry'' Vol. 23 (2012) pp. 1945-1951. \\ DOI: 10.1021/bc300319c PMID: 22917215 PMCID: PMC3775343\item \htmladdnormallink{\it  Bioorthogonal Imaging of Aurora Kinase A in Live Cells}{https://boh/2012-AC.pdf} \\ Yang, K. S. and Budin, G. and Reiner, T. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Angewandte Chemie-International Edition'' Vol. 51 (2012) pp. 6598-6603. \\ DOI: 10.1002/anie.201200994 PMID: 22644700 PMCID: PMC3523717\item \htmladdnormallink{\it  Indocyanine Green Enables Near-Infrared Fluorescence Imaging of Lipid-Rich, Inflamed Atherosclerotic Plaques}{https://boh/2011-STM.pdf} \\ {\bf Vinegoni, C.} and Botnaru, I. and Aikawa, E. and Calfon, M. A. and Iwamoto, Y. and Folco, E. J. and Ntziachristos, V. and Weissleder, R. and Libby, P. and Jaffer$^\#$, F. A. \\ ``Science Translational Medicine'' Vol. 3 (2011) pp. 9. \\ DOI: 10.1126/scitranslmed.3001577 PMID: 21613624 PMCID: PMC3112179\item \htmladdnormallink{\it  Accurate measurement of pancreatic islet beta-cell mass using a second-generation fluorescent exendin-4 analog}{https://boh/2011-PNAS.pdf} \\ Reiner, T. and Thurber, G. and Gaglia, J. and {\bf Vinegoni, C.} and Liew, C. W. and Upadhyay, R. and Kohler, R. H. and Li, L. and Kulkarni, R. N. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 108 (2011) pp. 12815-12820. \\ DOI: 10.1073/pnas.1109859108 PMID: 21768367 PMCID: PMC3150928\item \htmladdnormallink{\it  A multimodal approach for tracing lateralisation along the olfactory pathway in the honeybee through electrophysiological recordings, morpho-functional imaging, and behavioural studies}{https://boh/2011-EB.pdf} \\ Haase, A. and Rigosi, E. and Frasnelli, E. and Trona, F. and Tessarolo, F. and {\bf Vinegoni, C.} and Anfora, G. and Vallortigara, G. and Antolini$^\#$, R. \\ ``European Biophysics Journal with Biophysics Letters'' Vol. 40 (2011) pp. 1247-1258. \\ DOI: 10.1007/s00249-011-0748-6 PMID: 21956452 PMCID: PMC3366498\item \htmladdnormallink{\it  Searching for anatomical correlates of olfactory lateralization in the honeybee antennal lobes: A morphological and behavioural study}{https://boh/2011-BBR.pdf} \\ Rigosi$^\#$, E. and Frasnelli, E. and {\bf Vinegoni, C.} and Antolini, R. and Anfora, G. and Vallortigara, G. and Haase, A. \\ ``Behavioural Brain Research'' Vol. 221 (2011) pp. 290-294. \\ DOI: 10.1016/j.bbr.2011.03.015 PMID: 21402106 PMCID: PMC3089663\item \htmladdnormallink{\it  Intraoperative Near-infrared Fluorescent Cholangiography (NIRFC) in Mouse Models of Bile Duct Injury: Reply}{https://boh/2010-WJS.pdf} \\ Figueiredo, J. L. and Nahrendorf, M. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``World Journal of Surgery'' Vol. 35 (2011) pp. 694-695. \\ DOI: 10.1007/s00268-010-0728-5 PMID: 20645091 PMCID: N/A\item \htmladdnormallink{\it  Hybrid PET-optical imaging using targeted probes}{https://boh/2010-PNAS.pdf} \\ Nahrendorf$^{\dag \#}$, M. and Keliher$^\dag$, E. and Marinelli, B. and Waterman, P. and Fumene Feruglio, P. and Fexon, L. and Pivovarov, M. and Swirski, F. K. and Pittet, M. J. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 107 (2010) pp. 7910-7915. \\ DOI: 10.1073/pnas.0915163107 PMID: 20385821 PMCID: PMC2867879\item \htmladdnormallink{\it  Block matching 3D random noise filtering for absorption optical projection tomography}{https://boh/2010-PMB.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Gros, J. and Sbarbati, A. and Weissleder, R. \\ ``Physics in Medicine and Biology'' Vol. 55 (2010) pp. 5401-5415. \\ DOI: 10.1088/0031-9155/55/18/009 PMID: 20736500 PMCID: PMC2934766\item \htmladdnormallink{\it  Imaging of molecular probe activity with Born-normalized fluorescence optical projection tomography}{https://boh/2010-OL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Cortez-Retamozo, V. and Razansky, D. and Medoff, B. D. and Ntziachristos, V. and Sbarbati, A. and Pittet, M. and Weissleder, R. \\ ``Optics Letters'' Vol. 35 (2010) pp. 1088-1090. \\ DOI: 10.1364/ol.35.001088 PMID: 20364226 PMCID: PMC2900933\item \htmladdnormallink{\it  Intravascular near-infrared fluorescence molecular imaging of atherosclerosis: toward coronary arterial visualization of biologically high-risk plaques}{https://boh/2010-JBO.pdf} \\ Calfon, M. A. and {\bf Vinegoni, C.} and Ntziachristos, V. and Jaffer$^\#$, F. A. \\ ``Journal of Biomedical Optics'' Vol. 15 (2010) pp. 6. \\ DOI: 10.1117/1.3280282 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  WNT5A/JNK and FGF/MAPK Pathways Regulate the Cellular Events Shaping the Vertebrate Limb Bud}{https://boh/2010-CB.pdf} \\ Gros, J. and Hu, J. K. H. and {\bf Vinegoni, C.} and Fumene Feruglio, P. and Weissleder, R. and Tabin$^\#$, C. J. \\ ``Current Biology'' Vol. 20 (2010) pp. 1993-2002. \\ DOI: 10.1016/j.cub.2010.09.063 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  In-vivo two-photon imaging of the honey bee antennal lobe}{https://boh/2010-BOEX.pdf} \\ Haase, A. and Rigosi, E. and Trona, F. and Anfora, G. and Vallortigara, G. and Antolini, R. and {\bf Vinegoni$^\#$, C.} \\ ``Biomedical Optics Express'' Vol. 2 (2011) pp. 131-138. \\ DOI: 10.1364/boe.2.000131 PMID: 21326643 PMCID: PMC3028488\item \htmladdnormallink{\it  Imaging of mesoscopic-scale organisms using selective-plane optoacoustic tomography}{https://boh/2009-PMB.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Physics in Medicine and Biology'' Vol. 54 (2009) pp. 2769-2777. \\ DOI: 10.1088/0031-9155/54/9/012 PMID: 19369709 PMCID: N/A\item \htmladdnormallink{\it  Normalized Born ratio for fluorescence optical projection tomography}{https://boh/2009-OL-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 319-321. \\ DOI: 10.1364/ol.34.000319 PMID: 19183644 PMCID: PMC2771918\item \htmladdnormallink{\it  Transillumination fluorescence imaging in mice using biocompatible upconverting nanoparticles}{https://boh/2009-OL-1.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Razansky$^\dag$, D. and Hilderbrand, S. A. and Shao, F. W. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 2566-2568. \\ DOI: 10.1364/ol.34.002566 PMID: 19724491 PMCID: PMC2749971\item \htmladdnormallink{\it  Diffractionless beam in free space with adiabatic changing refractive index in a single mode tapered slab waveguide}{https://boh/2009-OE-2.pdf} \\ Tsai$^\#$, C. C. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 21723-21731. \\ DOI: 10.1364/oe.17.021723 PMID: 19997414 PMCID: PMC2805120\item \htmladdnormallink{\it  High throughput transmission optical projection tomography using low cost graphics processing unit}{https://boh/2009-OE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fexon, L. and Fumene Feruglio, P. and Pivovarov, M. and Figueiredo, J. L. and Nahrendorf, M. and Pozzo, A. and Sbarbati, A. and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 22320-22332. \\ DOI: 10.1364/oe.17.022320 PMID: 20052155 PMCID: PMC2805020\item \htmladdnormallink{\it  Multispectral opto-acoustic tomography of deep-seated fluorescent proteins in vivo}{https://boh/2009-NATPHOT.pdf} \\ Razansky$^\#$, D. and Distel, M. and {\bf Vinegoni, C.} and Ma, R. and Perrimon, N. and Koster, R. W. and Ntziachristos$^\#$, V. \\ ``Nature Photonics'' Vol. 3 (2009) pp. 412-417. \\ DOI: 10.1038/nphoton.2009.98 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Mesoscopic Fluorescence Tomography for In-vivo Imaging of Developing Drosophila}{https://boh/2009-JOVE-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Pitsouli, C. and Perrimon, N. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1510. \\ DOI: 10.3791/1510 PMID: 19696720 PMCID: PMC2736679\item \htmladdnormallink{\it  Born normalization for fluorescence optical projection tomography for whole heart imaging}{https://boh/2009-JOVE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Fexon, L. and Pivoravov, M. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1389. \\ DOI: 10.3791/1389 PMID: 19578329 PMCID: PMC2794886\item \htmladdnormallink{\it  Unprecedent in vivo views at the mesoscopic scale}{https://boh/2009-BOW.pdf} \\ Razansky, R. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``BioOptics World'' Vol. 2 (2009) pp. 22. \\ DOI: N/A PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Polarization-sensitive optoacoustic tomography of optically diffuse tissues}{https://boh/2008-OL.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Optics Letters'' Vol. 33 (2008) pp. 2308-2310. \\ DOI: 10.1364/ol.33.002308 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  In vivo imaging of Drosophila melanogaster pupae with mesoscopic fluorescence tomography}{https://boh/2008-NM.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Pitsouli$^\dag$, C. and Razansky$^\dag$, D. and Perrimon, N. and Ntziachristos, V. \\ ``Nature Methods'' Vol. 5 (2008) pp. 45-47. \\ DOI: 10.1038/nmeth1149 PMID: 18066071 PMCID: N/A\item \htmladdnormallink{\it  Real-time assessment of inflammation and treatment response in a mouse model of allergic airway inflammation}{https://boh/2008-JCI.pdf} \\ Cortez-Retamozo, V. and Swirski, F. K. and Waterman, P. and Yuan, H. and Figueiredo, J. L. and Newton, A. P. and Upadhyay, R. and {\bf Vinegoni, C.} and Kohler, R. and Blois, J. and Smith, A. and Nahrendorf, M. and Josephson, L. and Weissleder, R. and Pittet$^\#$, M. J. \\ ``Journal of Clinical Investigation'' Vol. 118 (2008) pp. 4058-4066. \\ DOI: 10.1172/jci36335 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  Real-Time Catheter Molecular Sensing of Inflammation in Proteolytically Active Atherosclerosis}{https://boh/2008-CRCLT.pdf} \\ Jaffer, F. A. and {\bf Vinegoni, C.} and John, M. C. and Aikawa, E. and Gold, H. K. and Finn, A. V. and Ntziachristos, V. and Libby, P. and Weissleder$^\#$, R. \\ ``Circulation'' Vol. 118 (2008) pp. 1802-1809. \\ DOI: 10.1161/circulationaha.108.785881 PMID: 18852366 PMCID: PMC2729441\item \htmladdnormallink{\it  Multispectral photoacoustic imaging of fluorochromes in small animals}{https://boh/2007-OL.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``Optics Letters'' Vol. 32 (2007) pp. 2891-2893. \\ DOI: 10.1364/ol.32.002891 PMID: 17909608 PMCID: N/A\item \htmladdnormallink{\it  Imaging cellular responses to mechanical stimuli within three-dimensional tissue constructs}{https://boh/2007-MRT.pdf} \\ Tan, W. and {\bf Vinegoni, C.} and Norman, J. J. and Desai, T. A. and Boppart$^\#$, S. A. \\ ``Microscopy Research and Technique'' Vol. 70 (2007) pp. 361-371. \\ DOI: 10.1002/jemt.20420 PMID: 17262787 PMCID: N/A\item \htmladdnormallink{\it  High-spectral-resolution coherent anti-Stokes Raman scattering with interferometric ally detected broadband chirped pulses}{https://boh/2006-OL-2.pdf} \\ Jones, G. W. and Marks, D. L. and {\bf Vinegoni, C.} and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1543-1545. \\ DOI: 10.1364/ol.31.001543 PMID: 16642166 PMCID: N/A\item \htmladdnormallink{\it  Spectroscopic spectral-domain optical coherence microscopy}{https://boh/2006-OL-1.pdf} \\ Xu, C. Y. and {\bf Vinegoni, C.} and Ralston, T. S. and Luo, W. and Tan, W. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1079-1081. \\ DOI: 10.1364/ol.31.001079 PMID: 16625909 PMCID: N/A\item \htmladdnormallink{\it  Integrated structural and functional optical imaging combining spectral-domain optical coherence and multiphoton microscopy}{https://boh/2006-APL.pdf} \\ {\bf Vinegoni, C.} and Ralston, T. and Tan, W. and Luo, W. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 88 (2006) pp. 3. \\ DOI: 10.1063/1.2171477 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Nonlinear Interferometric Vibrational Imaging. efficient detection of Coherent Anti-Stokes Raman Scattering}{https://boh/2005-OPN.pdf} \\ McAlpine, C. S. and Marks, D. and {\bf Vinegoni, C.} and Bredfeldt, J. and Boppart$^\#$, S.A. \\ ``Optics & Photonics News'' Vol. 16 (2005) pp. 23. \\ DOI: 10.1364/OPN.16.12.000023 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Molecularly sensitive optical coherence tomography}{https://boh/2005-OL.pdf} \\ Bredfeldt, J. S. and {\bf Vinegoni, C.} and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 30 (2005) pp. 495-497. \\ DOI: 10.1364/ol.30.000495 PMID: 15789714 PMCID: N/A\item \htmladdnormallink{\it  Nonlinear optical contrast enhancement for optical coherence tomography}{https://boh/2004-OE.pdf} \\ {\bf Vinegoni, C.} and Bredfeldt, J. S. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Express'' Vol. 12 (2004) pp. 331-341. \\ DOI: 10.1364/opex.12.000331 PMID: 19471542 PMCID: N/A\item \htmladdnormallink{\it  The statistics of polarization-dependent loss in a recirculating loop}{https://boh/2004-JLT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Karlsson, M. and Petersson, M. and Sunnerud, H. \\ ``Journal of Lightwave Technology'' Vol. 22 (2004) pp. 968-976. \\ DOI: 10.1109/jlt.2004.824861 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Interferometric differentiation between resonant coherent anti-Stokes Raman scattering and nonresonant four-wave-mixing processes}{https://boh/2004-APL.pdf} \\ Marks, D. L. and {\bf Vinegoni, C.} and Bredfeldt, J. S. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 85 (2004) pp. 5787-5789. \\ DOI: 10.1063/1.1829162 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed measurements of chromatic dispersion and nonlinear coefficient in low-PMD dispersion-shifted fibers}{https://boh/2003-PTL-2.pdf} \\ {\bf Vinegoni, C.} and Chen$^\#$, H. X. and Leblanc, M. and Schinn, G. W. and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 739-741. \\ DOI: 10.1109/lpt.2003.810249 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Statistics of PMD in recirculating loops}{https://boh/2003-PTL-1.pdf} \\ Petersson$^\#$, M. and {\bf Vinegoni, C.} and Sunnerud, H. and Karlsson, M. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 1543-1545. \\ DOI: 10.1109/lpt.2003.818681 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Emulator of first- and second-order polarization-mode dispersion}{https://boh/2002-PTL.pdf} \\ Wegmuller, M. and Demma, S. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 14 (2002) pp. 630-632. \\ DOI: 10.1109/68.998707 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Analysis of the polarization evolution in a ribbon cable using high-resolution coherent OFDR}{https://boh/2001-PTL-2.pdf} \\ Wegmuller, M. and Legre, M. and Oberson, P. and Guinnard, O. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 145-147. \\ DOI: 10.1109/68.910516 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurements of the nonlinear coefficient of standard SMF, DSF, and DCF fibers using a self-aligned interferometer and a Faraday mirror}{https://boh/2001-PTL-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 1337-1339. \\ DOI: 10.1109/68.969900 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Morphological and optical characterization of GaN prepared by pulsed laser deposition}{https://boh/2000-SCT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Cazzanelli, M. and Trivelli, A. and Mariotto, G. and Castro, J. and Lunney, J. G. and Levy, J. \\ ``Surface & Coatings Technology'' Vol. 124 (2000) pp. 272-277. \\ DOI: 10.1016/s0257-8972(99)00657-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Optical absorption and photoluminescence properties of alpha-Si1-xNx : H films deposited by plasma-enhanced CVD}{https://boh/2000-PRB.pdf} \\ Giorgis$^\#$, F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 61 (2000) pp. 4693-4698. \\ DOI: 10.1103/PhysRevB.61.4693 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  All optical switching in a highly birefringent and a standard telecom fiber using a Faraday mirror stabilization scheme}{https://boh/2000-OC.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Optics Communications'' Vol. 182 (2000) pp. 335-341. \\ DOI: 10.1016/s0030-4018(00)00845-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurement of nonlinear polarization rotation in a highly birefringent optical fibre using a Faraday mirror}{https://boh/2000-JOA.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Journal of Optics a-Pure and Applied Optics'' Vol. 2 (2000) pp. 314-318. \\ DOI: 10.1088/1464-4258/2/4/313 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed gain measurements in Er-doped fibers with high resolution and accuracy using an optical frequency domain reflectometer}{https://boh/2000-JLT.pdf} \\ Wegmuller$^\#$, M. and Oberson, P. and Guinnard, O. and Huttner, B. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin, N. \\ ``Journal of Lightwave Technology'' Vol. 18 (2000) pp. 2127-2132. \\ DOI: 10.1109/50.908823 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Determination of nonlinear coefficient n(2)/A(eff) using self-aligned interferometer and Faraday mirror}{https://boh/2000-EL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Electronics Letters'' Vol. 36 (2000) pp. 886-888. \\ DOI: 10.1049/el:20000668 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman study of the phase transitions sequence in pure WO3 at high temperature and in HxWO3 with variable hydrogen content}{https://boh/1999-SSI.pdf} \\ Cazzanelli$^\#$, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzmin, A. and Purans, J. \\ ``Solid State Ionics'' Vol. 123 (1999) pp. 67-74. \\ DOI: 10.1016/s0167-2738(99)00101-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescence processes in amorphous hydrogenated silicon-nitride nanometric multilayers}{https://boh/1999-PRB.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 60 (1999) pp. 11572-11576. \\ DOI: 10.1103/PhysRevB.60.11572 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescent properties of GaN thin films prepared by pulsed laser deposition}{https://boh/1999-MSEB.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Cole, D. and Lunney, J. G. and Middleton, P. G. and Trager-Cowan, C. and O'Donnell, K. P. and Pavesi$^\#$, L. \\ ``Materials Science and Engineering B-Solid State Materials for Advanced Technology'' Vol. 59 (1999) pp. 137-140. \\ DOI: 10.1016/s0921-5107(98)00333-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Low-temperature polymorphism in tungsten trioxide powders and its dependence on mechanical treatments}{https://boh/1999-JSSC.pdf} \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto$^\#$, G. and Kuzmin, A. and Purans, J. \\ ``Journal of Solid State Chemistry'' Vol. 143 (1999) pp. 24-32. \\ DOI: 10.1006/jssc.1998.8061 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Temperature dependence of the photoluminescence of all-porous-silicon optical microcavities}{https://boh/1999-JAP.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Journal of Applied Physics'' Vol. 85 (1999) pp. 1760-1764. \\ DOI: 10.1063/1.369320 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Color Centres and Polymorphism in Pure WO(3) and Mixed (1-x)WO(3-y)center dot xReO(2) Powders}{https://boh/1999-INCS.pdf} \\ Cazzanelli$^\#$, E. and Mariotto, G. and {\bf Vinegoni, C.} and Kuzmin, A. and Purans, J. \\ ``Ionics'' Vol. 5 (1999) pp. 335-344. \\ DOI: 10.1007/bf02375997 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman spectroscopy and scanning electron microscopy investigation of annealed amorphous carbon-germanium films deposited by d.c. magnetron sputtering}{https://boh/1999-DRM.pdf} \\ Mariotto, G. and {\bf Vinegoni, C.} and Jacobsohn, L. G. and Freire$^\#$, F. L. \\ ``Diamond and Related Materials'' Vol. 8 (1999) pp. 668-672. \\ DOI: 10.1016/s0925-9635(98)00328-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Resonant second harmonic generation in ZnSe bulk microcavity}{https://boh/1999-APL.pdf} \\ Pellegrini, V. and Colombelli, R. and Carusotto, I. and Beltram, F. and Rubini, S. and Lantier, R. and Franciosi, A. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Applied Physics Letters'' Vol. 74 (1999) pp. 1945-1947. \\ DOI: 10.1063/1.123736 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Radiative emission properties of a-SiN : H based nanometric multilayers for light emitting devices}{https://boh/1998-JL.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Journal of Luminescence'' Vol. 80 (1998) pp. 423-427. \\ DOI: 10.1016/s0022-2313(98)00141-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  X-ray diffraction, extended x-ray absorption fine structure and Raman spectroscopy studies of WO3 powders and, (1-x)WO3-y center dot xReO(2) mixtures}{https://boh/1998-JAP.pdf} \\ Kuzmin$^\#$, A. and Purans, J. and Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. \\ ``Journal of Applied Physics'' Vol. 84 (1998) pp. 5515-5524. \\ DOI: 10.1063/1.368596 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Photoluminescence of localized excitons in pulsed-laser-deposited GaN}{https://boh/1998-APL.pdf} \\ Cazzanelli$^\#$, M. and Cole, D. and Donegan, J. F. and Lunney, J. G. and Middleton, P. G. and O'Donnell, K. P. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Applied Physics Letters'' Vol. 73 (1998) pp. 3390-3392. \\ DOI: 10.1063/1.122776 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Spatiotemporal multiplexed immunofluorescence imaging of living cells and tissues with bioorthogonal cycling of fluorescent probes}{https://boh/2022-NB.pdf} \\ Ko, J.A. and Wilkovitsch, M. and Oh, J. and Kohler, R.H. and Bolli, E. and Pittet, M.J. and {\bf Vinegoni, C.} and Sykes, D.B. and Mikula, H. and Weissleder, R. and Carlson$^\#$, J.C.T. \\ ``Nature Biotechnology'' Vol. N/A (2022) pp. online. \\ DOI: 10.1038/s41587-022-01339-6 PMID: 35654978 PMCID: N/A\item \htmladdnormallink{\it  Neutrophils incite and macrophages avert electrical storm after myocardial infarction}{https://boh/2022-NCR-2.pdf} \\ Grune, J. and Lewis, A.J.M. and Yamazoe, M. and Hulsmans, M. and Rohde, D. and Xiao, L. and Zhang, S. and Ott, C. and Calcagno, D.M. and Zhou, Y. and Timm, K. and Shanmuganathan, M. and Pulous, F.E. and Schloss, M.J. and Foy, B.H. and Capen, D. and {\bf Vinegoni, C.} and Wojtkiewicz, G.R. and Iwamoto, I. and Grune, T. and Brown, D. and Higgins, J. and Ferreira, V.M. and Herring, N. and Channon, K.M. and Neubauer, S. and Oxford Acute Myocardial Infarction (OxAMI) Study and Sosnovik, D.E. and Milan, D.J. and Swirski, F.K. and King, K.R. and Aguirre, A.D. and Ellinor, P.T. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 649–664. \\ DOI: 10.1038/s44161-022-00094-w PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Cerebrospinal fluid can exit into the skull bone marrow and instruct cranial hematopoiesis in mice with bacterial meningitis}{https://boh/2022-NN.PDF} \\ Pulous, F. E. and Cruz-Hernandez, J. C. and Yang, C. B. and Kaya, Z. and Paccalet, A. and Wojtkiewicz, G. and Capen, D. and Brown, D. and Wu, J. W. and Schloss, M. J. and {\bf Vinegoni, C.} and Richter, D. and Yamazoe, M. and Hulsmans, M. and Momin, N. and Grune, J. and Rohde, D. and McAlpine, C. S. and Panizzi, P. and Weissleder, R. and Kim, D. E. and Swirski, F. K. and Lin, C. P. and Moskowitz, M. A. and Nahrendorf, M. \\ ``Nature Neuroscience'' Vol. 25 (2022) pp. 567-+. \\ DOI: 10.1038/s41593-022-01060-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Bone marrow endothelial dysfunction promotes myeloid cell expansion in cardiovascular disease}{https://boh/2022-NCR-1.pdf} \\ Rohde, D. and Vandoorne, K. and Lee, I. H. and Grune, J. and Zhang, S. and McAlpine, C. S. and Schloss, M. J. and Nayar, R. and Courties, G. and Frodermann, V. and Wojtkiewicz, G. and Honold, L. and Chen, Q. and Schmidt, S. and Iwamoto, Y. and Sun, Y. and Cremer, S. and Hoyer, F. F. and Iborra-Egea, O. and Muñoz-Guijosa, C. and Ji, F. and Zhou, G. and Adams, R. H. and Wythe, J. D. and Hidalgo, J. and Watanabe, H. and Jung, Y. and van der Laan, A. M. and Piek, J. J. and Kfoury, Y. and Désogère, P. A. and {\bf Vinegoni, C.} and Dutta, P. and Sadreyev, R. I. and Caravan, P. and Bayes-Genis, A. and Libby, P. and Scadden, D. T. and Lin, C. P. and Naxerova, K. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 28-44. \\ DOI: 10.1038/s44161-021-00002-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Astrocytic interleukin-3 programs microglia and limits Alzheimer's disease}{https://boh/2021-NATURE.pdf} \\ McAlpine, C. S. and Park, J. and Griciuc, A. and Kim, E. and Choi, S. H. and Iwamoto, Y. and Kiss, M. G. and Christie, K. A. and {\bf Vinegoni, C.} and Poller, W. C. and Mindur, J. E. and Chan, C. T. and He, S. and Janssen, H. and Wong, L. P. and Downey, J. and Singh, S. and Anzai, A. and Kahles, F. and Jorfi, M. and Feruglio, P. F. and Sadreyev, R. I. and Weissleder, R. and Kleinstiver, B. P. and Nahrendorf, M. and Tanzi, R. E. and Swirski$^\#$, F. K. \\ ``Nature'' Vol. 595 (2021) pp. 701-+. \\ DOI: 10.1038/s41586-021-03734-6 PMID: 34262178 PMCID: PMC8934148\item \htmladdnormallink{\it  CytoPAN-Portable cellular analyses for rapid point-of-care cancer diagnosis}{https://boh/2020-STM.pdf} \\ Min, J. and Chin, L. K. and Oh, J. and Landeros, C. and {\bf Vinegoni, C.} and Lee, J. and Lee, S. J. and Park, J. Y. and Liu, A. Q. and Castro, C. M. and Lee, H. and Im, H. and Weissleder$^\#$, R. \\ ``Science Translational Medicine'' Vol. 12 (2020) pp. 14. \\ DOI: 10.1126/scitranslmed.aaz9746 PMID: 32759277 PMCID: PMC8217912\item \htmladdnormallink{\it  Fluorescence microscopy tensor imaging representations for large-scale dataset analysis}{https://boh/2020-SCIREP.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Feruglio$^\dag$, P. F. and Courties, G. and Schmidt, S. and Hulsmans, M. and Lee, S. and Wang, R. and Sosnovik, D. and Nahrendorf, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 10 (2020) pp. 15. \\ DOI: 10.1038/s41598-020-62233-2 PMID: 32221334 PMCID: PMC7101442\item \htmladdnormallink{\it  Extended dynamic range imaging for noise mitigation in fluorescence anisotropy imaging}{https://boh/2020-JBO.pdf} \\ Feruglio$^\dag$, P. F. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 25 (2020) pp. 13. \\ DOI: 10.1117/1.Jbo.25.8.086003 PMID: 32820624 PMCID: PMC7439791\item \htmladdnormallink{\it  Diminished Reactive Hematopoiesis and Cardiac Inflammation in a Mouse Model of Recurrent Myocardial Infarction}{https://boh/2020-JAMCC.pdf} \\ Cremer, S. and Schloss, M. J. and {\bf Vinegoni, C.} and Foy, B. H. and Zhang, S. and Rohde, D. and Hulsmans, M. and Feruglio, P. F. and Schmidt, S. and Wojtkiewicz, G. and Higgins, J. M. and Weissleder, R. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 75 (2020) pp. 901-915. \\ DOI: 10.1016/j.jacc.2019.12.056 PMID: 32130926 PMCID: PMC7254576\item \htmladdnormallink{\it  Characterization of single microvesicles in plasma from glioblastoma patients}{https://boh/2019-NO.pdf} \\ Fraser, K. and Jo, A. and Giedt, J. and {\bf Vinegoni, C.} and Yang, K. S. and Peruzzi, P. and Chiocca, E. A. and Breakefield, X. O. and Lee, H. and Weissleder$^\#$, R. \\ ``Neuro-Oncology'' Vol. 21 (2019) pp. 606-615. \\ DOI: 10.1093/neuonc/noy187 PMID: 30561734 PMCID: 6502493\item \htmladdnormallink{\it  High Dynamic Range Fluorescence Imaging}{https://boh/2019-JSTQE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 25 (2019) pp. 7. \\ DOI: 10.1109/jstqe.2018.2881608 PMID: 31598059 PMCID: PMC6785194\item \htmladdnormallink{\it  Fluorescence anisotropy imaging in drug discovery}{https://boh/2019-ADDR.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Gryczynski, I. and Mazitschek, R. and Weissleder, R. \\ ``Advanced Drug Delivery Reviews'' Vol. 151 (2019) pp. 262-288. \\ DOI: 10.1016/j.addr.2018.01.019 PMID: 29410158 PMCID: 6072632\item \htmladdnormallink{\it  The anti-tumor diterpene oridonin is a direct inhibitor of Nucleolin in cancer cells}{https://boh/2018-SCIREP.pdf} \\ Vasaturo, M. and Cotugno, R. and Fiengo, L. and {\bf Vinegoni, C.} and Dal Piaz, F. and De Tommasi$^\#$, N. \\ ``Scientific Reports'' Vol. 8 (2018) pp. 13. \\ DOI: 10.1038/s41598-018-35088-x PMID: 30425290 PMCID: 6233161\item \htmladdnormallink{\it  Direct vascular channels connect skull bone marrow and the brain surface enabling myeloid cell migration}{https://boh/2018-NATNEURO.pdf} \\ Herisson, F. and Frodermann, V. and Courties, G. and Rohde, D. and Sun, Y. and Vandoorne, K. and Wojtkiewicz, G. R. and Masson, G. S. and {\bf Vinegoni, C.} and Kim, J. and Kim, D. E. and Weissleder, R. and Swirski, F. K. and Moskowitz, M. A. and Nahrendorf$^\#$, M. \\ ``Nature Neuroscience'' Vol. 21 (2018) pp. 1209-+. \\ DOI: 10.1038/s41593-018-0213-2 PMID: 30150661 PMCID: PMC6148759 \item \htmladdnormallink{\it  Cardiac macrophages promote diastolic dysfunction}{https://boh/2018-JEM.pdf} \\ Hulsmans, M. and Sager, H. B. and Roh, J. D. and Valero-Munoz, M. and Houstis, N. E. and Iwamoto, Y. and Sun, Y. and Wilson, R. M. and Wojtkiewicz, G. and Tricot, B. and Osborne, M. T. and Hung, J. and {\bf Vinegoni, C.} and Naxerova, K. and Sosnovik, D. E. and Zile, M. R. and Bradshaw, A. D. and Liao, R. and Tawakol, A. and Weissleder, R. and Rosenzweig, A. and Swirski, F. K. and Sam, F. and Nahrendorf$^\#$, M. \\ ``Journal of Experimental Medicine'' Vol. 215 (2018) pp. 423-440. \\ DOI: 10.1084/jem.20171274 PMID: 29339450 PMCID: PMC3366498\item \htmladdnormallink{\it  Imaging the Vascular Bone Marrow Niche During Inflammatory Stress}{https://boh/2018-CIRCRES.pdf} \\ Vandoorne, K. and Rohde, D. and Kim, H. Y. and Courties, G. and Wojtkiewicz, G. and Honold, L. and Hoyer, F. F. and Frodermann, V. and Nayar, R. and Herisson, F. and Jung, Y. and Desogere, P. A. and {\bf Vinegoni, C.} and Caravan, P. and Weissleder, R. and Sosnovik, D. E. and Lin, C. P. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Circulation Research'' Vol. 123 (2018) pp. 415-427. \\ DOI: 10.1161/circresaha.118.313302 PMID: 29980569 PMCID: 6202141\item \htmladdnormallink{\it  Design and Development of Fluorescent Vemurafenib Analogs for In Vivo Imaging}{https://boh/2017-THERA.pdf} \\ Mikula, H. and Stapleton, S. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Theranostics'' Vol. 7 (2017) pp. 1257-1265. \\ DOI: 10.7150/thno.18238 PMID: 28435463 PMCID: PMC5399591\item \htmladdnormallink{\it  Measurement of drug-target engagement in live cells by two-photon fluorescence anisotropy imaging}{https://boh/2017-NP.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Brand, C. and Lee, S. and Nibbs, A. E. and Stapleton, S. and Shah, S. and Gryczynski, I. and Reiner, T. and Mazitschek, R. and Weissleder, R. \\ ``Nature Protocols'' Vol. 12 (2017) pp. 1472-1497. \\ DOI: 10.1038/nprot.2017.043 PMID: 28686582 PMCID: PMC5928516\item \htmladdnormallink{\it  Quantitating drug-target engagement in single cells in vitro and in vivo}{https://boh/2017-NCBIOL.pdf} \\ Dubach, J. M. and Kim, E. and Yang, K. and Cuccarese, M. and Giedt, R. J. and Meirnetis, L. G. and {\bf Vinegoni$^\#$, C.} and Weissleder$^\#$, R. \\ ``Nature Chemical Biology'' Vol. 13 (2017) pp. 168-173. \\ DOI: 10.1038/nchembio.2248 PMID: 27918558 PMCID: PMC5630128\item \htmladdnormallink{\it  Motion characterization scheme to minimize motion artifacts in intravital microscopy}{https://boh/2017-JBO.pdf} \\ Lee, S. and Courties, G. and Nahrendorf, M. and Weissleder, R. and {\bf Vinegoni$^\#$, C.} \\ ``Journal of Biomedical Optics'' Vol. 22 (2017) pp. 7. \\ DOI: 10.1117/1.Jbo.22.3.036005 PMID: 28253383 PMCID: PMC5333764\item \htmladdnormallink{\it  Macrophages Facilitate Electrical Conduction in the Heart}{https://boh/2017-CELL.pdf} \\ Hulsmans, M. and Clauss, S. and Xiao, L. and Aguirre, A. D. and King, K. R. and Hanley, A. and Hucker, W. J. and Wulfers, E. M. and Seemann, G. and Courties, G. and Iwamoto, Y. and Sun, Y. and Savol, A. J. and Sager, H. B. and Lavine, K. J. and Fishbein, G. A. and Capen, D. E. and Da Silva, N. and Miquerol, L. and Wakimoto, H. and Seidman, C. E. and Seidman, J. G. and Sadreyev, R. I. and Naxerova, K. and Mitchell, R. N. and Brown, D. and Libby, P. and Weissleder, R. and Swirski, F. K. and Kohl, P. and {\bf Vinegoni, C.} and Milan, D. J. and Ellinor, P. T. and Nahrendorf$^\#$, M. \\ ``Cell'' Vol. 169 (2017) pp. 510-+. \\ DOI: 10.1016/j.cell.2017.03.050 PMID: 28431249 PMCID: PMC5474950\item \htmladdnormallink{\it  Transparent Electrophysiology Microelectrodes and Interconnects from Meta Nanomesh}{https://boh/2017-ACSN.pdf} \\ Seo, K. J. and Qiang, Y. and Bilgin, I. and Kar, S. and {\bf Vinegoni, C.} and Weissleder, R. and Fang$^\#$, H. \\ ``Acs Nano'' Vol. 11 (2017) pp. 4365-4372. \\ DOI: 10.1021/acsnano.7b01995 PMID: 28391679 PMCID: N/A\item \htmladdnormallink{\it  Two-photon imaging of pancreatic beta cells in real time in vivo}{https://boh/2016-TECHNOL.pdf} \\ Clardy, S. M. and Kohler, R. and {\bf Vinegoni, C.} and Iwamoto, Y. and Keliher, E. and Weissleder$^\#$, R. \\ ``Technology'' Vol. 4 (2016) pp. 130-34. \\ DOI: 10.1142/S2339547816200028 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  RNAi targeting multiple cell adhesion molecules reduces immune cell recruitment and vascular inflammation after myocardial infarction}{https://boh/2016-STM.pdf} \\ Sager, H. B. and Dutta, P. and Dahlman, J. E. and Hulsmans, M. and Courties, G. and Sun, Y. and Heidt, T. and {\bf Vinegoni, C.} and Borodovsky, A. and Fitzgerald, K. and Wojtkiewicz, G. R. and Iwamoto, Y. and Tricot, B. and Khan, O. F. and Kauffman, K. J. and Xing, Y. P. and Shaw, T. E. and Libby, P. and Langer, R. and Weissleder, R. and Swirski, F. K. and Anderson, D. G. and Nahrendorf$^\#$, M. \\ ``Science Translational Medicine'' Vol. 8 (2016) pp. 11. \\ DOI: 10.1126/scitranslmed.aaf1435 PMID: 27280687 PMCID: PMC5125383\item \htmladdnormallink{\it  Computational imaging reveals mitochondrial morphology as a biomarker of cancer phenotype and drug response}{https://boh/2016-SCIREP.pdf} \\ Giedt, R. J. and Fumene Feruglio, P. and Pathania, D. and Yang, K. S. and Kilcoyne, A. and {\bf Vinegoni, C.} and Mitchison, T. J. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 6 (2016) pp. 10. \\ DOI: 10.1038/srep32985 PMID: 27609668 PMCID: PMC5017129\item \htmladdnormallink{\it  Real-time high dynamic range laser scanning microscopy}{https://boh/2016-NCOMM-2.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Swisher$^\dag$, C. L. and Fumene Feruglio$^\dag$, P. and Giedt, R. J. and Rousso, D. L. and Stapleton, S. and Weissleder, R. \\ ``Nature Communications'' Vol. 7 (2016) pp. 13. \\ DOI: 10.1038/ncomms11077 PMID: 27032979 PMCID: PMC4821995\item \htmladdnormallink{\it  Tyrosine kinase-mediated axial motility of basal cells revealed by intravital imaging}{https://boh/2016-NCOMM-1.pdf} \\ Roy, J. and Kim, B. and Hill, E. and Visconti, P. and Krapf, D. and {\bf Vinegoni, C.} and Weissleder, R. and Brown, D. and Breton$^\#$, S. \\ ``Nature Communications'' Vol. 7 (2016) pp. 11. \\ DOI: 10.1038/ncomms10666 PMID: 26868824 PMCID: PMC4754344\item \htmladdnormallink{\it  Two-Photon Fluorescence Anisotropy Microscopy for Imaging and Direct Measurement of Intracellular Drug Target Engagement}{https://boh/2016-IEEE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 22 (2016) pp. 7. \\ DOI: 10.1109/jstqe.2015.2501384 PMID: 27440991 PMCID: PMC4946648\item \htmladdnormallink{\it  Rapid, high efficiency isolation of pancreatic beta-cells}{https://boh/2015-SREP.pdf} \\ Clardy, S. M. and Mohan, J. F. and {\bf Vinegoni, C.} and Keliher, E. J. and Iwamoto, Y. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 5 (2015) pp. 9. \\ DOI: 10.1038/srep13681 PMID: 26330153 PMCID: PMC4557033\item \htmladdnormallink{\it  Imaging the beating heart in the mouse using intravital microscopy techniques}{https://boh/2015-NPROT.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Aguirre$^\dag$, A. D. and Lee, S. and Weissleder, R. \\ ``Nature Protocols'' Vol. 10 (2015) pp. 1802-1819. \\ DOI: 10.1038/nprot.2015.119 PMID: 26492138 PMCID: PMC5380003\item \htmladdnormallink{\it  New techniques for motion-artifact-free in vivo cardiac microscopy}{https://boh/2015-FPHYS.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Aguirre, A. D. and Weissleder, R. \\ ``Frontiers in Physiology'' Vol. 6 (2015) pp. 12. \\ DOI: 10.3389/fphys.2015.00147 PMID: 26029116 PMCID: PMC4428079\item \htmladdnormallink{\it  Advances in measuring single-cell pharmacology in vivo}{https://boh/2015-DDT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Thurber, G. M. and Miller, M. A. and Mazitschek, R. and Weissleder, R. \\ ``Drug Discovery Today'' Vol. 20 (2015) pp. 1087-1092. \\ DOI: 10.1016/j.drudis.2015.05.011 PMID: 26024776 PMCID: PMC4567932\item \htmladdnormallink{\it  Myocardial Infarction Activates CCR2(+) Hematopoietic Stem and Progenitor Cells}{https://boh/2015-CSC.pdf} \\ Dutta, P. and Sager, H. B. and Stengel, K. R. and Naxerova, K. and Courties, G. and Saez, B. and Silberstein, L. and Heidt, T. and Sebas, M. and Sun, Y. and Wojtkiewicz, G. and Fumene Feruglio, P. and King, K. and Baker, J. N. and van der Laan, A. M. and Borodovsky, A. and Fitzgerald, K. and Hulsmans, M. and Hoyer, F. and Iwamoto, Y. and {\bf Vinegoni, C.} and Brown, D. and Di Carli, M. and Libby, P. and Hiebert, S. W. and Scadden, D. T. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Cell Stem Cell'' Vol. 16 (2015) pp. 477-487. \\ DOI: 10.1016/j.stem.2015.04.008 PMID: 25957903 PMCID: PMC4426344\item \htmladdnormallink{\it  Automated motion artifact removal for intravital microscopy, without a priori information}{https://boh/2014-SR.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Sebas, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 4 (2014) pp. 9. \\ DOI: 10.1038/srep04507 PMID: 24676021 PMCID: PMC3968488\item \htmladdnormallink{\it  Intravital imaging of cardiac function at the single-cell level}{https://boh/2014-PNAS.pdf} \\ Aguirre, A. D. and {\bf Vinegoni$^\#$, C.} and Sebas, M. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 111 (2014) pp. 11257-11262. \\ DOI: 10.1073/pnas.1401316111 PMID: 25053815 PMCID: PMC4128110\item \htmladdnormallink{\it  Steady state anisotropy two-photon microscopy resolves multiple, spectrally similar fluorophores, enabling in vivo multilabel imaging}{https://boh/2014-OL.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Optics Letters'' Vol. 39 (2014) pp. 4482-4485. \\ DOI: 10.1364/ol.39.004482 PMID: 25078208 PMCID: PMC4341989\item \htmladdnormallink{\it  Chronic variable stress activates hematopoietic stem cells}{https://boh/2014-NM.pdf} \\ Heidt, T. and Sager, H. B. and Courties, G. and Dutta, P. and Iwamoto, Y. and Zaltsman, A. and von zur Muhlen, C. and Bode, C. and Fricchione, G. L. and Denninger, J. and Lin, C. P. and {\bf Vinegoni, C.} and Libby, P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature Medicine'' Vol. 20 (2014) pp. 754-758. \\ DOI: 10.1038/nm.3589 PMID: 24952646 PMCID: PMC4087061\item \htmladdnormallink{\it  In vivo imaging of specific drug-target binding at subcellular resolution}{https://boh/2014-NC.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Mazitschek, R. and Fumene Feruglio, P. and Cameron, L. A. and Weissleder, R. \\ ``Nature Communications'' Vol. 5 (2014) pp. 9. \\ DOI: 10.1038/ncomms4946 PMID: 24867710 PMCID: PMC4362617\item \htmladdnormallink{\it  Advanced Motion Compensation Methods for Intravital Optical Microscopy}{https://boh/2014-IEEE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 20 (2014) pp. 9. \\ DOI: 10.1109/jstqe.2013.2279314 PMID: 24273405 PMCID: PMC3832946\item \htmladdnormallink{\it  Perinatal health and translational medicine}{https://boh/2013-JHGD.pdf} \\ Figueiredo, J. L. and {\bf Vinegoni, C.} and De Abreu, L. C. \\ ``Journal of Human Growth and Development'' Vol. 23 (2013) pp. 125-127. \\ DOI: 10.7322/jhgd.61318 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Sequential average segmented microscopy for high signal-to-noise ratio motion-artifact-free in vivo heart imaging}{https://boh/2013-BOE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Marzola, P. and Nahrendorf, M. and Weissleder, R. \\ ``Biomedical Optics Express'' Vol. 4 (2013) pp. 2095-2106. \\ DOI: 10.1364/boe.4.002095 PMID: 24156067 PMCID: PMC3799669\item \htmladdnormallink{\it  Noise suppressed, multifocus image fusion for enhanced intraoperative navigation}{https://boh/2013-BIOPHTNCS.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Fexon, L. and Thurber, G. and Sbarbati, A. and Weissleder, R. \\ ``Journal of Biophotonics'' Vol. 6 (2013) pp. 363-370. \\ DOI: 10.1002/jbio.201200086 PMID: 22887724 PMCID: PMC3779878\item \htmladdnormallink{\it  Implantable microenvironments to attract hematopoietic stem/cancer cells}{https://boh/2012-PNAS.pdf} \\ Lee, J. and Li, M. and Milwid, J. and Dunham, J. and {\bf Vinegoni, C.} and Gorbatov, R. and Iwamoto, Y. and Wang, F. J. and Shen, K. Y. and Hatfield, K. and Enger, M. and Shafiee, S. and McCormack, E. and Ebert, B. L. and Weissleder, R. and Yarmush, M. L. and Parekkadan$^\#$, B. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 109 (2012) pp. 19638-19643. \\ DOI: 10.1073/pnas.1208384109 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Mapping Molecular Agents Distributions in Whole Mice Hearts Using Born-Normalized Optical Projection Tomography}{https://boh/2012-PLOSONE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio$^\dag$, P. and Razansky, D. and Gorbatov, R. and Ntziachristos, V. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Plos One'' Vol. 7 (2012) pp. 9. \\ DOI: 10.1371/journal.pone.0034427 PMID: 22509302 PMCID: PMC3324534\item \htmladdnormallink{\it  Imaging Therapeutic PARP Inhibition In Vivo through Bioorthogonally Developed Companion Imaging Agents}{https://boh/2012-NEOPLASIA.pdf} \\ Reiner, T. and Lacy, J. and Keliher, E. J. and Yang, K. S. and Ullal, A. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Neoplasia'' Vol. 14 (2012) pp. 169-+. \\ DOI: 10.1593/neo.12414 PMID: 22496617 PMCID: PMC3323895\item \htmladdnormallink{\it  Real-time in vivo imaging of the beating mouse heart at microscopic resolution}{https://boh/2012-NC.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Fexon, L. and Gorbatov, R. and Pivoravov, M. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Nature Communications'' Vol. 3 (2012) pp. 8. \\ DOI: 10.1038/ncomms2060 PMID: 22968700 PMCID: PMC3622400\item \htmladdnormallink{\it  Myocardial infarction accelerates atherosclerosis}{https://boh/2012-NATURE.pdf} \\ Dutta, P. and Courties, G. and Wei, Y. and Leuschner, F. and Gorbatov, R. and Robbins, C. S. and Iwamoto, Y. and Thompson, B. and Carlson, A. L. and Heidt, T. and Majmudar, M. D. and Lasitschka, F. and Etzrodt, M. and Waterman, P. and Waring, M. T. and Chicoine, A. T. and van der Laan, A. M. and Niessen, H. W. M. and Piek, J. J. and Rubin, B. B. and Butany, J. and Stone, J. R. and Katus, H. A. and Murphy, S. A. and Morrow, D. A. and Sabatine, M. S. and {\bf Vinegoni, C.} and Moskowitz, M. A. and Pittet, M. J. and Libby, P. and Lin, C. P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature'' Vol. 487 (2012) pp. 325-329. \\ DOI: 10.1038/nature11260 PMID: 22763456 PMCID: PMC3401326\item \htmladdnormallink{\it  Improved intravital microscopy via synchronization of respiration and holder stabilization}{https://boh/2012-JBO.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 17 (2012) pp. 8. \\ DOI: 10.1117/1.Jbo.17.9.096018 PMID: 23085919 PMCID: PMC3449295\item \htmladdnormallink{\it  PET/MRI of Inflammation in Myocardial Infarction}{https://boh/2012-JACC.pdf} \\ Lee, W. W. and Marinelli, B. and van der Laan, A. M. and Sena, B. F. and Gorbatov, R. and Leuschner, F. and Dutta, P. and Iwamoto, Y. and Ueno, T. and Begieneman, M. P. V. and Niessen, H. W. M. and Piek, J. J. and {\bf Vinegoni, C.} and Pittet, M. J. and Swirski, F. K. and Tawakol, A. and Di Carli, M. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 59 (2012) pp. 153-163. \\ DOI: 10.1016/j.jacc.2011.08.066 PMID: 22222080 PMCID: PMC3257823\item \htmladdnormallink{\it  Motion compensation using a suctioning stabilizer for intravital microscopy}{https://boh/2012-INTRVTL.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Gorbatov, R. and Weissleder, R. \\ ``Intravital'' Vol. 1 (2012) pp. 115. \\ DOI: 10.4161/intv.23017 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Deep Tissue Optical and Optoacoustic Molecular Imaging Technologies for Pre-Clinical Research and Drug Discovery}{https://boh/2012-CPB.pdf} \\ Razansky$^\#$, D. and Deliolanis, N. C. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Current Pharmaceutical Biotechnology'' Vol. 13 (2012) pp. 504-522. \\ DOI: 10.2174/138920112799436258 PMID: 22216767 PMCID: N/A\item \htmladdnormallink{\it  In Vivo Imaging of Drug-Induced Mitochondrial Outer Membrane Permeabilization at Single-Cell Resolution}{https://boh/2012-CNCRRES.pdf} \\ Earley, S. and {\bf Vinegoni, C.} and Dunham, J. and Gorbatov, R. and Fumene Feruglio, P. and Weissleder$^\#$, R. \\ ``Cancer Research'' Vol. 72 (2012) pp. 2949-2956. \\ DOI: 10.1158/0008-5472.Can-11-4096 PMID: 22505651 PMCID: PMC3603290\item \htmladdnormallink{\it  Optochemogenetics (OCG) Allows More Precise Control of Genetic Engineering in Mice with CreER regulators}{https://boh/2012-BIOCHEM.pdf} \\ Lu, X. and Agasti, S. S. and {\bf Vinegoni, C.} and Waterman, P. and DePinho, R. A. and Weissleder$^\#$, R. \\ ``Bioconjugate Chemistry'' Vol. 23 (2012) pp. 1945-1951. \\ DOI: 10.1021/bc300319c PMID: 22917215 PMCID: PMC3775343\item \htmladdnormallink{\it  Bioorthogonal Imaging of Aurora Kinase A in Live Cells}{https://boh/2012-AC.pdf} \\ Yang, K. S. and Budin, G. and Reiner, T. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Angewandte Chemie-International Edition'' Vol. 51 (2012) pp. 6598-6603. \\ DOI: 10.1002/anie.201200994 PMID: 22644700 PMCID: PMC3523717\item \htmladdnormallink{\it  Indocyanine Green Enables Near-Infrared Fluorescence Imaging of Lipid-Rich, Inflamed Atherosclerotic Plaques}{https://boh/2011-STM.pdf} \\ {\bf Vinegoni, C.} and Botnaru, I. and Aikawa, E. and Calfon, M. A. and Iwamoto, Y. and Folco, E. J. and Ntziachristos, V. and Weissleder, R. and Libby, P. and Jaffer$^\#$, F. A. \\ ``Science Translational Medicine'' Vol. 3 (2011) pp. 9. \\ DOI: 10.1126/scitranslmed.3001577 PMID: 21613624 PMCID: PMC3112179\item \htmladdnormallink{\it  Accurate measurement of pancreatic islet beta-cell mass using a second-generation fluorescent exendin-4 analog}{https://boh/2011-PNAS.pdf} \\ Reiner, T. and Thurber, G. and Gaglia, J. and {\bf Vinegoni, C.} and Liew, C. W. and Upadhyay, R. and Kohler, R. H. and Li, L. and Kulkarni, R. N. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 108 (2011) pp. 12815-12820. \\ DOI: 10.1073/pnas.1109859108 PMID: 21768367 PMCID: PMC3150928\item \htmladdnormallink{\it  A multimodal approach for tracing lateralisation along the olfactory pathway in the honeybee through electrophysiological recordings, morpho-functional imaging, and behavioural studies}{https://boh/2011-EB.pdf} \\ Haase, A. and Rigosi, E. and Frasnelli, E. and Trona, F. and Tessarolo, F. and {\bf Vinegoni, C.} and Anfora, G. and Vallortigara, G. and Antolini$^\#$, R. \\ ``European Biophysics Journal with Biophysics Letters'' Vol. 40 (2011) pp. 1247-1258. \\ DOI: 10.1007/s00249-011-0748-6 PMID: 21956452 PMCID: PMC3366498\item \htmladdnormallink{\it  Searching for anatomical correlates of olfactory lateralization in the honeybee antennal lobes: A morphological and behavioural study}{https://boh/2011-BBR.pdf} \\ Rigosi$^\#$, E. and Frasnelli, E. and {\bf Vinegoni, C.} and Antolini, R. and Anfora, G. and Vallortigara, G. and Haase, A. \\ ``Behavioural Brain Research'' Vol. 221 (2011) pp. 290-294. \\ DOI: 10.1016/j.bbr.2011.03.015 PMID: 21402106 PMCID: PMC3089663\item \htmladdnormallink{\it  Intraoperative Near-infrared Fluorescent Cholangiography (NIRFC) in Mouse Models of Bile Duct Injury: Reply}{https://boh/2010-WJS.pdf} \\ Figueiredo, J. L. and Nahrendorf, M. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``World Journal of Surgery'' Vol. 35 (2011) pp. 694-695. \\ DOI: 10.1007/s00268-010-0728-5 PMID: 20645091 PMCID: N/A\item \htmladdnormallink{\it  Hybrid PET-optical imaging using targeted probes}{https://boh/2010-PNAS.pdf} \\ Nahrendorf$^{\dag \#}$, M. and Keliher$^\dag$, E. and Marinelli, B. and Waterman, P. and Fumene Feruglio, P. and Fexon, L. and Pivovarov, M. and Swirski, F. K. and Pittet, M. J. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 107 (2010) pp. 7910-7915. \\ DOI: 10.1073/pnas.0915163107 PMID: 20385821 PMCID: PMC2867879\item \htmladdnormallink{\it  Block matching 3D random noise filtering for absorption optical projection tomography}{https://boh/2010-PMB.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Gros, J. and Sbarbati, A. and Weissleder, R. \\ ``Physics in Medicine and Biology'' Vol. 55 (2010) pp. 5401-5415. \\ DOI: 10.1088/0031-9155/55/18/009 PMID: 20736500 PMCID: PMC2934766\item \htmladdnormallink{\it  Imaging of molecular probe activity with Born-normalized fluorescence optical projection tomography}{https://boh/2010-OL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Cortez-Retamozo, V. and Razansky, D. and Medoff, B. D. and Ntziachristos, V. and Sbarbati, A. and Pittet, M. and Weissleder, R. \\ ``Optics Letters'' Vol. 35 (2010) pp. 1088-1090. \\ DOI: 10.1364/ol.35.001088 PMID: 20364226 PMCID: PMC2900933\item \htmladdnormallink{\it  Intravascular near-infrared fluorescence molecular imaging of atherosclerosis: toward coronary arterial visualization of biologically high-risk plaques}{https://boh/2010-JBO.pdf} \\ Calfon, M. A. and {\bf Vinegoni, C.} and Ntziachristos, V. and Jaffer$^\#$, F. A. \\ ``Journal of Biomedical Optics'' Vol. 15 (2010) pp. 6. \\ DOI: 10.1117/1.3280282 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  WNT5A/JNK and FGF/MAPK Pathways Regulate the Cellular Events Shaping the Vertebrate Limb Bud}{https://boh/2010-CB.pdf} \\ Gros, J. and Hu, J. K. H. and {\bf Vinegoni, C.} and Fumene Feruglio, P. and Weissleder, R. and Tabin$^\#$, C. J. \\ ``Current Biology'' Vol. 20 (2010) pp. 1993-2002. \\ DOI: 10.1016/j.cub.2010.09.063 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  In-vivo two-photon imaging of the honey bee antennal lobe}{https://boh/2010-BOEX.pdf} \\ Haase, A. and Rigosi, E. and Trona, F. and Anfora, G. and Vallortigara, G. and Antolini, R. and {\bf Vinegoni$^\#$, C.} \\ ``Biomedical Optics Express'' Vol. 2 (2011) pp. 131-138. \\ DOI: 10.1364/boe.2.000131 PMID: 21326643 PMCID: PMC3028488\item \htmladdnormallink{\it  Imaging of mesoscopic-scale organisms using selective-plane optoacoustic tomography}{https://boh/2009-PMB.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Physics in Medicine and Biology'' Vol. 54 (2009) pp. 2769-2777. \\ DOI: 10.1088/0031-9155/54/9/012 PMID: 19369709 PMCID: N/A\item \htmladdnormallink{\it  Normalized Born ratio for fluorescence optical projection tomography}{https://boh/2009-OL-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 319-321. \\ DOI: 10.1364/ol.34.000319 PMID: 19183644 PMCID: PMC2771918\item \htmladdnormallink{\it  Transillumination fluorescence imaging in mice using biocompatible upconverting nanoparticles}{https://boh/2009-OL-1.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Razansky$^\dag$, D. and Hilderbrand, S. A. and Shao, F. W. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 2566-2568. \\ DOI: 10.1364/ol.34.002566 PMID: 19724491 PMCID: PMC2749971\item \htmladdnormallink{\it  Diffractionless beam in free space with adiabatic changing refractive index in a single mode tapered slab waveguide}{https://boh/2009-OE-2.pdf} \\ Tsai$^\#$, C. C. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 21723-21731. \\ DOI: 10.1364/oe.17.021723 PMID: 19997414 PMCID: PMC2805120\item \htmladdnormallink{\it  High throughput transmission optical projection tomography using low cost graphics processing unit}{https://boh/2009-OE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fexon, L. and Fumene Feruglio, P. and Pivovarov, M. and Figueiredo, J. L. and Nahrendorf, M. and Pozzo, A. and Sbarbati, A. and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 22320-22332. \\ DOI: 10.1364/oe.17.022320 PMID: 20052155 PMCID: PMC2805020\item \htmladdnormallink{\it  Multispectral opto-acoustic tomography of deep-seated fluorescent proteins in vivo}{https://boh/2009-NATPHOT.pdf} \\ Razansky$^\#$, D. and Distel, M. and {\bf Vinegoni, C.} and Ma, R. and Perrimon, N. and Koster, R. W. and Ntziachristos$^\#$, V. \\ ``Nature Photonics'' Vol. 3 (2009) pp. 412-417. \\ DOI: 10.1038/nphoton.2009.98 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Mesoscopic Fluorescence Tomography for In-vivo Imaging of Developing Drosophila}{https://boh/2009-JOVE-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Pitsouli, C. and Perrimon, N. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1510. \\ DOI: 10.3791/1510 PMID: 19696720 PMCID: PMC2736679\item \htmladdnormallink{\it  Born normalization for fluorescence optical projection tomography for whole heart imaging}{https://boh/2009-JOVE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Fexon, L. and Pivoravov, M. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1389. \\ DOI: 10.3791/1389 PMID: 19578329 PMCID: PMC2794886\item \htmladdnormallink{\it  Unprecedent in vivo views at the mesoscopic scale}{https://boh/2009-BOW.pdf} \\ Razansky, R. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``BioOptics World'' Vol. 2 (2009) pp. 22. \\ DOI: N/A PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Polarization-sensitive optoacoustic tomography of optically diffuse tissues}{https://boh/2008-OL.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Optics Letters'' Vol. 33 (2008) pp. 2308-2310. \\ DOI: 10.1364/ol.33.002308 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  In vivo imaging of Drosophila melanogaster pupae with mesoscopic fluorescence tomography}{https://boh/2008-NM.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Pitsouli$^\dag$, C. and Razansky$^\dag$, D. and Perrimon, N. and Ntziachristos, V. \\ ``Nature Methods'' Vol. 5 (2008) pp. 45-47. \\ DOI: 10.1038/nmeth1149 PMID: 18066071 PMCID: N/A\item \htmladdnormallink{\it  Real-time assessment of inflammation and treatment response in a mouse model of allergic airway inflammation}{https://boh/2008-JCI.pdf} \\ Cortez-Retamozo, V. and Swirski, F. K. and Waterman, P. and Yuan, H. and Figueiredo, J. L. and Newton, A. P. and Upadhyay, R. and {\bf Vinegoni, C.} and Kohler, R. and Blois, J. and Smith, A. and Nahrendorf, M. and Josephson, L. and Weissleder, R. and Pittet$^\#$, M. J. \\ ``Journal of Clinical Investigation'' Vol. 118 (2008) pp. 4058-4066. \\ DOI: 10.1172/jci36335 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  Real-Time Catheter Molecular Sensing of Inflammation in Proteolytically Active Atherosclerosis}{https://boh/2008-CRCLT.pdf} \\ Jaffer, F. A. and {\bf Vinegoni, C.} and John, M. C. and Aikawa, E. and Gold, H. K. and Finn, A. V. and Ntziachristos, V. and Libby, P. and Weissleder$^\#$, R. \\ ``Circulation'' Vol. 118 (2008) pp. 1802-1809. \\ DOI: 10.1161/circulationaha.108.785881 PMID: 18852366 PMCID: PMC2729441\item \htmladdnormallink{\it  Multispectral photoacoustic imaging of fluorochromes in small animals}{https://boh/2007-OL.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``Optics Letters'' Vol. 32 (2007) pp. 2891-2893. \\ DOI: 10.1364/ol.32.002891 PMID: 17909608 PMCID: N/A\item \htmladdnormallink{\it  Imaging cellular responses to mechanical stimuli within three-dimensional tissue constructs}{https://boh/2007-MRT.pdf} \\ Tan, W. and {\bf Vinegoni, C.} and Norman, J. J. and Desai, T. A. and Boppart$^\#$, S. A. \\ ``Microscopy Research and Technique'' Vol. 70 (2007) pp. 361-371. \\ DOI: 10.1002/jemt.20420 PMID: 17262787 PMCID: N/A\item \htmladdnormallink{\it  High-spectral-resolution coherent anti-Stokes Raman scattering with interferometric ally detected broadband chirped pulses}{https://boh/2006-OL-2.pdf} \\ Jones, G. W. and Marks, D. L. and {\bf Vinegoni, C.} and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1543-1545. \\ DOI: 10.1364/ol.31.001543 PMID: 16642166 PMCID: N/A\item \htmladdnormallink{\it  Spectroscopic spectral-domain optical coherence microscopy}{https://boh/2006-OL-1.pdf} \\ Xu, C. Y. and {\bf Vinegoni, C.} and Ralston, T. S. and Luo, W. and Tan, W. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1079-1081. \\ DOI: 10.1364/ol.31.001079 PMID: 16625909 PMCID: N/A\item \htmladdnormallink{\it  Integrated structural and functional optical imaging combining spectral-domain optical coherence and multiphoton microscopy}{https://boh/2006-APL.pdf} \\ {\bf Vinegoni, C.} and Ralston, T. and Tan, W. and Luo, W. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 88 (2006) pp. 3. \\ DOI: 10.1063/1.2171477 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Nonlinear Interferometric Vibrational Imaging. efficient detection of Coherent Anti-Stokes Raman Scattering}{https://boh/2005-OPN.pdf} \\ McAlpine, C. S. and Marks, D. and {\bf Vinegoni, C.} and Bredfeldt, J. and Boppart$^\#$, S.A. \\ ``Optics & Photonics News'' Vol. 16 (2005) pp. 23. \\ DOI: 10.1364/OPN.16.12.000023 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Molecularly sensitive optical coherence tomography}{https://boh/2005-OL.pdf} \\ Bredfeldt, J. S. and {\bf Vinegoni, C.} and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 30 (2005) pp. 495-497. \\ DOI: 10.1364/ol.30.000495 PMID: 15789714 PMCID: N/A\item \htmladdnormallink{\it  Nonlinear optical contrast enhancement for optical coherence tomography}{https://boh/2004-OE.pdf} \\ {\bf Vinegoni, C.} and Bredfeldt, J. S. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Express'' Vol. 12 (2004) pp. 331-341. \\ DOI: 10.1364/opex.12.000331 PMID: 19471542 PMCID: N/A\item \htmladdnormallink{\it  The statistics of polarization-dependent loss in a recirculating loop}{https://boh/2004-JLT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Karlsson, M. and Petersson, M. and Sunnerud, H. \\ ``Journal of Lightwave Technology'' Vol. 22 (2004) pp. 968-976. \\ DOI: 10.1109/jlt.2004.824861 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Interferometric differentiation between resonant coherent anti-Stokes Raman scattering and nonresonant four-wave-mixing processes}{https://boh/2004-APL.pdf} \\ Marks, D. L. and {\bf Vinegoni, C.} and Bredfeldt, J. S. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 85 (2004) pp. 5787-5789. \\ DOI: 10.1063/1.1829162 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed measurements of chromatic dispersion and nonlinear coefficient in low-PMD dispersion-shifted fibers}{https://boh/2003-PTL-2.pdf} \\ {\bf Vinegoni, C.} and Chen$^\#$, H. X. and Leblanc, M. and Schinn, G. W. and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 739-741. \\ DOI: 10.1109/lpt.2003.810249 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Statistics of PMD in recirculating loops}{https://boh/2003-PTL-1.pdf} \\ Petersson$^\#$, M. and {\bf Vinegoni, C.} and Sunnerud, H. and Karlsson, M. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 1543-1545. \\ DOI: 10.1109/lpt.2003.818681 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Emulator of first- and second-order polarization-mode dispersion}{https://boh/2002-PTL.pdf} \\ Wegmuller, M. and Demma, S. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 14 (2002) pp. 630-632. \\ DOI: 10.1109/68.998707 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Analysis of the polarization evolution in a ribbon cable using high-resolution coherent OFDR}{https://boh/2001-PTL-2.pdf} \\ Wegmuller, M. and Legre, M. and Oberson, P. and Guinnard, O. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 145-147. \\ DOI: 10.1109/68.910516 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurements of the nonlinear coefficient of standard SMF, DSF, and DCF fibers using a self-aligned interferometer and a Faraday mirror}{https://boh/2001-PTL-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 1337-1339. \\ DOI: 10.1109/68.969900 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Morphological and optical characterization of GaN prepared by pulsed laser deposition}{https://boh/2000-SCT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Cazzanelli, M. and Trivelli, A. and Mariotto, G. and Castro, J. and Lunney, J. G. and Levy, J. \\ ``Surface & Coatings Technology'' Vol. 124 (2000) pp. 272-277. \\ DOI: 10.1016/s0257-8972(99)00657-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Optical absorption and photoluminescence properties of alpha-Si1-xNx : H films deposited by plasma-enhanced CVD}{https://boh/2000-PRB.pdf} \\ Giorgis$^\#$, F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 61 (2000) pp. 4693-4698. \\ DOI: 10.1103/PhysRevB.61.4693 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  All optical switching in a highly birefringent and a standard telecom fiber using a Faraday mirror stabilization scheme}{https://boh/2000-OC.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Optics Communications'' Vol. 182 (2000) pp. 335-341. \\ DOI: 10.1016/s0030-4018(00)00845-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurement of nonlinear polarization rotation in a highly birefringent optical fibre using a Faraday mirror}{https://boh/2000-JOA.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Journal of Optics a-Pure and Applied Optics'' Vol. 2 (2000) pp. 314-318. \\ DOI: 10.1088/1464-4258/2/4/313 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed gain measurements in Er-doped fibers with high resolution and accuracy using an optical frequency domain reflectometer}{https://boh/2000-JLT.pdf} \\ Wegmuller$^\#$, M. and Oberson, P. and Guinnard, O. and Huttner, B. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin, N. \\ ``Journal of Lightwave Technology'' Vol. 18 (2000) pp. 2127-2132. \\ DOI: 10.1109/50.908823 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Determination of nonlinear coefficient n(2)/A(eff) using self-aligned interferometer and Faraday mirror}{https://boh/2000-EL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Electronics Letters'' Vol. 36 (2000) pp. 886-888. \\ DOI: 10.1049/el:20000668 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman study of the phase transitions sequence in pure WO3 at high temperature and in HxWO3 with variable hydrogen content}{https://boh/1999-SSI.pdf} \\ Cazzanelli$^\#$, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzmin, A. and Purans, J. \\ ``Solid State Ionics'' Vol. 123 (1999) pp. 67-74. \\ DOI: 10.1016/s0167-2738(99)00101-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescence processes in amorphous hydrogenated silicon-nitride nanometric multilayers}{https://boh/1999-PRB.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 60 (1999) pp. 11572-11576. \\ DOI: 10.1103/PhysRevB.60.11572 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescent properties of GaN thin films prepared by pulsed laser deposition}{https://boh/1999-MSEB.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Cole, D. and Lunney, J. G. and Middleton, P. G. and Trager-Cowan, C. and O'Donnell, K. P. and Pavesi$^\#$, L. \\ ``Materials Science and Engineering B-Solid State Materials for Advanced Technology'' Vol. 59 (1999) pp. 137-140. \\ DOI: 10.1016/s0921-5107(98)00333-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Low-temperature polymorphism in tungsten trioxide powders and its dependence on mechanical treatments}{https://boh/1999-JSSC.pdf} \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto$^\#$, G. and Kuzmin, A. and Purans, J. \\ ``Journal of Solid State Chemistry'' Vol. 143 (1999) pp. 24-32. \\ DOI: 10.1006/jssc.1998.8061 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Temperature dependence of the photoluminescence of all-porous-silicon optical microcavities}{https://boh/1999-JAP.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Journal of Applied Physics'' Vol. 85 (1999) pp. 1760-1764. \\ DOI: 10.1063/1.369320 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Color Centres and Polymorphism in Pure WO(3) and Mixed (1-x)WO(3-y)center dot xReO(2) Powders}{https://boh/1999-INCS.pdf} \\ Cazzanelli$^\#$, E. and Mariotto, G. and {\bf Vinegoni, C.} and Kuzmin, A. and Purans, J. \\ ``Ionics'' Vol. 5 (1999) pp. 335-344. \\ DOI: 10.1007/bf02375997 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman spectroscopy and scanning electron microscopy investigation of annealed amorphous carbon-germanium films deposited by d.c. magnetron sputtering}{https://boh/1999-DRM.pdf} \\ Mariotto, G. and {\bf Vinegoni, C.} and Jacobsohn, L. G. and Freire$^\#$, F. L. \\ ``Diamond and Related Materials'' Vol. 8 (1999) pp. 668-672. \\ DOI: 10.1016/s0925-9635(98)00328-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Resonant second harmonic generation in ZnSe bulk microcavity}{https://boh/1999-APL.pdf} \\ Pellegrini, V. and Colombelli, R. and Carusotto, I. and Beltram, F. and Rubini, S. and Lantier, R. and Franciosi, A. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Applied Physics Letters'' Vol. 74 (1999) pp. 1945-1947. \\ DOI: 10.1063/1.123736 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Radiative emission properties of a-SiN : H based nanometric multilayers for light emitting devices}{https://boh/1998-JL.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Journal of Luminescence'' Vol. 80 (1998) pp. 423-427. \\ DOI: 10.1016/s0022-2313(98)00141-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  X-ray diffraction, extended x-ray absorption fine structure and Raman spectroscopy studies of WO3 powders and, (1-x)WO3-y center dot xReO(2) mixtures}{https://boh/1998-JAP.pdf} \\ Kuzmin$^\#$, A. and Purans, J. and Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. \\ ``Journal of Applied Physics'' Vol. 84 (1998) pp. 5515-5524. \\ DOI: 10.1063/1.368596 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Photoluminescence of localized excitons in pulsed-laser-deposited GaN}{https://boh/1998-APL.pdf} \\ Cazzanelli$^\#$, M. and Cole, D. and Donegan, J. F. and Lunney, J. G. and Middleton, P. G. and O'Donnell, K. P. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Applied Physics Letters'' Vol. 73 (1998) pp. 3390-3392. \\ DOI: 10.1063/1.122776 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Spatiotemporal multiplexed immunofluorescence imaging of living cells and tissues with bioorthogonal cycling of fluorescent probes}{https://boh/2022-NB.pdf} \\ Ko, J.A. and Wilkovitsch, M. and Oh, J. and Kohler, R.H. and Bolli, E. and Pittet, M.J. and {\bf Vinegoni, C.} and Sykes, D.B. and Mikula, H. and Weissleder, R. and Carlson$^\#$, J.C.T. \\ ``Nature Biotechnology'' Vol. N/A (2022) pp. online. \\ DOI: 10.1038/s41587-022-01339-6 PMID: 35654978 PMCID: N/A\item \htmladdnormallink{\it  Neutrophils incite and macrophages avert electrical storm after myocardial infarction}{https://boh/2022-NCR-2.pdf} \\ Grune, J. and Lewis, A.J.M. and Yamazoe, M. and Hulsmans, M. and Rohde, D. and Xiao, L. and Zhang, S. and Ott, C. and Calcagno, D.M. and Zhou, Y. and Timm, K. and Shanmuganathan, M. and Pulous, F.E. and Schloss, M.J. and Foy, B.H. and Capen, D. and {\bf Vinegoni, C.} and Wojtkiewicz, G.R. and Iwamoto, I. and Grune, T. and Brown, D. and Higgins, J. and Ferreira, V.M. and Herring, N. and Channon, K.M. and Neubauer, S. and Oxford Acute Myocardial Infarction (OxAMI) Study and Sosnovik, D.E. and Milan, D.J. and Swirski, F.K. and King, K.R. and Aguirre, A.D. and Ellinor, P.T. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 649–664. \\ DOI: 10.1038/s44161-022-00094-w PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Cerebrospinal fluid can exit into the skull bone marrow and instruct cranial hematopoiesis in mice with bacterial meningitis}{https://boh/2022-NN.PDF} \\ Pulous, F. E. and Cruz-Hernandez, J. C. and Yang, C. B. and Kaya, Z. and Paccalet, A. and Wojtkiewicz, G. and Capen, D. and Brown, D. and Wu, J. W. and Schloss, M. J. and {\bf Vinegoni, C.} and Richter, D. and Yamazoe, M. and Hulsmans, M. and Momin, N. and Grune, J. and Rohde, D. and McAlpine, C. S. and Panizzi, P. and Weissleder, R. and Kim, D. E. and Swirski, F. K. and Lin, C. P. and Moskowitz, M. A. and Nahrendorf, M. \\ ``Nature Neuroscience'' Vol. 25 (2022) pp. 567-+. \\ DOI: 10.1038/s41593-022-01060-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Bone marrow endothelial dysfunction promotes myeloid cell expansion in cardiovascular disease}{https://boh/2022-NCR-1.pdf} \\ Rohde, D. and Vandoorne, K. and Lee, I. H. and Grune, J. and Zhang, S. and McAlpine, C. S. and Schloss, M. J. and Nayar, R. and Courties, G. and Frodermann, V. and Wojtkiewicz, G. and Honold, L. and Chen, Q. and Schmidt, S. and Iwamoto, Y. and Sun, Y. and Cremer, S. and Hoyer, F. F. and Iborra-Egea, O. and Muñoz-Guijosa, C. and Ji, F. and Zhou, G. and Adams, R. H. and Wythe, J. D. and Hidalgo, J. and Watanabe, H. and Jung, Y. and van der Laan, A. M. and Piek, J. J. and Kfoury, Y. and Désogère, P. A. and {\bf Vinegoni, C.} and Dutta, P. and Sadreyev, R. I. and Caravan, P. and Bayes-Genis, A. and Libby, P. and Scadden, D. T. and Lin, C. P. and Naxerova, K. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 28-44. \\ DOI: 10.1038/s44161-021-00002-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Astrocytic interleukin-3 programs microglia and limits Alzheimer's disease}{https://boh/2021-NATURE.pdf} \\ McAlpine, C. S. and Park, J. and Griciuc, A. and Kim, E. and Choi, S. H. and Iwamoto, Y. and Kiss, M. G. and Christie, K. A. and {\bf Vinegoni, C.} and Poller, W. C. and Mindur, J. E. and Chan, C. T. and He, S. and Janssen, H. and Wong, L. P. and Downey, J. and Singh, S. and Anzai, A. and Kahles, F. and Jorfi, M. and Feruglio, P. F. and Sadreyev, R. I. and Weissleder, R. and Kleinstiver, B. P. and Nahrendorf, M. and Tanzi, R. E. and Swirski$^\#$, F. K. \\ ``Nature'' Vol. 595 (2021) pp. 701-+. \\ DOI: 10.1038/s41586-021-03734-6 PMID: 34262178 PMCID: PMC8934148\item \htmladdnormallink{\it  CytoPAN-Portable cellular analyses for rapid point-of-care cancer diagnosis}{https://boh/2020-STM.pdf} \\ Min, J. and Chin, L. K. and Oh, J. and Landeros, C. and {\bf Vinegoni, C.} and Lee, J. and Lee, S. J. and Park, J. Y. and Liu, A. Q. and Castro, C. M. and Lee, H. and Im, H. and Weissleder$^\#$, R. \\ ``Science Translational Medicine'' Vol. 12 (2020) pp. 14. \\ DOI: 10.1126/scitranslmed.aaz9746 PMID: 32759277 PMCID: PMC8217912\item \htmladdnormallink{\it  Fluorescence microscopy tensor imaging representations for large-scale dataset analysis}{https://boh/2020-SCIREP.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Feruglio$^\dag$, P. F. and Courties, G. and Schmidt, S. and Hulsmans, M. and Lee, S. and Wang, R. and Sosnovik, D. and Nahrendorf, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 10 (2020) pp. 15. \\ DOI: 10.1038/s41598-020-62233-2 PMID: 32221334 PMCID: PMC7101442\item \htmladdnormallink{\it  Extended dynamic range imaging for noise mitigation in fluorescence anisotropy imaging}{https://boh/2020-JBO.pdf} \\ Feruglio$^\dag$, P. F. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 25 (2020) pp. 13. \\ DOI: 10.1117/1.Jbo.25.8.086003 PMID: 32820624 PMCID: PMC7439791\item \htmladdnormallink{\it  Diminished Reactive Hematopoiesis and Cardiac Inflammation in a Mouse Model of Recurrent Myocardial Infarction}{https://boh/2020-JAMCC.pdf} \\ Cremer, S. and Schloss, M. J. and {\bf Vinegoni, C.} and Foy, B. H. and Zhang, S. and Rohde, D. and Hulsmans, M. and Feruglio, P. F. and Schmidt, S. and Wojtkiewicz, G. and Higgins, J. M. and Weissleder, R. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 75 (2020) pp. 901-915. \\ DOI: 10.1016/j.jacc.2019.12.056 PMID: 32130926 PMCID: PMC7254576\item \htmladdnormallink{\it  Characterization of single microvesicles in plasma from glioblastoma patients}{https://boh/2019-NO.pdf} \\ Fraser, K. and Jo, A. and Giedt, J. and {\bf Vinegoni, C.} and Yang, K. S. and Peruzzi, P. and Chiocca, E. A. and Breakefield, X. O. and Lee, H. and Weissleder$^\#$, R. \\ ``Neuro-Oncology'' Vol. 21 (2019) pp. 606-615. \\ DOI: 10.1093/neuonc/noy187 PMID: 30561734 PMCID: 6502493\item \htmladdnormallink{\it  High Dynamic Range Fluorescence Imaging}{https://boh/2019-JSTQE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 25 (2019) pp. 7. \\ DOI: 10.1109/jstqe.2018.2881608 PMID: 31598059 PMCID: PMC6785194\item \htmladdnormallink{\it  Fluorescence anisotropy imaging in drug discovery}{https://boh/2019-ADDR.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Gryczynski, I. and Mazitschek, R. and Weissleder, R. \\ ``Advanced Drug Delivery Reviews'' Vol. 151 (2019) pp. 262-288. \\ DOI: 10.1016/j.addr.2018.01.019 PMID: 29410158 PMCID: 6072632\item \htmladdnormallink{\it  The anti-tumor diterpene oridonin is a direct inhibitor of Nucleolin in cancer cells}{https://boh/2018-SCIREP.pdf} \\ Vasaturo, M. and Cotugno, R. and Fiengo, L. and {\bf Vinegoni, C.} and Dal Piaz, F. and De Tommasi$^\#$, N. \\ ``Scientific Reports'' Vol. 8 (2018) pp. 13. \\ DOI: 10.1038/s41598-018-35088-x PMID: 30425290 PMCID: 6233161\item \htmladdnormallink{\it  Direct vascular channels connect skull bone marrow and the brain surface enabling myeloid cell migration}{https://boh/2018-NATNEURO.pdf} \\ Herisson, F. and Frodermann, V. and Courties, G. and Rohde, D. and Sun, Y. and Vandoorne, K. and Wojtkiewicz, G. R. and Masson, G. S. and {\bf Vinegoni, C.} and Kim, J. and Kim, D. E. and Weissleder, R. and Swirski, F. K. and Moskowitz, M. A. and Nahrendorf$^\#$, M. \\ ``Nature Neuroscience'' Vol. 21 (2018) pp. 1209-+. \\ DOI: 10.1038/s41593-018-0213-2 PMID: 30150661 PMCID: PMC6148759 \item \htmladdnormallink{\it  Cardiac macrophages promote diastolic dysfunction}{https://boh/2018-JEM.pdf} \\ Hulsmans, M. and Sager, H. B. and Roh, J. D. and Valero-Munoz, M. and Houstis, N. E. and Iwamoto, Y. and Sun, Y. and Wilson, R. M. and Wojtkiewicz, G. and Tricot, B. and Osborne, M. T. and Hung, J. and {\bf Vinegoni, C.} and Naxerova, K. and Sosnovik, D. E. and Zile, M. R. and Bradshaw, A. D. and Liao, R. and Tawakol, A. and Weissleder, R. and Rosenzweig, A. and Swirski, F. K. and Sam, F. and Nahrendorf$^\#$, M. \\ ``Journal of Experimental Medicine'' Vol. 215 (2018) pp. 423-440. \\ DOI: 10.1084/jem.20171274 PMID: 29339450 PMCID: PMC3366498\item \htmladdnormallink{\it  Imaging the Vascular Bone Marrow Niche During Inflammatory Stress}{https://boh/2018-CIRCRES.pdf} \\ Vandoorne, K. and Rohde, D. and Kim, H. Y. and Courties, G. and Wojtkiewicz, G. and Honold, L. and Hoyer, F. F. and Frodermann, V. and Nayar, R. and Herisson, F. and Jung, Y. and Desogere, P. A. and {\bf Vinegoni, C.} and Caravan, P. and Weissleder, R. and Sosnovik, D. E. and Lin, C. P. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Circulation Research'' Vol. 123 (2018) pp. 415-427. \\ DOI: 10.1161/circresaha.118.313302 PMID: 29980569 PMCID: 6202141\item \htmladdnormallink{\it  Design and Development of Fluorescent Vemurafenib Analogs for In Vivo Imaging}{https://boh/2017-THERA.pdf} \\ Mikula, H. and Stapleton, S. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Theranostics'' Vol. 7 (2017) pp. 1257-1265. \\ DOI: 10.7150/thno.18238 PMID: 28435463 PMCID: PMC5399591\item \htmladdnormallink{\it  Measurement of drug-target engagement in live cells by two-photon fluorescence anisotropy imaging}{https://boh/2017-NP.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Brand, C. and Lee, S. and Nibbs, A. E. and Stapleton, S. and Shah, S. and Gryczynski, I. and Reiner, T. and Mazitschek, R. and Weissleder, R. \\ ``Nature Protocols'' Vol. 12 (2017) pp. 1472-1497. \\ DOI: 10.1038/nprot.2017.043 PMID: 28686582 PMCID: PMC5928516\item \htmladdnormallink{\it  Quantitating drug-target engagement in single cells in vitro and in vivo}{https://boh/2017-NCBIOL.pdf} \\ Dubach, J. M. and Kim, E. and Yang, K. and Cuccarese, M. and Giedt, R. J. and Meirnetis, L. G. and {\bf Vinegoni$^\#$, C.} and Weissleder$^\#$, R. \\ ``Nature Chemical Biology'' Vol. 13 (2017) pp. 168-173. \\ DOI: 10.1038/nchembio.2248 PMID: 27918558 PMCID: PMC5630128\item \htmladdnormallink{\it  Motion characterization scheme to minimize motion artifacts in intravital microscopy}{https://boh/2017-JBO.pdf} \\ Lee, S. and Courties, G. and Nahrendorf, M. and Weissleder, R. and {\bf Vinegoni$^\#$, C.} \\ ``Journal of Biomedical Optics'' Vol. 22 (2017) pp. 7. \\ DOI: 10.1117/1.Jbo.22.3.036005 PMID: 28253383 PMCID: PMC5333764\item \htmladdnormallink{\it  Macrophages Facilitate Electrical Conduction in the Heart}{https://boh/2017-CELL.pdf} \\ Hulsmans, M. and Clauss, S. and Xiao, L. and Aguirre, A. D. and King, K. R. and Hanley, A. and Hucker, W. J. and Wulfers, E. M. and Seemann, G. and Courties, G. and Iwamoto, Y. and Sun, Y. and Savol, A. J. and Sager, H. B. and Lavine, K. J. and Fishbein, G. A. and Capen, D. E. and Da Silva, N. and Miquerol, L. and Wakimoto, H. and Seidman, C. E. and Seidman, J. G. and Sadreyev, R. I. and Naxerova, K. and Mitchell, R. N. and Brown, D. and Libby, P. and Weissleder, R. and Swirski, F. K. and Kohl, P. and {\bf Vinegoni, C.} and Milan, D. J. and Ellinor, P. T. and Nahrendorf$^\#$, M. \\ ``Cell'' Vol. 169 (2017) pp. 510-+. \\ DOI: 10.1016/j.cell.2017.03.050 PMID: 28431249 PMCID: PMC5474950\item \htmladdnormallink{\it  Transparent Electrophysiology Microelectrodes and Interconnects from Meta Nanomesh}{https://boh/2017-ACSN.pdf} \\ Seo, K. J. and Qiang, Y. and Bilgin, I. and Kar, S. and {\bf Vinegoni, C.} and Weissleder, R. and Fang$^\#$, H. \\ ``Acs Nano'' Vol. 11 (2017) pp. 4365-4372. \\ DOI: 10.1021/acsnano.7b01995 PMID: 28391679 PMCID: N/A\item \htmladdnormallink{\it  Two-photon imaging of pancreatic beta cells in real time in vivo}{https://boh/2016-TECHNOL.pdf} \\ Clardy, S. M. and Kohler, R. and {\bf Vinegoni, C.} and Iwamoto, Y. and Keliher, E. and Weissleder$^\#$, R. \\ ``Technology'' Vol. 4 (2016) pp. 130-34. \\ DOI: 10.1142/S2339547816200028 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  RNAi targeting multiple cell adhesion molecules reduces immune cell recruitment and vascular inflammation after myocardial infarction}{https://boh/2016-STM.pdf} \\ Sager, H. B. and Dutta, P. and Dahlman, J. E. and Hulsmans, M. and Courties, G. and Sun, Y. and Heidt, T. and {\bf Vinegoni, C.} and Borodovsky, A. and Fitzgerald, K. and Wojtkiewicz, G. R. and Iwamoto, Y. and Tricot, B. and Khan, O. F. and Kauffman, K. J. and Xing, Y. P. and Shaw, T. E. and Libby, P. and Langer, R. and Weissleder, R. and Swirski, F. K. and Anderson, D. G. and Nahrendorf$^\#$, M. \\ ``Science Translational Medicine'' Vol. 8 (2016) pp. 11. \\ DOI: 10.1126/scitranslmed.aaf1435 PMID: 27280687 PMCID: PMC5125383\item \htmladdnormallink{\it  Computational imaging reveals mitochondrial morphology as a biomarker of cancer phenotype and drug response}{https://boh/2016-SCIREP.pdf} \\ Giedt, R. J. and Fumene Feruglio, P. and Pathania, D. and Yang, K. S. and Kilcoyne, A. and {\bf Vinegoni, C.} and Mitchison, T. J. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 6 (2016) pp. 10. \\ DOI: 10.1038/srep32985 PMID: 27609668 PMCID: PMC5017129\item \htmladdnormallink{\it  Real-time high dynamic range laser scanning microscopy}{https://boh/2016-NCOMM-2.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Swisher$^\dag$, C. L. and Fumene Feruglio$^\dag$, P. and Giedt, R. J. and Rousso, D. L. and Stapleton, S. and Weissleder, R. \\ ``Nature Communications'' Vol. 7 (2016) pp. 13. \\ DOI: 10.1038/ncomms11077 PMID: 27032979 PMCID: PMC4821995\item \htmladdnormallink{\it  Tyrosine kinase-mediated axial motility of basal cells revealed by intravital imaging}{https://boh/2016-NCOMM-1.pdf} \\ Roy, J. and Kim, B. and Hill, E. and Visconti, P. and Krapf, D. and {\bf Vinegoni, C.} and Weissleder, R. and Brown, D. and Breton$^\#$, S. \\ ``Nature Communications'' Vol. 7 (2016) pp. 11. \\ DOI: 10.1038/ncomms10666 PMID: 26868824 PMCID: PMC4754344\item \htmladdnormallink{\it  Two-Photon Fluorescence Anisotropy Microscopy for Imaging and Direct Measurement of Intracellular Drug Target Engagement}{https://boh/2016-IEEE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 22 (2016) pp. 7. \\ DOI: 10.1109/jstqe.2015.2501384 PMID: 27440991 PMCID: PMC4946648\item \htmladdnormallink{\it  Rapid, high efficiency isolation of pancreatic beta-cells}{https://boh/2015-SREP.pdf} \\ Clardy, S. M. and Mohan, J. F. and {\bf Vinegoni, C.} and Keliher, E. J. and Iwamoto, Y. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 5 (2015) pp. 9. \\ DOI: 10.1038/srep13681 PMID: 26330153 PMCID: PMC4557033\item \htmladdnormallink{\it  Imaging the beating heart in the mouse using intravital microscopy techniques}{https://boh/2015-NPROT.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Aguirre$^\dag$, A. D. and Lee, S. and Weissleder, R. \\ ``Nature Protocols'' Vol. 10 (2015) pp. 1802-1819. \\ DOI: 10.1038/nprot.2015.119 PMID: 26492138 PMCID: PMC5380003\item \htmladdnormallink{\it  New techniques for motion-artifact-free in vivo cardiac microscopy}{https://boh/2015-FPHYS.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Aguirre, A. D. and Weissleder, R. \\ ``Frontiers in Physiology'' Vol. 6 (2015) pp. 12. \\ DOI: 10.3389/fphys.2015.00147 PMID: 26029116 PMCID: PMC4428079\item \htmladdnormallink{\it  Advances in measuring single-cell pharmacology in vivo}{https://boh/2015-DDT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Thurber, G. M. and Miller, M. A. and Mazitschek, R. and Weissleder, R. \\ ``Drug Discovery Today'' Vol. 20 (2015) pp. 1087-1092. \\ DOI: 10.1016/j.drudis.2015.05.011 PMID: 26024776 PMCID: PMC4567932\item \htmladdnormallink{\it  Myocardial Infarction Activates CCR2(+) Hematopoietic Stem and Progenitor Cells}{https://boh/2015-CSC.pdf} \\ Dutta, P. and Sager, H. B. and Stengel, K. R. and Naxerova, K. and Courties, G. and Saez, B. and Silberstein, L. and Heidt, T. and Sebas, M. and Sun, Y. and Wojtkiewicz, G. and Fumene Feruglio, P. and King, K. and Baker, J. N. and van der Laan, A. M. and Borodovsky, A. and Fitzgerald, K. and Hulsmans, M. and Hoyer, F. and Iwamoto, Y. and {\bf Vinegoni, C.} and Brown, D. and Di Carli, M. and Libby, P. and Hiebert, S. W. and Scadden, D. T. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Cell Stem Cell'' Vol. 16 (2015) pp. 477-487. \\ DOI: 10.1016/j.stem.2015.04.008 PMID: 25957903 PMCID: PMC4426344\item \htmladdnormallink{\it  Automated motion artifact removal for intravital microscopy, without a priori information}{https://boh/2014-SR.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Sebas, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 4 (2014) pp. 9. \\ DOI: 10.1038/srep04507 PMID: 24676021 PMCID: PMC3968488\item \htmladdnormallink{\it  Intravital imaging of cardiac function at the single-cell level}{https://boh/2014-PNAS.pdf} \\ Aguirre, A. D. and {\bf Vinegoni$^\#$, C.} and Sebas, M. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 111 (2014) pp. 11257-11262. \\ DOI: 10.1073/pnas.1401316111 PMID: 25053815 PMCID: PMC4128110\item \htmladdnormallink{\it  Steady state anisotropy two-photon microscopy resolves multiple, spectrally similar fluorophores, enabling in vivo multilabel imaging}{https://boh/2014-OL.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Optics Letters'' Vol. 39 (2014) pp. 4482-4485. \\ DOI: 10.1364/ol.39.004482 PMID: 25078208 PMCID: PMC4341989\item \htmladdnormallink{\it  Chronic variable stress activates hematopoietic stem cells}{https://boh/2014-NM.pdf} \\ Heidt, T. and Sager, H. B. and Courties, G. and Dutta, P. and Iwamoto, Y. and Zaltsman, A. and von zur Muhlen, C. and Bode, C. and Fricchione, G. L. and Denninger, J. and Lin, C. P. and {\bf Vinegoni, C.} and Libby, P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature Medicine'' Vol. 20 (2014) pp. 754-758. \\ DOI: 10.1038/nm.3589 PMID: 24952646 PMCID: PMC4087061\item \htmladdnormallink{\it  In vivo imaging of specific drug-target binding at subcellular resolution}{https://boh/2014-NC.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Mazitschek, R. and Fumene Feruglio, P. and Cameron, L. A. and Weissleder, R. \\ ``Nature Communications'' Vol. 5 (2014) pp. 9. \\ DOI: 10.1038/ncomms4946 PMID: 24867710 PMCID: PMC4362617\item \htmladdnormallink{\it  Advanced Motion Compensation Methods for Intravital Optical Microscopy}{https://boh/2014-IEEE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 20 (2014) pp. 9. \\ DOI: 10.1109/jstqe.2013.2279314 PMID: 24273405 PMCID: PMC3832946\item \htmladdnormallink{\it  Perinatal health and translational medicine}{https://boh/2013-JHGD.pdf} \\ Figueiredo, J. L. and {\bf Vinegoni, C.} and De Abreu, L. C. \\ ``Journal of Human Growth and Development'' Vol. 23 (2013) pp. 125-127. \\ DOI: 10.7322/jhgd.61318 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Sequential average segmented microscopy for high signal-to-noise ratio motion-artifact-free in vivo heart imaging}{https://boh/2013-BOE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Marzola, P. and Nahrendorf, M. and Weissleder, R. \\ ``Biomedical Optics Express'' Vol. 4 (2013) pp. 2095-2106. \\ DOI: 10.1364/boe.4.002095 PMID: 24156067 PMCID: PMC3799669\item \htmladdnormallink{\it  Noise suppressed, multifocus image fusion for enhanced intraoperative navigation}{https://boh/2013-BIOPHTNCS.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Fexon, L. and Thurber, G. and Sbarbati, A. and Weissleder, R. \\ ``Journal of Biophotonics'' Vol. 6 (2013) pp. 363-370. \\ DOI: 10.1002/jbio.201200086 PMID: 22887724 PMCID: PMC3779878\item \htmladdnormallink{\it  Implantable microenvironments to attract hematopoietic stem/cancer cells}{https://boh/2012-PNAS.pdf} \\ Lee, J. and Li, M. and Milwid, J. and Dunham, J. and {\bf Vinegoni, C.} and Gorbatov, R. and Iwamoto, Y. and Wang, F. J. and Shen, K. Y. and Hatfield, K. and Enger, M. and Shafiee, S. and McCormack, E. and Ebert, B. L. and Weissleder, R. and Yarmush, M. L. and Parekkadan$^\#$, B. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 109 (2012) pp. 19638-19643. \\ DOI: 10.1073/pnas.1208384109 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Mapping Molecular Agents Distributions in Whole Mice Hearts Using Born-Normalized Optical Projection Tomography}{https://boh/2012-PLOSONE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio$^\dag$, P. and Razansky, D. and Gorbatov, R. and Ntziachristos, V. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Plos One'' Vol. 7 (2012) pp. 9. \\ DOI: 10.1371/journal.pone.0034427 PMID: 22509302 PMCID: PMC3324534\item \htmladdnormallink{\it  Imaging Therapeutic PARP Inhibition In Vivo through Bioorthogonally Developed Companion Imaging Agents}{https://boh/2012-NEOPLASIA.pdf} \\ Reiner, T. and Lacy, J. and Keliher, E. J. and Yang, K. S. and Ullal, A. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Neoplasia'' Vol. 14 (2012) pp. 169-+. \\ DOI: 10.1593/neo.12414 PMID: 22496617 PMCID: PMC3323895\item \htmladdnormallink{\it  Real-time in vivo imaging of the beating mouse heart at microscopic resolution}{https://boh/2012-NC.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Fexon, L. and Gorbatov, R. and Pivoravov, M. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Nature Communications'' Vol. 3 (2012) pp. 8. \\ DOI: 10.1038/ncomms2060 PMID: 22968700 PMCID: PMC3622400\item \htmladdnormallink{\it  Myocardial infarction accelerates atherosclerosis}{https://boh/2012-NATURE.pdf} \\ Dutta, P. and Courties, G. and Wei, Y. and Leuschner, F. and Gorbatov, R. and Robbins, C. S. and Iwamoto, Y. and Thompson, B. and Carlson, A. L. and Heidt, T. and Majmudar, M. D. and Lasitschka, F. and Etzrodt, M. and Waterman, P. and Waring, M. T. and Chicoine, A. T. and van der Laan, A. M. and Niessen, H. W. M. and Piek, J. J. and Rubin, B. B. and Butany, J. and Stone, J. R. and Katus, H. A. and Murphy, S. A. and Morrow, D. A. and Sabatine, M. S. and {\bf Vinegoni, C.} and Moskowitz, M. A. and Pittet, M. J. and Libby, P. and Lin, C. P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature'' Vol. 487 (2012) pp. 325-329. \\ DOI: 10.1038/nature11260 PMID: 22763456 PMCID: PMC3401326\item \htmladdnormallink{\it  Improved intravital microscopy via synchronization of respiration and holder stabilization}{https://boh/2012-JBO.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 17 (2012) pp. 8. \\ DOI: 10.1117/1.Jbo.17.9.096018 PMID: 23085919 PMCID: PMC3449295\item \htmladdnormallink{\it  PET/MRI of Inflammation in Myocardial Infarction}{https://boh/2012-JACC.pdf} \\ Lee, W. W. and Marinelli, B. and van der Laan, A. M. and Sena, B. F. and Gorbatov, R. and Leuschner, F. and Dutta, P. and Iwamoto, Y. and Ueno, T. and Begieneman, M. P. V. and Niessen, H. W. M. and Piek, J. J. and {\bf Vinegoni, C.} and Pittet, M. J. and Swirski, F. K. and Tawakol, A. and Di Carli, M. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 59 (2012) pp. 153-163. \\ DOI: 10.1016/j.jacc.2011.08.066 PMID: 22222080 PMCID: PMC3257823\item \htmladdnormallink{\it  Motion compensation using a suctioning stabilizer for intravital microscopy}{https://boh/2012-INTRVTL.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Gorbatov, R. and Weissleder, R. \\ ``Intravital'' Vol. 1 (2012) pp. 115. \\ DOI: 10.4161/intv.23017 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Deep Tissue Optical and Optoacoustic Molecular Imaging Technologies for Pre-Clinical Research and Drug Discovery}{https://boh/2012-CPB.pdf} \\ Razansky$^\#$, D. and Deliolanis, N. C. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Current Pharmaceutical Biotechnology'' Vol. 13 (2012) pp. 504-522. \\ DOI: 10.2174/138920112799436258 PMID: 22216767 PMCID: N/A\item \htmladdnormallink{\it  In Vivo Imaging of Drug-Induced Mitochondrial Outer Membrane Permeabilization at Single-Cell Resolution}{https://boh/2012-CNCRRES.pdf} \\ Earley, S. and {\bf Vinegoni, C.} and Dunham, J. and Gorbatov, R. and Fumene Feruglio, P. and Weissleder$^\#$, R. \\ ``Cancer Research'' Vol. 72 (2012) pp. 2949-2956. \\ DOI: 10.1158/0008-5472.Can-11-4096 PMID: 22505651 PMCID: PMC3603290\item \htmladdnormallink{\it  Optochemogenetics (OCG) Allows More Precise Control of Genetic Engineering in Mice with CreER regulators}{https://boh/2012-BIOCHEM.pdf} \\ Lu, X. and Agasti, S. S. and {\bf Vinegoni, C.} and Waterman, P. and DePinho, R. A. and Weissleder$^\#$, R. \\ ``Bioconjugate Chemistry'' Vol. 23 (2012) pp. 1945-1951. \\ DOI: 10.1021/bc300319c PMID: 22917215 PMCID: PMC3775343\item \htmladdnormallink{\it  Bioorthogonal Imaging of Aurora Kinase A in Live Cells}{https://boh/2012-AC.pdf} \\ Yang, K. S. and Budin, G. and Reiner, T. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Angewandte Chemie-International Edition'' Vol. 51 (2012) pp. 6598-6603. \\ DOI: 10.1002/anie.201200994 PMID: 22644700 PMCID: PMC3523717\item \htmladdnormallink{\it  Indocyanine Green Enables Near-Infrared Fluorescence Imaging of Lipid-Rich, Inflamed Atherosclerotic Plaques}{https://boh/2011-STM.pdf} \\ {\bf Vinegoni, C.} and Botnaru, I. and Aikawa, E. and Calfon, M. A. and Iwamoto, Y. and Folco, E. J. and Ntziachristos, V. and Weissleder, R. and Libby, P. and Jaffer$^\#$, F. A. \\ ``Science Translational Medicine'' Vol. 3 (2011) pp. 9. \\ DOI: 10.1126/scitranslmed.3001577 PMID: 21613624 PMCID: PMC3112179\item \htmladdnormallink{\it  Accurate measurement of pancreatic islet beta-cell mass using a second-generation fluorescent exendin-4 analog}{https://boh/2011-PNAS.pdf} \\ Reiner, T. and Thurber, G. and Gaglia, J. and {\bf Vinegoni, C.} and Liew, C. W. and Upadhyay, R. and Kohler, R. H. and Li, L. and Kulkarni, R. N. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 108 (2011) pp. 12815-12820. \\ DOI: 10.1073/pnas.1109859108 PMID: 21768367 PMCID: PMC3150928\item \htmladdnormallink{\it  A multimodal approach for tracing lateralisation along the olfactory pathway in the honeybee through electrophysiological recordings, morpho-functional imaging, and behavioural studies}{https://boh/2011-EB.pdf} \\ Haase, A. and Rigosi, E. and Frasnelli, E. and Trona, F. and Tessarolo, F. and {\bf Vinegoni, C.} and Anfora, G. and Vallortigara, G. and Antolini$^\#$, R. \\ ``European Biophysics Journal with Biophysics Letters'' Vol. 40 (2011) pp. 1247-1258. \\ DOI: 10.1007/s00249-011-0748-6 PMID: 21956452 PMCID: PMC3366498\item \htmladdnormallink{\it  Searching for anatomical correlates of olfactory lateralization in the honeybee antennal lobes: A morphological and behavioural study}{https://boh/2011-BBR.pdf} \\ Rigosi$^\#$, E. and Frasnelli, E. and {\bf Vinegoni, C.} and Antolini, R. and Anfora, G. and Vallortigara, G. and Haase, A. \\ ``Behavioural Brain Research'' Vol. 221 (2011) pp. 290-294. \\ DOI: 10.1016/j.bbr.2011.03.015 PMID: 21402106 PMCID: PMC3089663\item \htmladdnormallink{\it  Intraoperative Near-infrared Fluorescent Cholangiography (NIRFC) in Mouse Models of Bile Duct Injury: Reply}{https://boh/2010-WJS.pdf} \\ Figueiredo, J. L. and Nahrendorf, M. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``World Journal of Surgery'' Vol. 35 (2011) pp. 694-695. \\ DOI: 10.1007/s00268-010-0728-5 PMID: 20645091 PMCID: N/A\item \htmladdnormallink{\it  Hybrid PET-optical imaging using targeted probes}{https://boh/2010-PNAS.pdf} \\ Nahrendorf$^{\dag \#}$, M. and Keliher$^\dag$, E. and Marinelli, B. and Waterman, P. and Fumene Feruglio, P. and Fexon, L. and Pivovarov, M. and Swirski, F. K. and Pittet, M. J. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 107 (2010) pp. 7910-7915. \\ DOI: 10.1073/pnas.0915163107 PMID: 20385821 PMCID: PMC2867879\item \htmladdnormallink{\it  Block matching 3D random noise filtering for absorption optical projection tomography}{https://boh/2010-PMB.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Gros, J. and Sbarbati, A. and Weissleder, R. \\ ``Physics in Medicine and Biology'' Vol. 55 (2010) pp. 5401-5415. \\ DOI: 10.1088/0031-9155/55/18/009 PMID: 20736500 PMCID: PMC2934766\item \htmladdnormallink{\it  Imaging of molecular probe activity with Born-normalized fluorescence optical projection tomography}{https://boh/2010-OL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Cortez-Retamozo, V. and Razansky, D. and Medoff, B. D. and Ntziachristos, V. and Sbarbati, A. and Pittet, M. and Weissleder, R. \\ ``Optics Letters'' Vol. 35 (2010) pp. 1088-1090. \\ DOI: 10.1364/ol.35.001088 PMID: 20364226 PMCID: PMC2900933\item \htmladdnormallink{\it  Intravascular near-infrared fluorescence molecular imaging of atherosclerosis: toward coronary arterial visualization of biologically high-risk plaques}{https://boh/2010-JBO.pdf} \\ Calfon, M. A. and {\bf Vinegoni, C.} and Ntziachristos, V. and Jaffer$^\#$, F. A. \\ ``Journal of Biomedical Optics'' Vol. 15 (2010) pp. 6. \\ DOI: 10.1117/1.3280282 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  WNT5A/JNK and FGF/MAPK Pathways Regulate the Cellular Events Shaping the Vertebrate Limb Bud}{https://boh/2010-CB.pdf} \\ Gros, J. and Hu, J. K. H. and {\bf Vinegoni, C.} and Fumene Feruglio, P. and Weissleder, R. and Tabin$^\#$, C. J. \\ ``Current Biology'' Vol. 20 (2010) pp. 1993-2002. \\ DOI: 10.1016/j.cub.2010.09.063 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  In-vivo two-photon imaging of the honey bee antennal lobe}{https://boh/2010-BOEX.pdf} \\ Haase, A. and Rigosi, E. and Trona, F. and Anfora, G. and Vallortigara, G. and Antolini, R. and {\bf Vinegoni$^\#$, C.} \\ ``Biomedical Optics Express'' Vol. 2 (2011) pp. 131-138. \\ DOI: 10.1364/boe.2.000131 PMID: 21326643 PMCID: PMC3028488\item \htmladdnormallink{\it  Imaging of mesoscopic-scale organisms using selective-plane optoacoustic tomography}{https://boh/2009-PMB.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Physics in Medicine and Biology'' Vol. 54 (2009) pp. 2769-2777. \\ DOI: 10.1088/0031-9155/54/9/012 PMID: 19369709 PMCID: N/A\item \htmladdnormallink{\it  Normalized Born ratio for fluorescence optical projection tomography}{https://boh/2009-OL-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 319-321. \\ DOI: 10.1364/ol.34.000319 PMID: 19183644 PMCID: PMC2771918\item \htmladdnormallink{\it  Transillumination fluorescence imaging in mice using biocompatible upconverting nanoparticles}{https://boh/2009-OL-1.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Razansky$^\dag$, D. and Hilderbrand, S. A. and Shao, F. W. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 2566-2568. \\ DOI: 10.1364/ol.34.002566 PMID: 19724491 PMCID: PMC2749971\item \htmladdnormallink{\it  Diffractionless beam in free space with adiabatic changing refractive index in a single mode tapered slab waveguide}{https://boh/2009-OE-2.pdf} \\ Tsai$^\#$, C. C. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 21723-21731. \\ DOI: 10.1364/oe.17.021723 PMID: 19997414 PMCID: PMC2805120\item \htmladdnormallink{\it  High throughput transmission optical projection tomography using low cost graphics processing unit}{https://boh/2009-OE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fexon, L. and Fumene Feruglio, P. and Pivovarov, M. and Figueiredo, J. L. and Nahrendorf, M. and Pozzo, A. and Sbarbati, A. and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 22320-22332. \\ DOI: 10.1364/oe.17.022320 PMID: 20052155 PMCID: PMC2805020\item \htmladdnormallink{\it  Multispectral opto-acoustic tomography of deep-seated fluorescent proteins in vivo}{https://boh/2009-NATPHOT.pdf} \\ Razansky$^\#$, D. and Distel, M. and {\bf Vinegoni, C.} and Ma, R. and Perrimon, N. and Koster, R. W. and Ntziachristos$^\#$, V. \\ ``Nature Photonics'' Vol. 3 (2009) pp. 412-417. \\ DOI: 10.1038/nphoton.2009.98 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Mesoscopic Fluorescence Tomography for In-vivo Imaging of Developing Drosophila}{https://boh/2009-JOVE-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Pitsouli, C. and Perrimon, N. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1510. \\ DOI: 10.3791/1510 PMID: 19696720 PMCID: PMC2736679\item \htmladdnormallink{\it  Born normalization for fluorescence optical projection tomography for whole heart imaging}{https://boh/2009-JOVE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Fexon, L. and Pivoravov, M. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1389. \\ DOI: 10.3791/1389 PMID: 19578329 PMCID: PMC2794886\item \htmladdnormallink{\it  Unprecedent in vivo views at the mesoscopic scale}{https://boh/2009-BOW.pdf} \\ Razansky, R. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``BioOptics World'' Vol. 2 (2009) pp. 22. \\ DOI: N/A PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Polarization-sensitive optoacoustic tomography of optically diffuse tissues}{https://boh/2008-OL.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Optics Letters'' Vol. 33 (2008) pp. 2308-2310. \\ DOI: 10.1364/ol.33.002308 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  In vivo imaging of Drosophila melanogaster pupae with mesoscopic fluorescence tomography}{https://boh/2008-NM.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Pitsouli$^\dag$, C. and Razansky$^\dag$, D. and Perrimon, N. and Ntziachristos, V. \\ ``Nature Methods'' Vol. 5 (2008) pp. 45-47. \\ DOI: 10.1038/nmeth1149 PMID: 18066071 PMCID: N/A\item \htmladdnormallink{\it  Real-time assessment of inflammation and treatment response in a mouse model of allergic airway inflammation}{https://boh/2008-JCI.pdf} \\ Cortez-Retamozo, V. and Swirski, F. K. and Waterman, P. and Yuan, H. and Figueiredo, J. L. and Newton, A. P. and Upadhyay, R. and {\bf Vinegoni, C.} and Kohler, R. and Blois, J. and Smith, A. and Nahrendorf, M. and Josephson, L. and Weissleder, R. and Pittet$^\#$, M. J. \\ ``Journal of Clinical Investigation'' Vol. 118 (2008) pp. 4058-4066. \\ DOI: 10.1172/jci36335 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  Real-Time Catheter Molecular Sensing of Inflammation in Proteolytically Active Atherosclerosis}{https://boh/2008-CRCLT.pdf} \\ Jaffer, F. A. and {\bf Vinegoni, C.} and John, M. C. and Aikawa, E. and Gold, H. K. and Finn, A. V. and Ntziachristos, V. and Libby, P. and Weissleder$^\#$, R. \\ ``Circulation'' Vol. 118 (2008) pp. 1802-1809. \\ DOI: 10.1161/circulationaha.108.785881 PMID: 18852366 PMCID: PMC2729441\item \htmladdnormallink{\it  Multispectral photoacoustic imaging of fluorochromes in small animals}{https://boh/2007-OL.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``Optics Letters'' Vol. 32 (2007) pp. 2891-2893. \\ DOI: 10.1364/ol.32.002891 PMID: 17909608 PMCID: N/A\item \htmladdnormallink{\it  Imaging cellular responses to mechanical stimuli within three-dimensional tissue constructs}{https://boh/2007-MRT.pdf} \\ Tan, W. and {\bf Vinegoni, C.} and Norman, J. J. and Desai, T. A. and Boppart$^\#$, S. A. \\ ``Microscopy Research and Technique'' Vol. 70 (2007) pp. 361-371. \\ DOI: 10.1002/jemt.20420 PMID: 17262787 PMCID: N/A\item \htmladdnormallink{\it  High-spectral-resolution coherent anti-Stokes Raman scattering with interferometric ally detected broadband chirped pulses}{https://boh/2006-OL-2.pdf} \\ Jones, G. W. and Marks, D. L. and {\bf Vinegoni, C.} and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1543-1545. \\ DOI: 10.1364/ol.31.001543 PMID: 16642166 PMCID: N/A\item \htmladdnormallink{\it  Spectroscopic spectral-domain optical coherence microscopy}{https://boh/2006-OL-1.pdf} \\ Xu, C. Y. and {\bf Vinegoni, C.} and Ralston, T. S. and Luo, W. and Tan, W. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1079-1081. \\ DOI: 10.1364/ol.31.001079 PMID: 16625909 PMCID: N/A\item \htmladdnormallink{\it  Integrated structural and functional optical imaging combining spectral-domain optical coherence and multiphoton microscopy}{https://boh/2006-APL.pdf} \\ {\bf Vinegoni, C.} and Ralston, T. and Tan, W. and Luo, W. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 88 (2006) pp. 3. \\ DOI: 10.1063/1.2171477 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Nonlinear Interferometric Vibrational Imaging. efficient detection of Coherent Anti-Stokes Raman Scattering}{https://boh/2005-OPN.pdf} \\ McAlpine, C. S. and Marks, D. and {\bf Vinegoni, C.} and Bredfeldt, J. and Boppart$^\#$, S.A. \\ ``Optics & Photonics News'' Vol. 16 (2005) pp. 23. \\ DOI: 10.1364/OPN.16.12.000023 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Molecularly sensitive optical coherence tomography}{https://boh/2005-OL.pdf} \\ Bredfeldt, J. S. and {\bf Vinegoni, C.} and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 30 (2005) pp. 495-497. \\ DOI: 10.1364/ol.30.000495 PMID: 15789714 PMCID: N/A\item \htmladdnormallink{\it  Nonlinear optical contrast enhancement for optical coherence tomography}{https://boh/2004-OE.pdf} \\ {\bf Vinegoni, C.} and Bredfeldt, J. S. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Express'' Vol. 12 (2004) pp. 331-341. \\ DOI: 10.1364/opex.12.000331 PMID: 19471542 PMCID: N/A\item \htmladdnormallink{\it  The statistics of polarization-dependent loss in a recirculating loop}{https://boh/2004-JLT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Karlsson, M. and Petersson, M. and Sunnerud, H. \\ ``Journal of Lightwave Technology'' Vol. 22 (2004) pp. 968-976. \\ DOI: 10.1109/jlt.2004.824861 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Interferometric differentiation between resonant coherent anti-Stokes Raman scattering and nonresonant four-wave-mixing processes}{https://boh/2004-APL.pdf} \\ Marks, D. L. and {\bf Vinegoni, C.} and Bredfeldt, J. S. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 85 (2004) pp. 5787-5789. \\ DOI: 10.1063/1.1829162 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed measurements of chromatic dispersion and nonlinear coefficient in low-PMD dispersion-shifted fibers}{https://boh/2003-PTL-2.pdf} \\ {\bf Vinegoni, C.} and Chen$^\#$, H. X. and Leblanc, M. and Schinn, G. W. and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 739-741. \\ DOI: 10.1109/lpt.2003.810249 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Statistics of PMD in recirculating loops}{https://boh/2003-PTL-1.pdf} \\ Petersson$^\#$, M. and {\bf Vinegoni, C.} and Sunnerud, H. and Karlsson, M. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 1543-1545. \\ DOI: 10.1109/lpt.2003.818681 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Emulator of first- and second-order polarization-mode dispersion}{https://boh/2002-PTL.pdf} \\ Wegmuller, M. and Demma, S. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 14 (2002) pp. 630-632. \\ DOI: 10.1109/68.998707 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Analysis of the polarization evolution in a ribbon cable using high-resolution coherent OFDR}{https://boh/2001-PTL-2.pdf} \\ Wegmuller, M. and Legre, M. and Oberson, P. and Guinnard, O. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 145-147. \\ DOI: 10.1109/68.910516 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurements of the nonlinear coefficient of standard SMF, DSF, and DCF fibers using a self-aligned interferometer and a Faraday mirror}{https://boh/2001-PTL-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 1337-1339. \\ DOI: 10.1109/68.969900 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Morphological and optical characterization of GaN prepared by pulsed laser deposition}{https://boh/2000-SCT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Cazzanelli, M. and Trivelli, A. and Mariotto, G. and Castro, J. and Lunney, J. G. and Levy, J. \\ ``Surface & Coatings Technology'' Vol. 124 (2000) pp. 272-277. \\ DOI: 10.1016/s0257-8972(99)00657-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Optical absorption and photoluminescence properties of alpha-Si1-xNx : H films deposited by plasma-enhanced CVD}{https://boh/2000-PRB.pdf} \\ Giorgis$^\#$, F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 61 (2000) pp. 4693-4698. \\ DOI: 10.1103/PhysRevB.61.4693 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  All optical switching in a highly birefringent and a standard telecom fiber using a Faraday mirror stabilization scheme}{https://boh/2000-OC.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Optics Communications'' Vol. 182 (2000) pp. 335-341. \\ DOI: 10.1016/s0030-4018(00)00845-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurement of nonlinear polarization rotation in a highly birefringent optical fibre using a Faraday mirror}{https://boh/2000-JOA.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Journal of Optics a-Pure and Applied Optics'' Vol. 2 (2000) pp. 314-318. \\ DOI: 10.1088/1464-4258/2/4/313 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed gain measurements in Er-doped fibers with high resolution and accuracy using an optical frequency domain reflectometer}{https://boh/2000-JLT.pdf} \\ Wegmuller$^\#$, M. and Oberson, P. and Guinnard, O. and Huttner, B. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin, N. \\ ``Journal of Lightwave Technology'' Vol. 18 (2000) pp. 2127-2132. \\ DOI: 10.1109/50.908823 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Determination of nonlinear coefficient n(2)/A(eff) using self-aligned interferometer and Faraday mirror}{https://boh/2000-EL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Electronics Letters'' Vol. 36 (2000) pp. 886-888. \\ DOI: 10.1049/el:20000668 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman study of the phase transitions sequence in pure WO3 at high temperature and in HxWO3 with variable hydrogen content}{https://boh/1999-SSI.pdf} \\ Cazzanelli$^\#$, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzmin, A. and Purans, J. \\ ``Solid State Ionics'' Vol. 123 (1999) pp. 67-74. \\ DOI: 10.1016/s0167-2738(99)00101-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescence processes in amorphous hydrogenated silicon-nitride nanometric multilayers}{https://boh/1999-PRB.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 60 (1999) pp. 11572-11576. \\ DOI: 10.1103/PhysRevB.60.11572 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescent properties of GaN thin films prepared by pulsed laser deposition}{https://boh/1999-MSEB.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Cole, D. and Lunney, J. G. and Middleton, P. G. and Trager-Cowan, C. and O'Donnell, K. P. and Pavesi$^\#$, L. \\ ``Materials Science and Engineering B-Solid State Materials for Advanced Technology'' Vol. 59 (1999) pp. 137-140. \\ DOI: 10.1016/s0921-5107(98)00333-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Low-temperature polymorphism in tungsten trioxide powders and its dependence on mechanical treatments}{https://boh/1999-JSSC.pdf} \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto$^\#$, G. and Kuzmin, A. and Purans, J. \\ ``Journal of Solid State Chemistry'' Vol. 143 (1999) pp. 24-32. \\ DOI: 10.1006/jssc.1998.8061 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Temperature dependence of the photoluminescence of all-porous-silicon optical microcavities}{https://boh/1999-JAP.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Journal of Applied Physics'' Vol. 85 (1999) pp. 1760-1764. \\ DOI: 10.1063/1.369320 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Color Centres and Polymorphism in Pure WO(3) and Mixed (1-x)WO(3-y)center dot xReO(2) Powders}{https://boh/1999-INCS.pdf} \\ Cazzanelli$^\#$, E. and Mariotto, G. and {\bf Vinegoni, C.} and Kuzmin, A. and Purans, J. \\ ``Ionics'' Vol. 5 (1999) pp. 335-344. \\ DOI: 10.1007/bf02375997 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman spectroscopy and scanning electron microscopy investigation of annealed amorphous carbon-germanium films deposited by d.c. magnetron sputtering}{https://boh/1999-DRM.pdf} \\ Mariotto, G. and {\bf Vinegoni, C.} and Jacobsohn, L. G. and Freire$^\#$, F. L. \\ ``Diamond and Related Materials'' Vol. 8 (1999) pp. 668-672. \\ DOI: 10.1016/s0925-9635(98)00328-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Resonant second harmonic generation in ZnSe bulk microcavity}{https://boh/1999-APL.pdf} \\ Pellegrini, V. and Colombelli, R. and Carusotto, I. and Beltram, F. and Rubini, S. and Lantier, R. and Franciosi, A. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Applied Physics Letters'' Vol. 74 (1999) pp. 1945-1947. \\ DOI: 10.1063/1.123736 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Radiative emission properties of a-SiN : H based nanometric multilayers for light emitting devices}{https://boh/1998-JL.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Journal of Luminescence'' Vol. 80 (1998) pp. 423-427. \\ DOI: 10.1016/s0022-2313(98)00141-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  X-ray diffraction, extended x-ray absorption fine structure and Raman spectroscopy studies of WO3 powders and, (1-x)WO3-y center dot xReO(2) mixtures}{https://boh/1998-JAP.pdf} \\ Kuzmin$^\#$, A. and Purans, J. and Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. \\ ``Journal of Applied Physics'' Vol. 84 (1998) pp. 5515-5524. \\ DOI: 10.1063/1.368596 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Photoluminescence of localized excitons in pulsed-laser-deposited GaN}{https://boh/1998-APL.pdf} \\ Cazzanelli$^\#$, M. and Cole, D. and Donegan, J. F. and Lunney, J. G. and Middleton, P. G. and O'Donnell, K. P. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Applied Physics Letters'' Vol. 73 (1998) pp. 3390-3392. \\ DOI: 10.1063/1.122776 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Spatiotemporal multiplexed immunofluorescence imaging of living cells and tissues with bioorthogonal cycling of fluorescent probes}{https://boh/2022-NB.pdf} \\ Ko, J.A. and Wilkovitsch, M. and Oh, J. and Kohler, R.H. and Bolli, E. and Pittet, M.J. and {\bf Vinegoni, C.} and Sykes, D.B. and Mikula, H. and Weissleder, R. and Carlson$^\#$, J.C.T. \\ ``Nature Biotechnology'' Vol. N/A (2022) pp. online. \\ DOI: 10.1038/s41587-022-01339-6 PMID: 35654978 PMCID: N/A\item \htmladdnormallink{\it  Neutrophils incite and macrophages avert electrical storm after myocardial infarction}{https://boh/2022-NCR-2.pdf} \\ Grune, J. and Lewis, A.J.M. and Yamazoe, M. and Hulsmans, M. and Rohde, D. and Xiao, L. and Zhang, S. and Ott, C. and Calcagno, D.M. and Zhou, Y. and Timm, K. and Shanmuganathan, M. and Pulous, F.E. and Schloss, M.J. and Foy, B.H. and Capen, D. and {\bf Vinegoni, C.} and Wojtkiewicz, G.R. and Iwamoto, I. and Grune, T. and Brown, D. and Higgins, J. and Ferreira, V.M. and Herring, N. and Channon, K.M. and Neubauer, S. and Oxford Acute Myocardial Infarction (OxAMI) Study and Sosnovik, D.E. and Milan, D.J. and Swirski, F.K. and King, K.R. and Aguirre, A.D. and Ellinor, P.T. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 649–664. \\ DOI: 10.1038/s44161-022-00094-w PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Cerebrospinal fluid can exit into the skull bone marrow and instruct cranial hematopoiesis in mice with bacterial meningitis}{https://boh/2022-NN.PDF} \\ Pulous, F. E. and Cruz-Hernandez, J. C. and Yang, C. B. and Kaya, Z. and Paccalet, A. and Wojtkiewicz, G. and Capen, D. and Brown, D. and Wu, J. W. and Schloss, M. J. and {\bf Vinegoni, C.} and Richter, D. and Yamazoe, M. and Hulsmans, M. and Momin, N. and Grune, J. and Rohde, D. and McAlpine, C. S. and Panizzi, P. and Weissleder, R. and Kim, D. E. and Swirski, F. K. and Lin, C. P. and Moskowitz, M. A. and Nahrendorf, M. \\ ``Nature Neuroscience'' Vol. 25 (2022) pp. 567-+. \\ DOI: 10.1038/s41593-022-01060-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Bone marrow endothelial dysfunction promotes myeloid cell expansion in cardiovascular disease}{https://boh/2022-NCR-1.pdf} \\ Rohde, D. and Vandoorne, K. and Lee, I. H. and Grune, J. and Zhang, S. and McAlpine, C. S. and Schloss, M. J. and Nayar, R. and Courties, G. and Frodermann, V. and Wojtkiewicz, G. and Honold, L. and Chen, Q. and Schmidt, S. and Iwamoto, Y. and Sun, Y. and Cremer, S. and Hoyer, F. F. and Iborra-Egea, O. and Muñoz-Guijosa, C. and Ji, F. and Zhou, G. and Adams, R. H. and Wythe, J. D. and Hidalgo, J. and Watanabe, H. and Jung, Y. and van der Laan, A. M. and Piek, J. J. and Kfoury, Y. and Désogère, P. A. and {\bf Vinegoni, C.} and Dutta, P. and Sadreyev, R. I. and Caravan, P. and Bayes-Genis, A. and Libby, P. and Scadden, D. T. and Lin, C. P. and Naxerova, K. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Nature Cardiovascular Research'' Vol. 1 (2022) pp. 28-44. \\ DOI: 10.1038/s44161-021-00002-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Astrocytic interleukin-3 programs microglia and limits Alzheimer's disease}{https://boh/2021-NATURE.pdf} \\ McAlpine, C. S. and Park, J. and Griciuc, A. and Kim, E. and Choi, S. H. and Iwamoto, Y. and Kiss, M. G. and Christie, K. A. and {\bf Vinegoni, C.} and Poller, W. C. and Mindur, J. E. and Chan, C. T. and He, S. and Janssen, H. and Wong, L. P. and Downey, J. and Singh, S. and Anzai, A. and Kahles, F. and Jorfi, M. and Feruglio, P. F. and Sadreyev, R. I. and Weissleder, R. and Kleinstiver, B. P. and Nahrendorf, M. and Tanzi, R. E. and Swirski$^\#$, F. K. \\ ``Nature'' Vol. 595 (2021) pp. 701-+. \\ DOI: 10.1038/s41586-021-03734-6 PMID: 34262178 PMCID: PMC8934148\item \htmladdnormallink{\it  CytoPAN-Portable cellular analyses for rapid point-of-care cancer diagnosis}{https://boh/2020-STM.pdf} \\ Min, J. and Chin, L. K. and Oh, J. and Landeros, C. and {\bf Vinegoni, C.} and Lee, J. and Lee, S. J. and Park, J. Y. and Liu, A. Q. and Castro, C. M. and Lee, H. and Im, H. and Weissleder$^\#$, R. \\ ``Science Translational Medicine'' Vol. 12 (2020) pp. 14. \\ DOI: 10.1126/scitranslmed.aaz9746 PMID: 32759277 PMCID: PMC8217912\item \htmladdnormallink{\it  Fluorescence microscopy tensor imaging representations for large-scale dataset analysis}{https://boh/2020-SCIREP.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Feruglio$^\dag$, P. F. and Courties, G. and Schmidt, S. and Hulsmans, M. and Lee, S. and Wang, R. and Sosnovik, D. and Nahrendorf, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 10 (2020) pp. 15. \\ DOI: 10.1038/s41598-020-62233-2 PMID: 32221334 PMCID: PMC7101442\item \htmladdnormallink{\it  Extended dynamic range imaging for noise mitigation in fluorescence anisotropy imaging}{https://boh/2020-JBO.pdf} \\ Feruglio$^\dag$, P. F. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 25 (2020) pp. 13. \\ DOI: 10.1117/1.Jbo.25.8.086003 PMID: 32820624 PMCID: PMC7439791\item \htmladdnormallink{\it  Diminished Reactive Hematopoiesis and Cardiac Inflammation in a Mouse Model of Recurrent Myocardial Infarction}{https://boh/2020-JAMCC.pdf} \\ Cremer, S. and Schloss, M. J. and {\bf Vinegoni, C.} and Foy, B. H. and Zhang, S. and Rohde, D. and Hulsmans, M. and Feruglio, P. F. and Schmidt, S. and Wojtkiewicz, G. and Higgins, J. M. and Weissleder, R. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 75 (2020) pp. 901-915. \\ DOI: 10.1016/j.jacc.2019.12.056 PMID: 32130926 PMCID: PMC7254576\item \htmladdnormallink{\it  Characterization of single microvesicles in plasma from glioblastoma patients}{https://boh/2019-NO.pdf} \\ Fraser, K. and Jo, A. and Giedt, J. and {\bf Vinegoni, C.} and Yang, K. S. and Peruzzi, P. and Chiocca, E. A. and Breakefield, X. O. and Lee, H. and Weissleder$^\#$, R. \\ ``Neuro-Oncology'' Vol. 21 (2019) pp. 606-615. \\ DOI: 10.1093/neuonc/noy187 PMID: 30561734 PMCID: 6502493\item \htmladdnormallink{\it  High Dynamic Range Fluorescence Imaging}{https://boh/2019-JSTQE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 25 (2019) pp. 7. \\ DOI: 10.1109/jstqe.2018.2881608 PMID: 31598059 PMCID: PMC6785194\item \htmladdnormallink{\it  Fluorescence anisotropy imaging in drug discovery}{https://boh/2019-ADDR.pdf} \\ {\bf Vinegoni$^\#$, C.} and Feruglio, P. F. and Gryczynski, I. and Mazitschek, R. and Weissleder, R. \\ ``Advanced Drug Delivery Reviews'' Vol. 151 (2019) pp. 262-288. \\ DOI: 10.1016/j.addr.2018.01.019 PMID: 29410158 PMCID: 6072632\item \htmladdnormallink{\it  The anti-tumor diterpene oridonin is a direct inhibitor of Nucleolin in cancer cells}{https://boh/2018-SCIREP.pdf} \\ Vasaturo, M. and Cotugno, R. and Fiengo, L. and {\bf Vinegoni, C.} and Dal Piaz, F. and De Tommasi$^\#$, N. \\ ``Scientific Reports'' Vol. 8 (2018) pp. 13. \\ DOI: 10.1038/s41598-018-35088-x PMID: 30425290 PMCID: 6233161\item \htmladdnormallink{\it  Direct vascular channels connect skull bone marrow and the brain surface enabling myeloid cell migration}{https://boh/2018-NATNEURO.pdf} \\ Herisson, F. and Frodermann, V. and Courties, G. and Rohde, D. and Sun, Y. and Vandoorne, K. and Wojtkiewicz, G. R. and Masson, G. S. and {\bf Vinegoni, C.} and Kim, J. and Kim, D. E. and Weissleder, R. and Swirski, F. K. and Moskowitz, M. A. and Nahrendorf$^\#$, M. \\ ``Nature Neuroscience'' Vol. 21 (2018) pp. 1209-+. \\ DOI: 10.1038/s41593-018-0213-2 PMID: 30150661 PMCID: PMC6148759 \item \htmladdnormallink{\it  Cardiac macrophages promote diastolic dysfunction}{https://boh/2018-JEM.pdf} \\ Hulsmans, M. and Sager, H. B. and Roh, J. D. and Valero-Munoz, M. and Houstis, N. E. and Iwamoto, Y. and Sun, Y. and Wilson, R. M. and Wojtkiewicz, G. and Tricot, B. and Osborne, M. T. and Hung, J. and {\bf Vinegoni, C.} and Naxerova, K. and Sosnovik, D. E. and Zile, M. R. and Bradshaw, A. D. and Liao, R. and Tawakol, A. and Weissleder, R. and Rosenzweig, A. and Swirski, F. K. and Sam, F. and Nahrendorf$^\#$, M. \\ ``Journal of Experimental Medicine'' Vol. 215 (2018) pp. 423-440. \\ DOI: 10.1084/jem.20171274 PMID: 29339450 PMCID: PMC3366498\item \htmladdnormallink{\it  Imaging the Vascular Bone Marrow Niche During Inflammatory Stress}{https://boh/2018-CIRCRES.pdf} \\ Vandoorne, K. and Rohde, D. and Kim, H. Y. and Courties, G. and Wojtkiewicz, G. and Honold, L. and Hoyer, F. F. and Frodermann, V. and Nayar, R. and Herisson, F. and Jung, Y. and Desogere, P. A. and {\bf Vinegoni, C.} and Caravan, P. and Weissleder, R. and Sosnovik, D. E. and Lin, C. P. and Swirski, F. K. and Nahrendorf$^\#$, M. \\ ``Circulation Research'' Vol. 123 (2018) pp. 415-427. \\ DOI: 10.1161/circresaha.118.313302 PMID: 29980569 PMCID: 6202141\item \htmladdnormallink{\it  Design and Development of Fluorescent Vemurafenib Analogs for In Vivo Imaging}{https://boh/2017-THERA.pdf} \\ Mikula, H. and Stapleton, S. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Theranostics'' Vol. 7 (2017) pp. 1257-1265. \\ DOI: 10.7150/thno.18238 PMID: 28435463 PMCID: PMC5399591\item \htmladdnormallink{\it  Measurement of drug-target engagement in live cells by two-photon fluorescence anisotropy imaging}{https://boh/2017-NP.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Brand, C. and Lee, S. and Nibbs, A. E. and Stapleton, S. and Shah, S. and Gryczynski, I. and Reiner, T. and Mazitschek, R. and Weissleder, R. \\ ``Nature Protocols'' Vol. 12 (2017) pp. 1472-1497. \\ DOI: 10.1038/nprot.2017.043 PMID: 28686582 PMCID: PMC5928516\item \htmladdnormallink{\it  Quantitating drug-target engagement in single cells in vitro and in vivo}{https://boh/2017-NCBIOL.pdf} \\ Dubach, J. M. and Kim, E. and Yang, K. and Cuccarese, M. and Giedt, R. J. and Meirnetis, L. G. and {\bf Vinegoni$^\#$, C.} and Weissleder$^\#$, R. \\ ``Nature Chemical Biology'' Vol. 13 (2017) pp. 168-173. \\ DOI: 10.1038/nchembio.2248 PMID: 27918558 PMCID: PMC5630128\item \htmladdnormallink{\it  Motion characterization scheme to minimize motion artifacts in intravital microscopy}{https://boh/2017-JBO.pdf} \\ Lee, S. and Courties, G. and Nahrendorf, M. and Weissleder, R. and {\bf Vinegoni$^\#$, C.} \\ ``Journal of Biomedical Optics'' Vol. 22 (2017) pp. 7. \\ DOI: 10.1117/1.Jbo.22.3.036005 PMID: 28253383 PMCID: PMC5333764\item \htmladdnormallink{\it  Macrophages Facilitate Electrical Conduction in the Heart}{https://boh/2017-CELL.pdf} \\ Hulsmans, M. and Clauss, S. and Xiao, L. and Aguirre, A. D. and King, K. R. and Hanley, A. and Hucker, W. J. and Wulfers, E. M. and Seemann, G. and Courties, G. and Iwamoto, Y. and Sun, Y. and Savol, A. J. and Sager, H. B. and Lavine, K. J. and Fishbein, G. A. and Capen, D. E. and Da Silva, N. and Miquerol, L. and Wakimoto, H. and Seidman, C. E. and Seidman, J. G. and Sadreyev, R. I. and Naxerova, K. and Mitchell, R. N. and Brown, D. and Libby, P. and Weissleder, R. and Swirski, F. K. and Kohl, P. and {\bf Vinegoni, C.} and Milan, D. J. and Ellinor, P. T. and Nahrendorf$^\#$, M. \\ ``Cell'' Vol. 169 (2017) pp. 510-+. \\ DOI: 10.1016/j.cell.2017.03.050 PMID: 28431249 PMCID: PMC5474950\item \htmladdnormallink{\it  Transparent Electrophysiology Microelectrodes and Interconnects from Meta Nanomesh}{https://boh/2017-ACSN.pdf} \\ Seo, K. J. and Qiang, Y. and Bilgin, I. and Kar, S. and {\bf Vinegoni, C.} and Weissleder, R. and Fang$^\#$, H. \\ ``Acs Nano'' Vol. 11 (2017) pp. 4365-4372. \\ DOI: 10.1021/acsnano.7b01995 PMID: 28391679 PMCID: N/A\item \htmladdnormallink{\it  Two-photon imaging of pancreatic beta cells in real time in vivo}{https://boh/2016-TECHNOL.pdf} \\ Clardy, S. M. and Kohler, R. and {\bf Vinegoni, C.} and Iwamoto, Y. and Keliher, E. and Weissleder$^\#$, R. \\ ``Technology'' Vol. 4 (2016) pp. 130-34. \\ DOI: 10.1142/S2339547816200028 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  RNAi targeting multiple cell adhesion molecules reduces immune cell recruitment and vascular inflammation after myocardial infarction}{https://boh/2016-STM.pdf} \\ Sager, H. B. and Dutta, P. and Dahlman, J. E. and Hulsmans, M. and Courties, G. and Sun, Y. and Heidt, T. and {\bf Vinegoni, C.} and Borodovsky, A. and Fitzgerald, K. and Wojtkiewicz, G. R. and Iwamoto, Y. and Tricot, B. and Khan, O. F. and Kauffman, K. J. and Xing, Y. P. and Shaw, T. E. and Libby, P. and Langer, R. and Weissleder, R. and Swirski, F. K. and Anderson, D. G. and Nahrendorf$^\#$, M. \\ ``Science Translational Medicine'' Vol. 8 (2016) pp. 11. \\ DOI: 10.1126/scitranslmed.aaf1435 PMID: 27280687 PMCID: PMC5125383\item \htmladdnormallink{\it  Computational imaging reveals mitochondrial morphology as a biomarker of cancer phenotype and drug response}{https://boh/2016-SCIREP.pdf} \\ Giedt, R. J. and Fumene Feruglio, P. and Pathania, D. and Yang, K. S. and Kilcoyne, A. and {\bf Vinegoni, C.} and Mitchison, T. J. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 6 (2016) pp. 10. \\ DOI: 10.1038/srep32985 PMID: 27609668 PMCID: PMC5017129\item \htmladdnormallink{\it  Real-time high dynamic range laser scanning microscopy}{https://boh/2016-NCOMM-2.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Swisher$^\dag$, C. L. and Fumene Feruglio$^\dag$, P. and Giedt, R. J. and Rousso, D. L. and Stapleton, S. and Weissleder, R. \\ ``Nature Communications'' Vol. 7 (2016) pp. 13. \\ DOI: 10.1038/ncomms11077 PMID: 27032979 PMCID: PMC4821995\item \htmladdnormallink{\it  Tyrosine kinase-mediated axial motility of basal cells revealed by intravital imaging}{https://boh/2016-NCOMM-1.pdf} \\ Roy, J. and Kim, B. and Hill, E. and Visconti, P. and Krapf, D. and {\bf Vinegoni, C.} and Weissleder, R. and Brown, D. and Breton$^\#$, S. \\ ``Nature Communications'' Vol. 7 (2016) pp. 11. \\ DOI: 10.1038/ncomms10666 PMID: 26868824 PMCID: PMC4754344\item \htmladdnormallink{\it  Two-Photon Fluorescence Anisotropy Microscopy for Imaging and Direct Measurement of Intracellular Drug Target Engagement}{https://boh/2016-IEEE.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Feruglio, P. F. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 22 (2016) pp. 7. \\ DOI: 10.1109/jstqe.2015.2501384 PMID: 27440991 PMCID: PMC4946648\item \htmladdnormallink{\it  Rapid, high efficiency isolation of pancreatic beta-cells}{https://boh/2015-SREP.pdf} \\ Clardy, S. M. and Mohan, J. F. and {\bf Vinegoni, C.} and Keliher, E. J. and Iwamoto, Y. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Scientific Reports'' Vol. 5 (2015) pp. 9. \\ DOI: 10.1038/srep13681 PMID: 26330153 PMCID: PMC4557033\item \htmladdnormallink{\it  Imaging the beating heart in the mouse using intravital microscopy techniques}{https://boh/2015-NPROT.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Aguirre$^\dag$, A. D. and Lee, S. and Weissleder, R. \\ ``Nature Protocols'' Vol. 10 (2015) pp. 1802-1819. \\ DOI: 10.1038/nprot.2015.119 PMID: 26492138 PMCID: PMC5380003\item \htmladdnormallink{\it  New techniques for motion-artifact-free in vivo cardiac microscopy}{https://boh/2015-FPHYS.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Aguirre, A. D. and Weissleder, R. \\ ``Frontiers in Physiology'' Vol. 6 (2015) pp. 12. \\ DOI: 10.3389/fphys.2015.00147 PMID: 26029116 PMCID: PMC4428079\item \htmladdnormallink{\it  Advances in measuring single-cell pharmacology in vivo}{https://boh/2015-DDT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Dubach, J. M. and Thurber, G. M. and Miller, M. A. and Mazitschek, R. and Weissleder, R. \\ ``Drug Discovery Today'' Vol. 20 (2015) pp. 1087-1092. \\ DOI: 10.1016/j.drudis.2015.05.011 PMID: 26024776 PMCID: PMC4567932\item \htmladdnormallink{\it  Myocardial Infarction Activates CCR2(+) Hematopoietic Stem and Progenitor Cells}{https://boh/2015-CSC.pdf} \\ Dutta, P. and Sager, H. B. and Stengel, K. R. and Naxerova, K. and Courties, G. and Saez, B. and Silberstein, L. and Heidt, T. and Sebas, M. and Sun, Y. and Wojtkiewicz, G. and Fumene Feruglio, P. and King, K. and Baker, J. N. and van der Laan, A. M. and Borodovsky, A. and Fitzgerald, K. and Hulsmans, M. and Hoyer, F. and Iwamoto, Y. and {\bf Vinegoni, C.} and Brown, D. and Di Carli, M. and Libby, P. and Hiebert, S. W. and Scadden, D. T. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Cell Stem Cell'' Vol. 16 (2015) pp. 477-487. \\ DOI: 10.1016/j.stem.2015.04.008 PMID: 25957903 PMCID: PMC4426344\item \htmladdnormallink{\it  Automated motion artifact removal for intravital microscopy, without a priori information}{https://boh/2014-SR.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Sebas, M. and Weissleder, R. \\ ``Scientific Reports'' Vol. 4 (2014) pp. 9. \\ DOI: 10.1038/srep04507 PMID: 24676021 PMCID: PMC3968488\item \htmladdnormallink{\it  Intravital imaging of cardiac function at the single-cell level}{https://boh/2014-PNAS.pdf} \\ Aguirre, A. D. and {\bf Vinegoni$^\#$, C.} and Sebas, M. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 111 (2014) pp. 11257-11262. \\ DOI: 10.1073/pnas.1401316111 PMID: 25053815 PMCID: PMC4128110\item \htmladdnormallink{\it  Steady state anisotropy two-photon microscopy resolves multiple, spectrally similar fluorophores, enabling in vivo multilabel imaging}{https://boh/2014-OL.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Weissleder, R. \\ ``Optics Letters'' Vol. 39 (2014) pp. 4482-4485. \\ DOI: 10.1364/ol.39.004482 PMID: 25078208 PMCID: PMC4341989\item \htmladdnormallink{\it  Chronic variable stress activates hematopoietic stem cells}{https://boh/2014-NM.pdf} \\ Heidt, T. and Sager, H. B. and Courties, G. and Dutta, P. and Iwamoto, Y. and Zaltsman, A. and von zur Muhlen, C. and Bode, C. and Fricchione, G. L. and Denninger, J. and Lin, C. P. and {\bf Vinegoni, C.} and Libby, P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature Medicine'' Vol. 20 (2014) pp. 754-758. \\ DOI: 10.1038/nm.3589 PMID: 24952646 PMCID: PMC4087061\item \htmladdnormallink{\it  In vivo imaging of specific drug-target binding at subcellular resolution}{https://boh/2014-NC.pdf} \\ Dubach$^\dag$, J. M. and {\bf Vinegoni$^{\dag \#}$, C.} and Mazitschek, R. and Fumene Feruglio, P. and Cameron, L. A. and Weissleder, R. \\ ``Nature Communications'' Vol. 5 (2014) pp. 9. \\ DOI: 10.1038/ncomms4946 PMID: 24867710 PMCID: PMC4362617\item \htmladdnormallink{\it  Advanced Motion Compensation Methods for Intravital Optical Microscopy}{https://boh/2014-IEEE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Weissleder, R. \\ ``Ieee Journal of Selected Topics in Quantum Electronics'' Vol. 20 (2014) pp. 9. \\ DOI: 10.1109/jstqe.2013.2279314 PMID: 24273405 PMCID: PMC3832946\item \htmladdnormallink{\it  Perinatal health and translational medicine}{https://boh/2013-JHGD.pdf} \\ Figueiredo, J. L. and {\bf Vinegoni, C.} and De Abreu, L. C. \\ ``Journal of Human Growth and Development'' Vol. 23 (2013) pp. 125-127. \\ DOI: 10.7322/jhgd.61318 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Sequential average segmented microscopy for high signal-to-noise ratio motion-artifact-free in vivo heart imaging}{https://boh/2013-BOE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Fumene Feruglio, P. and Marzola, P. and Nahrendorf, M. and Weissleder, R. \\ ``Biomedical Optics Express'' Vol. 4 (2013) pp. 2095-2106. \\ DOI: 10.1364/boe.4.002095 PMID: 24156067 PMCID: PMC3799669\item \htmladdnormallink{\it  Noise suppressed, multifocus image fusion for enhanced intraoperative navigation}{https://boh/2013-BIOPHTNCS.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Fexon, L. and Thurber, G. and Sbarbati, A. and Weissleder, R. \\ ``Journal of Biophotonics'' Vol. 6 (2013) pp. 363-370. \\ DOI: 10.1002/jbio.201200086 PMID: 22887724 PMCID: PMC3779878\item \htmladdnormallink{\it  Implantable microenvironments to attract hematopoietic stem/cancer cells}{https://boh/2012-PNAS.pdf} \\ Lee, J. and Li, M. and Milwid, J. and Dunham, J. and {\bf Vinegoni, C.} and Gorbatov, R. and Iwamoto, Y. and Wang, F. J. and Shen, K. Y. and Hatfield, K. and Enger, M. and Shafiee, S. and McCormack, E. and Ebert, B. L. and Weissleder, R. and Yarmush, M. L. and Parekkadan$^\#$, B. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 109 (2012) pp. 19638-19643. \\ DOI: 10.1073/pnas.1208384109 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Mapping Molecular Agents Distributions in Whole Mice Hearts Using Born-Normalized Optical Projection Tomography}{https://boh/2012-PLOSONE.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio$^\dag$, P. and Razansky, D. and Gorbatov, R. and Ntziachristos, V. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Plos One'' Vol. 7 (2012) pp. 9. \\ DOI: 10.1371/journal.pone.0034427 PMID: 22509302 PMCID: PMC3324534\item \htmladdnormallink{\it  Imaging Therapeutic PARP Inhibition In Vivo through Bioorthogonally Developed Companion Imaging Agents}{https://boh/2012-NEOPLASIA.pdf} \\ Reiner, T. and Lacy, J. and Keliher, E. J. and Yang, K. S. and Ullal, A. and Kohler, R. H. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Neoplasia'' Vol. 14 (2012) pp. 169-+. \\ DOI: 10.1593/neo.12414 PMID: 22496617 PMCID: PMC3323895\item \htmladdnormallink{\it  Real-time in vivo imaging of the beating mouse heart at microscopic resolution}{https://boh/2012-NC.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Fexon, L. and Gorbatov, R. and Pivoravov, M. and Sbarbati, A. and Nahrendorf, M. and Weissleder, R. \\ ``Nature Communications'' Vol. 3 (2012) pp. 8. \\ DOI: 10.1038/ncomms2060 PMID: 22968700 PMCID: PMC3622400\item \htmladdnormallink{\it  Myocardial infarction accelerates atherosclerosis}{https://boh/2012-NATURE.pdf} \\ Dutta, P. and Courties, G. and Wei, Y. and Leuschner, F. and Gorbatov, R. and Robbins, C. S. and Iwamoto, Y. and Thompson, B. and Carlson, A. L. and Heidt, T. and Majmudar, M. D. and Lasitschka, F. and Etzrodt, M. and Waterman, P. and Waring, M. T. and Chicoine, A. T. and van der Laan, A. M. and Niessen, H. W. M. and Piek, J. J. and Rubin, B. B. and Butany, J. and Stone, J. R. and Katus, H. A. and Murphy, S. A. and Morrow, D. A. and Sabatine, M. S. and {\bf Vinegoni, C.} and Moskowitz, M. A. and Pittet, M. J. and Libby, P. and Lin, C. P. and Swirski, F. K. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Nature'' Vol. 487 (2012) pp. 325-329. \\ DOI: 10.1038/nature11260 PMID: 22763456 PMCID: PMC3401326\item \htmladdnormallink{\it  Improved intravital microscopy via synchronization of respiration and holder stabilization}{https://boh/2012-JBO.pdf} \\ Lee$^\dag$, S. and {\bf Vinegoni$^{\dag \#}$, C.} and Fumene Feruglio, P. and Weissleder, R. \\ ``Journal of Biomedical Optics'' Vol. 17 (2012) pp. 8. \\ DOI: 10.1117/1.Jbo.17.9.096018 PMID: 23085919 PMCID: PMC3449295\item \htmladdnormallink{\it  PET/MRI of Inflammation in Myocardial Infarction}{https://boh/2012-JACC.pdf} \\ Lee, W. W. and Marinelli, B. and van der Laan, A. M. and Sena, B. F. and Gorbatov, R. and Leuschner, F. and Dutta, P. and Iwamoto, Y. and Ueno, T. and Begieneman, M. P. V. and Niessen, H. W. M. and Piek, J. J. and {\bf Vinegoni, C.} and Pittet, M. J. and Swirski, F. K. and Tawakol, A. and Di Carli, M. and Weissleder, R. and Nahrendorf$^\#$, M. \\ ``Journal of the American College of Cardiology'' Vol. 59 (2012) pp. 153-163. \\ DOI: 10.1016/j.jacc.2011.08.066 PMID: 22222080 PMCID: PMC3257823\item \htmladdnormallink{\it  Motion compensation using a suctioning stabilizer for intravital microscopy}{https://boh/2012-INTRVTL.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Lee$^\dag$, S. and Gorbatov, R. and Weissleder, R. \\ ``Intravital'' Vol. 1 (2012) pp. 115. \\ DOI: 10.4161/intv.23017 PMID: 24086796 PMCID: PMC3786172\item \htmladdnormallink{\it  Deep Tissue Optical and Optoacoustic Molecular Imaging Technologies for Pre-Clinical Research and Drug Discovery}{https://boh/2012-CPB.pdf} \\ Razansky$^\#$, D. and Deliolanis, N. C. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Current Pharmaceutical Biotechnology'' Vol. 13 (2012) pp. 504-522. \\ DOI: 10.2174/138920112799436258 PMID: 22216767 PMCID: N/A\item \htmladdnormallink{\it  In Vivo Imaging of Drug-Induced Mitochondrial Outer Membrane Permeabilization at Single-Cell Resolution}{https://boh/2012-CNCRRES.pdf} \\ Earley, S. and {\bf Vinegoni, C.} and Dunham, J. and Gorbatov, R. and Fumene Feruglio, P. and Weissleder$^\#$, R. \\ ``Cancer Research'' Vol. 72 (2012) pp. 2949-2956. \\ DOI: 10.1158/0008-5472.Can-11-4096 PMID: 22505651 PMCID: PMC3603290\item \htmladdnormallink{\it  Optochemogenetics (OCG) Allows More Precise Control of Genetic Engineering in Mice with CreER regulators}{https://boh/2012-BIOCHEM.pdf} \\ Lu, X. and Agasti, S. S. and {\bf Vinegoni, C.} and Waterman, P. and DePinho, R. A. and Weissleder$^\#$, R. \\ ``Bioconjugate Chemistry'' Vol. 23 (2012) pp. 1945-1951. \\ DOI: 10.1021/bc300319c PMID: 22917215 PMCID: PMC3775343\item \htmladdnormallink{\it  Bioorthogonal Imaging of Aurora Kinase A in Live Cells}{https://boh/2012-AC.pdf} \\ Yang, K. S. and Budin, G. and Reiner, T. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Angewandte Chemie-International Edition'' Vol. 51 (2012) pp. 6598-6603. \\ DOI: 10.1002/anie.201200994 PMID: 22644700 PMCID: PMC3523717\item \htmladdnormallink{\it  Indocyanine Green Enables Near-Infrared Fluorescence Imaging of Lipid-Rich, Inflamed Atherosclerotic Plaques}{https://boh/2011-STM.pdf} \\ {\bf Vinegoni, C.} and Botnaru, I. and Aikawa, E. and Calfon, M. A. and Iwamoto, Y. and Folco, E. J. and Ntziachristos, V. and Weissleder, R. and Libby, P. and Jaffer$^\#$, F. A. \\ ``Science Translational Medicine'' Vol. 3 (2011) pp. 9. \\ DOI: 10.1126/scitranslmed.3001577 PMID: 21613624 PMCID: PMC3112179\item \htmladdnormallink{\it  Accurate measurement of pancreatic islet beta-cell mass using a second-generation fluorescent exendin-4 analog}{https://boh/2011-PNAS.pdf} \\ Reiner, T. and Thurber, G. and Gaglia, J. and {\bf Vinegoni, C.} and Liew, C. W. and Upadhyay, R. and Kohler, R. H. and Li, L. and Kulkarni, R. N. and Benoist, C. and Mathis, D. and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 108 (2011) pp. 12815-12820. \\ DOI: 10.1073/pnas.1109859108 PMID: 21768367 PMCID: PMC3150928\item \htmladdnormallink{\it  A multimodal approach for tracing lateralisation along the olfactory pathway in the honeybee through electrophysiological recordings, morpho-functional imaging, and behavioural studies}{https://boh/2011-EB.pdf} \\ Haase, A. and Rigosi, E. and Frasnelli, E. and Trona, F. and Tessarolo, F. and {\bf Vinegoni, C.} and Anfora, G. and Vallortigara, G. and Antolini$^\#$, R. \\ ``European Biophysics Journal with Biophysics Letters'' Vol. 40 (2011) pp. 1247-1258. \\ DOI: 10.1007/s00249-011-0748-6 PMID: 21956452 PMCID: PMC3366498\item \htmladdnormallink{\it  Searching for anatomical correlates of olfactory lateralization in the honeybee antennal lobes: A morphological and behavioural study}{https://boh/2011-BBR.pdf} \\ Rigosi$^\#$, E. and Frasnelli, E. and {\bf Vinegoni, C.} and Antolini, R. and Anfora, G. and Vallortigara, G. and Haase, A. \\ ``Behavioural Brain Research'' Vol. 221 (2011) pp. 290-294. \\ DOI: 10.1016/j.bbr.2011.03.015 PMID: 21402106 PMCID: PMC3089663\item \htmladdnormallink{\it  Intraoperative Near-infrared Fluorescent Cholangiography (NIRFC) in Mouse Models of Bile Duct Injury: Reply}{https://boh/2010-WJS.pdf} \\ Figueiredo, J. L. and Nahrendorf, M. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``World Journal of Surgery'' Vol. 35 (2011) pp. 694-695. \\ DOI: 10.1007/s00268-010-0728-5 PMID: 20645091 PMCID: N/A\item \htmladdnormallink{\it  Hybrid PET-optical imaging using targeted probes}{https://boh/2010-PNAS.pdf} \\ Nahrendorf$^{\dag \#}$, M. and Keliher$^\dag$, E. and Marinelli, B. and Waterman, P. and Fumene Feruglio, P. and Fexon, L. and Pivovarov, M. and Swirski, F. K. and Pittet, M. J. and {\bf Vinegoni, C.} and Weissleder$^\#$, R. \\ ``Proceedings of the National Academy of Sciences of the United States of America'' Vol. 107 (2010) pp. 7910-7915. \\ DOI: 10.1073/pnas.0915163107 PMID: 20385821 PMCID: PMC2867879\item \htmladdnormallink{\it  Block matching 3D random noise filtering for absorption optical projection tomography}{https://boh/2010-PMB.pdf} \\ Fumene Feruglio$^\dag$, P. and {\bf Vinegoni$^{\dag \#}$, C.} and Gros, J. and Sbarbati, A. and Weissleder, R. \\ ``Physics in Medicine and Biology'' Vol. 55 (2010) pp. 5401-5415. \\ DOI: 10.1088/0031-9155/55/18/009 PMID: 20736500 PMCID: PMC2934766\item \htmladdnormallink{\it  Imaging of molecular probe activity with Born-normalized fluorescence optical projection tomography}{https://boh/2010-OL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fumene Feruglio, P. and Cortez-Retamozo, V. and Razansky, D. and Medoff, B. D. and Ntziachristos, V. and Sbarbati, A. and Pittet, M. and Weissleder, R. \\ ``Optics Letters'' Vol. 35 (2010) pp. 1088-1090. \\ DOI: 10.1364/ol.35.001088 PMID: 20364226 PMCID: PMC2900933\item \htmladdnormallink{\it  Intravascular near-infrared fluorescence molecular imaging of atherosclerosis: toward coronary arterial visualization of biologically high-risk plaques}{https://boh/2010-JBO.pdf} \\ Calfon, M. A. and {\bf Vinegoni, C.} and Ntziachristos, V. and Jaffer$^\#$, F. A. \\ ``Journal of Biomedical Optics'' Vol. 15 (2010) pp. 6. \\ DOI: 10.1117/1.3280282 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  WNT5A/JNK and FGF/MAPK Pathways Regulate the Cellular Events Shaping the Vertebrate Limb Bud}{https://boh/2010-CB.pdf} \\ Gros, J. and Hu, J. K. H. and {\bf Vinegoni, C.} and Fumene Feruglio, P. and Weissleder, R. and Tabin$^\#$, C. J. \\ ``Current Biology'' Vol. 20 (2010) pp. 1993-2002. \\ DOI: 10.1016/j.cub.2010.09.063 PMID: 20210433 PMCID: PMC3188610\item \htmladdnormallink{\it  In-vivo two-photon imaging of the honey bee antennal lobe}{https://boh/2010-BOEX.pdf} \\ Haase, A. and Rigosi, E. and Trona, F. and Anfora, G. and Vallortigara, G. and Antolini, R. and {\bf Vinegoni$^\#$, C.} \\ ``Biomedical Optics Express'' Vol. 2 (2011) pp. 131-138. \\ DOI: 10.1364/boe.2.000131 PMID: 21326643 PMCID: PMC3028488\item \htmladdnormallink{\it  Imaging of mesoscopic-scale organisms using selective-plane optoacoustic tomography}{https://boh/2009-PMB.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Physics in Medicine and Biology'' Vol. 54 (2009) pp. 2769-2777. \\ DOI: 10.1088/0031-9155/54/9/012 PMID: 19369709 PMCID: N/A\item \htmladdnormallink{\it  Normalized Born ratio for fluorescence optical projection tomography}{https://boh/2009-OL-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 319-321. \\ DOI: 10.1364/ol.34.000319 PMID: 19183644 PMCID: PMC2771918\item \htmladdnormallink{\it  Transillumination fluorescence imaging in mice using biocompatible upconverting nanoparticles}{https://boh/2009-OL-1.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Razansky$^\dag$, D. and Hilderbrand, S. A. and Shao, F. W. and Ntziachristos, V. and Weissleder, R. \\ ``Optics Letters'' Vol. 34 (2009) pp. 2566-2568. \\ DOI: 10.1364/ol.34.002566 PMID: 19724491 PMCID: PMC2749971\item \htmladdnormallink{\it  Diffractionless beam in free space with adiabatic changing refractive index in a single mode tapered slab waveguide}{https://boh/2009-OE-2.pdf} \\ Tsai$^\#$, C. C. and {\bf Vinegoni, C.} and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 21723-21731. \\ DOI: 10.1364/oe.17.021723 PMID: 19997414 PMCID: PMC2805120\item \htmladdnormallink{\it  High throughput transmission optical projection tomography using low cost graphics processing unit}{https://boh/2009-OE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Fexon, L. and Fumene Feruglio, P. and Pivovarov, M. and Figueiredo, J. L. and Nahrendorf, M. and Pozzo, A. and Sbarbati, A. and Weissleder, R. \\ ``Optics Express'' Vol. 17 (2009) pp. 22320-22332. \\ DOI: 10.1364/oe.17.022320 PMID: 20052155 PMCID: PMC2805020\item \htmladdnormallink{\it  Multispectral opto-acoustic tomography of deep-seated fluorescent proteins in vivo}{https://boh/2009-NATPHOT.pdf} \\ Razansky$^\#$, D. and Distel, M. and {\bf Vinegoni, C.} and Ma, R. and Perrimon, N. and Koster, R. W. and Ntziachristos$^\#$, V. \\ ``Nature Photonics'' Vol. 3 (2009) pp. 412-417. \\ DOI: 10.1038/nphoton.2009.98 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Mesoscopic Fluorescence Tomography for In-vivo Imaging of Developing Drosophila}{https://boh/2009-JOVE-2.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Pitsouli, C. and Perrimon, N. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1510. \\ DOI: 10.3791/1510 PMID: 19696720 PMCID: PMC2736679\item \htmladdnormallink{\it  Born normalization for fluorescence optical projection tomography for whole heart imaging}{https://boh/2009-JOVE-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Razansky, D. and Figueiredo, J. L. and Fexon, L. and Pivoravov, M. and Nahrendorf, M. and Ntziachristos, V. and Weissleder, R. \\ ``Journal of Visualized Experiments'' Vol. 2 (2009) pp. 1389. \\ DOI: 10.3791/1389 PMID: 19578329 PMCID: PMC2794886\item \htmladdnormallink{\it  Unprecedent in vivo views at the mesoscopic scale}{https://boh/2009-BOW.pdf} \\ Razansky, R. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``BioOptics World'' Vol. 2 (2009) pp. 22. \\ DOI: N/A PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Polarization-sensitive optoacoustic tomography of optically diffuse tissues}{https://boh/2008-OL.pdf} \\ Razansky$^\#$, D. and {\bf Vinegoni, C.} and Ntziachristos, V. \\ ``Optics Letters'' Vol. 33 (2008) pp. 2308-2310. \\ DOI: 10.1364/ol.33.002308 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  In vivo imaging of Drosophila melanogaster pupae with mesoscopic fluorescence tomography}{https://boh/2008-NM.pdf} \\ {\bf Vinegoni$^{\dag \#}$, C.} and Pitsouli$^\dag$, C. and Razansky$^\dag$, D. and Perrimon, N. and Ntziachristos, V. \\ ``Nature Methods'' Vol. 5 (2008) pp. 45-47. \\ DOI: 10.1038/nmeth1149 PMID: 18066071 PMCID: N/A\item \htmladdnormallink{\it  Real-time assessment of inflammation and treatment response in a mouse model of allergic airway inflammation}{https://boh/2008-JCI.pdf} \\ Cortez-Retamozo, V. and Swirski, F. K. and Waterman, P. and Yuan, H. and Figueiredo, J. L. and Newton, A. P. and Upadhyay, R. and {\bf Vinegoni, C.} and Kohler, R. and Blois, J. and Smith, A. and Nahrendorf, M. and Josephson, L. and Weissleder, R. and Pittet$^\#$, M. J. \\ ``Journal of Clinical Investigation'' Vol. 118 (2008) pp. 4058-4066. \\ DOI: 10.1172/jci36335 PMID: 18923605 PMCID: N/A\item \htmladdnormallink{\it  Real-Time Catheter Molecular Sensing of Inflammation in Proteolytically Active Atherosclerosis}{https://boh/2008-CRCLT.pdf} \\ Jaffer, F. A. and {\bf Vinegoni, C.} and John, M. C. and Aikawa, E. and Gold, H. K. and Finn, A. V. and Ntziachristos, V. and Libby, P. and Weissleder$^\#$, R. \\ ``Circulation'' Vol. 118 (2008) pp. 1802-1809. \\ DOI: 10.1161/circulationaha.108.785881 PMID: 18852366 PMCID: PMC2729441\item \htmladdnormallink{\it  Multispectral photoacoustic imaging of fluorochromes in small animals}{https://boh/2007-OL.pdf} \\ Razansky, D. and {\bf Vinegoni, C.} and Ntziachristos$^\#$, V. \\ ``Optics Letters'' Vol. 32 (2007) pp. 2891-2893. \\ DOI: 10.1364/ol.32.002891 PMID: 17909608 PMCID: N/A\item \htmladdnormallink{\it  Imaging cellular responses to mechanical stimuli within three-dimensional tissue constructs}{https://boh/2007-MRT.pdf} \\ Tan, W. and {\bf Vinegoni, C.} and Norman, J. J. and Desai, T. A. and Boppart$^\#$, S. A. \\ ``Microscopy Research and Technique'' Vol. 70 (2007) pp. 361-371. \\ DOI: 10.1002/jemt.20420 PMID: 17262787 PMCID: N/A\item \htmladdnormallink{\it  High-spectral-resolution coherent anti-Stokes Raman scattering with interferometric ally detected broadband chirped pulses}{https://boh/2006-OL-2.pdf} \\ Jones, G. W. and Marks, D. L. and {\bf Vinegoni, C.} and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1543-1545. \\ DOI: 10.1364/ol.31.001543 PMID: 16642166 PMCID: N/A\item \htmladdnormallink{\it  Spectroscopic spectral-domain optical coherence microscopy}{https://boh/2006-OL-1.pdf} \\ Xu, C. Y. and {\bf Vinegoni, C.} and Ralston, T. S. and Luo, W. and Tan, W. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 31 (2006) pp. 1079-1081. \\ DOI: 10.1364/ol.31.001079 PMID: 16625909 PMCID: N/A\item \htmladdnormallink{\it  Integrated structural and functional optical imaging combining spectral-domain optical coherence and multiphoton microscopy}{https://boh/2006-APL.pdf} \\ {\bf Vinegoni, C.} and Ralston, T. and Tan, W. and Luo, W. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 88 (2006) pp. 3. \\ DOI: 10.1063/1.2171477 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Nonlinear Interferometric Vibrational Imaging. efficient detection of Coherent Anti-Stokes Raman Scattering}{https://boh/2005-OPN.pdf} \\ McAlpine, C. S. and Marks, D. and {\bf Vinegoni, C.} and Bredfeldt, J. and Boppart$^\#$, S.A. \\ ``Optics & Photonics News'' Vol. 16 (2005) pp. 23. \\ DOI: 10.1364/OPN.16.12.000023 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Molecularly sensitive optical coherence tomography}{https://boh/2005-OL.pdf} \\ Bredfeldt, J. S. and {\bf Vinegoni, C.} and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Letters'' Vol. 30 (2005) pp. 495-497. \\ DOI: 10.1364/ol.30.000495 PMID: 15789714 PMCID: N/A\item \htmladdnormallink{\it  Nonlinear optical contrast enhancement for optical coherence tomography}{https://boh/2004-OE.pdf} \\ {\bf Vinegoni, C.} and Bredfeldt, J. S. and Marks, D. L. and Boppart$^\#$, S. A. \\ ``Optics Express'' Vol. 12 (2004) pp. 331-341. \\ DOI: 10.1364/opex.12.000331 PMID: 19471542 PMCID: N/A\item \htmladdnormallink{\it  The statistics of polarization-dependent loss in a recirculating loop}{https://boh/2004-JLT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Karlsson, M. and Petersson, M. and Sunnerud, H. \\ ``Journal of Lightwave Technology'' Vol. 22 (2004) pp. 968-976. \\ DOI: 10.1109/jlt.2004.824861 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Interferometric differentiation between resonant coherent anti-Stokes Raman scattering and nonresonant four-wave-mixing processes}{https://boh/2004-APL.pdf} \\ Marks, D. L. and {\bf Vinegoni, C.} and Bredfeldt, J. S. and Boppart$^\#$, S. A. \\ ``Applied Physics Letters'' Vol. 85 (2004) pp. 5787-5789. \\ DOI: 10.1063/1.1829162 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed measurements of chromatic dispersion and nonlinear coefficient in low-PMD dispersion-shifted fibers}{https://boh/2003-PTL-2.pdf} \\ {\bf Vinegoni, C.} and Chen$^\#$, H. X. and Leblanc, M. and Schinn, G. W. and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 739-741. \\ DOI: 10.1109/lpt.2003.810249 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Statistics of PMD in recirculating loops}{https://boh/2003-PTL-1.pdf} \\ Petersson$^\#$, M. and {\bf Vinegoni, C.} and Sunnerud, H. and Karlsson, M. \\ ``Ieee Photonics Technology Letters'' Vol. 15 (2003) pp. 1543-1545. \\ DOI: 10.1109/lpt.2003.818681 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Emulator of first- and second-order polarization-mode dispersion}{https://boh/2002-PTL.pdf} \\ Wegmuller, M. and Demma, S. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 14 (2002) pp. 630-632. \\ DOI: 10.1109/68.998707 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Analysis of the polarization evolution in a ribbon cable using high-resolution coherent OFDR}{https://boh/2001-PTL-2.pdf} \\ Wegmuller, M. and Legre, M. and Oberson, P. and Guinnard, O. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin$^\#$, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 145-147. \\ DOI: 10.1109/68.910516 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurements of the nonlinear coefficient of standard SMF, DSF, and DCF fibers using a self-aligned interferometer and a Faraday mirror}{https://boh/2001-PTL-1.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Ieee Photonics Technology Letters'' Vol. 13 (2001) pp. 1337-1339. \\ DOI: 10.1109/68.969900 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Morphological and optical characterization of GaN prepared by pulsed laser deposition}{https://boh/2000-SCT.pdf} \\ {\bf Vinegoni$^\#$, C.} and Cazzanelli, M. and Trivelli, A. and Mariotto, G. and Castro, J. and Lunney, J. G. and Levy, J. \\ ``Surface & Coatings Technology'' Vol. 124 (2000) pp. 272-277. \\ DOI: 10.1016/s0257-8972(99)00657-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Optical absorption and photoluminescence properties of alpha-Si1-xNx : H films deposited by plasma-enhanced CVD}{https://boh/2000-PRB.pdf} \\ Giorgis$^\#$, F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 61 (2000) pp. 4693-4698. \\ DOI: 10.1103/PhysRevB.61.4693 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  All optical switching in a highly birefringent and a standard telecom fiber using a Faraday mirror stabilization scheme}{https://boh/2000-OC.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Optics Communications'' Vol. 182 (2000) pp. 335-341. \\ DOI: 10.1016/s0030-4018(00)00845-2 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Measurement of nonlinear polarization rotation in a highly birefringent optical fibre using a Faraday mirror}{https://boh/2000-JOA.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Huttner, B. and Gisin, N. \\ ``Journal of Optics a-Pure and Applied Optics'' Vol. 2 (2000) pp. 314-318. \\ DOI: 10.1088/1464-4258/2/4/313 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Distributed gain measurements in Er-doped fibers with high resolution and accuracy using an optical frequency domain reflectometer}{https://boh/2000-JLT.pdf} \\ Wegmuller$^\#$, M. and Oberson, P. and Guinnard, O. and Huttner, B. and Guinnard, L. and {\bf Vinegoni, C.} and Gisin, N. \\ ``Journal of Lightwave Technology'' Vol. 18 (2000) pp. 2127-2132. \\ DOI: 10.1109/50.908823 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Determination of nonlinear coefficient n(2)/A(eff) using self-aligned interferometer and Faraday mirror}{https://boh/2000-EL.pdf} \\ {\bf Vinegoni$^\#$, C.} and Wegmuller, M. and Gisin, N. \\ ``Electronics Letters'' Vol. 36 (2000) pp. 886-888. \\ DOI: 10.1049/el:20000668 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman study of the phase transitions sequence in pure WO3 at high temperature and in HxWO3 with variable hydrogen content}{https://boh/1999-SSI.pdf} \\ Cazzanelli$^\#$, E. and {\bf Vinegoni, C.} and Mariotto, G. and Kuzmin, A. and Purans, J. \\ ``Solid State Ionics'' Vol. 123 (1999) pp. 67-74. \\ DOI: 10.1016/s0167-2738(99)00101-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescence processes in amorphous hydrogenated silicon-nitride nanometric multilayers}{https://boh/1999-PRB.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Physical Review B'' Vol. 60 (1999) pp. 11572-11576. \\ DOI: 10.1103/PhysRevB.60.11572 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Luminescent properties of GaN thin films prepared by pulsed laser deposition}{https://boh/1999-MSEB.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Cole, D. and Lunney, J. G. and Middleton, P. G. and Trager-Cowan, C. and O'Donnell, K. P. and Pavesi$^\#$, L. \\ ``Materials Science and Engineering B-Solid State Materials for Advanced Technology'' Vol. 59 (1999) pp. 137-140. \\ DOI: 10.1016/s0921-5107(98)00333-x PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Low-temperature polymorphism in tungsten trioxide powders and its dependence on mechanical treatments}{https://boh/1999-JSSC.pdf} \\ Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto$^\#$, G. and Kuzmin, A. and Purans, J. \\ ``Journal of Solid State Chemistry'' Vol. 143 (1999) pp. 24-32. \\ DOI: 10.1006/jssc.1998.8061 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Temperature dependence of the photoluminescence of all-porous-silicon optical microcavities}{https://boh/1999-JAP.pdf} \\ Cazzanelli, M. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Journal of Applied Physics'' Vol. 85 (1999) pp. 1760-1764. \\ DOI: 10.1063/1.369320 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Color Centres and Polymorphism in Pure WO(3) and Mixed (1-x)WO(3-y)center dot xReO(2) Powders}{https://boh/1999-INCS.pdf} \\ Cazzanelli$^\#$, E. and Mariotto, G. and {\bf Vinegoni, C.} and Kuzmin, A. and Purans, J. \\ ``Ionics'' Vol. 5 (1999) pp. 335-344. \\ DOI: 10.1007/bf02375997 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Raman spectroscopy and scanning electron microscopy investigation of annealed amorphous carbon-germanium films deposited by d.c. magnetron sputtering}{https://boh/1999-DRM.pdf} \\ Mariotto, G. and {\bf Vinegoni, C.} and Jacobsohn, L. G. and Freire$^\#$, F. L. \\ ``Diamond and Related Materials'' Vol. 8 (1999) pp. 668-672. \\ DOI: 10.1016/s0925-9635(98)00328-8 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Resonant second harmonic generation in ZnSe bulk microcavity}{https://boh/1999-APL.pdf} \\ Pellegrini, V. and Colombelli, R. and Carusotto, I. and Beltram, F. and Rubini, S. and Lantier, R. and Franciosi, A. and {\bf Vinegoni, C.} and Pavesi$^\#$, L. \\ ``Applied Physics Letters'' Vol. 74 (1999) pp. 1945-1947. \\ DOI: 10.1063/1.123736 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Radiative emission properties of a-SiN : H based nanometric multilayers for light emitting devices}{https://boh/1998-JL.pdf} \\ Giorgis$^\#$, F. and Pirri, C. F. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Journal of Luminescence'' Vol. 80 (1998) pp. 423-427. \\ DOI: 10.1016/s0022-2313(98)00141-0 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  X-ray diffraction, extended x-ray absorption fine structure and Raman spectroscopy studies of WO3 powders and, (1-x)WO3-y center dot xReO(2) mixtures}{https://boh/1998-JAP.pdf} \\ Kuzmin$^\#$, A. and Purans, J. and Cazzanelli, E. and {\bf Vinegoni, C.} and Mariotto, G. \\ ``Journal of Applied Physics'' Vol. 84 (1998) pp. 5515-5524. \\ DOI: 10.1063/1.368596 PMID: N/A PMCID: N/A\item \htmladdnormallink{\it  Photoluminescence of localized excitons in pulsed-laser-deposited GaN}{https://boh/1998-APL.pdf} \\ Cazzanelli$^\#$, M. and Cole, D. and Donegan, J. F. and Lunney, J. G. and Middleton, P. G. and O'Donnell, K. P. and {\bf Vinegoni, C.} and Pavesi, L. \\ ``Applied Physics Letters'' Vol. 73 (1998) pp. 3390-3392. \\ DOI: 10.1063/1.122776 PMID: N/A PMCID: N/A